### 2011-03-15 papers/phase-zero/paper.tex
Add the framework for phase-zero paper, start build system work.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{dependencies/acm_proc_article-sp}

stuff blahh exceedingly fuck

\usepackage{url}
\usepackage{color}
\usepackage{verbatim}
\usepackage{listings}
\lstset{
  language=C++,             % choose the language of the code
  basicstyle=\small,       % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
  stepnumber=0,                   % the step between two line-numbers. If it is 1 each line will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  %frame=single,                   % adds a frame around the code
  tabsize=2,              % sets default tabsize to 2 spaces
  captionpos=t,                   % sets the caption-position to bottom
  breaklines=false,        % sets automatic line breaking
  breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
  escapeinside={\%}{)}          % if you want to add a comment within your code
}

\begin{document}

\title{ Distributed Systems: Project Description }
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Brian Gianforcaro \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{bjg1955@rit.edu}
\alignauthor
Steven Glazer \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{sfg6126@rit.edu}
\alignauthor
Samuel Milton \\
       \affaddr{Rochester Institue Of Technology}\\
       \email{srm2997@rit.edu}
}
\maketitle
\begin{abstract}
%the formatting guidelines for ACM SIG Proceedings.
%It complements the document \textit{Author's Guide to Preparing
%ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
%source file has been written with the intention of being
%compiled under \LaTeX$2_\epsilon$\ and BibTeX.
%
%The developers have tried to include every imaginable sort
%of ``bells and whistles", such as a subtitle, footnotes on
%title, subtitle and authors, as well as in the text, and
%every optional component (e.g. Acknowledgments, Additional
%Authors, Appendices), not to mention examples of
%equations, theorems, tables and figures.
%
%To make best use of this sample document, run it through \LaTeX\
%and BibTeX, and compare this source code with the printed
%output produced by the dvi file.

We will do things... they will be awesome
\end{abstract}

%% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%%%A category including the fourth, optional field follows...
%
%\terms{Theory}

\keywords{ Distributed Systems, Mobile Clients, RIT } % NOT required for Proceedings

stuff \cite{BLAS}
\section{Conclusions}

\newpage
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\balancecolumns
% That's all folks!
\end{document}

### 2011-03-20 src/server/db/insert-questions.py
Add more data to the question insertion script, fix bugs.

@@ -10,6 +10,7 @@ client = riak.RiakClient()
 #
 
 questions = client.bucket('questions')
+
 q = {
  "question" : "In oil painting, why shouldn't you dry your paintings in the dark?",
  "a" : "You can't see when it's dry.",
@@ -18,20 +19,20 @@ q = {
  "d" : "It will stay wet and eventually go mouldy.",
  "answer" : "b"
  }
-entry = questions.new( q["question"], data = q )
+entry = questions.new( "art-1", data = q )
 entry.store()
 
-"""
 q = {
- "question" : "Who painted \'The Scream\' (the famous painting of a man
- screaming with a nuclear mushroom cloud behind him.)?",
+ "question" : "Who painted \'The Scream\' (the famous painting of a man screaming with a nuclear mushroom cloud behind him.)?",
  "a" : "Oskar Kokoschka",
  "b" : "Marc Chagall",
  "c" : "Egon Schiele",
  "d" : "Edvard Munch",
- "answer" : " "
+ "answer" : "d"
 }
-questions.new( q["question"], q )
+entry = questions.new( "art-2", data = q )
+entry.store()
+
 
 q = {
  "question" : "Which famous twentieth century artist painted \"100 Cans\" (Pop Art)?",
@@ -39,9 +40,11 @@ q = {
  "b" : "Roy Lichtenstein",
  "c" : "Piet Mondrian",
  "d" : "Jeff Koons",
- "answer" : " "
+ "answer" : "a"
 }
-questions.new( q["question"], q )
+entry = questions.new( "art-3", data = q )
+entry.store()
+
 
 q = {
  "question" : "What is Pablo Picasso's style of artwork called?",
@@ -49,93 +52,143 @@ q = {
  "b" : "Cubism",
  "c" : "Abstract",
  "d" : "Romanticism",
- "answer" : " "
+ "answer" : "b"
 }
-questions.new( q["question"], q )
+entry = questions.new( "art-4", data = q )
+entry.store()
+
 
 q = {
   "question" : "What art movement was Yoko Ono associated with during the 1960s?",
-	"a" : "Dadaism"
-	"b" : "Futurism"
-	"c" : "Fluxus"
-	"d" : "Post-Impressionism"
-	"answer": " "
+	"a" : "Dadaism",
+	"b" : "Futurism",
+	"c" : "Fluxus",
+	"d" : "Post-Impressionism",
+	"answer": "c"
 }
[…]

### 2011-03-20 src/clients/android/src/edu/rit/cs/distrivia/QuestinActivity.java
Initialize an Eclipse Project for the android client.

@@ -1,0 +1,13 @@
+package edu.rit.cs.distrivia;
+
+import android.app.Activity;
+import android.os.Bundle;
+
+public class QuestinActivity extends Activity {
+    /** Called when the activity is first created. */
+    @Override
+    public void onCreate(Bundle savedInstanceState) {
+        super.onCreate(savedInstanceState);
+        setContentView(R.layout.main);
+    }
+}

### 2011-03-20 papers/phase-zero/paper.tex
Add the content Sticky wrote to latex paper, fix img dir.

@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
-
 \documentclass{dependencies/acm_proc_article-sp}
-
-stuff blahh exceedingly fuck
 
@@
 
+% Get rid of the permission block
+\makeatletter
+\let\@copyrightspace\relax
+\makeatother
+
 \begin{document}
 
-\title{ Distributed Systems: Project Description }
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{3} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
+%\title{ Distributed Systems: Project Description }
+\title{ Distrivia: A Distributed Trivia Game }
+\numberofauthors{3}
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
 \alignauthor
@@
 \maketitle
-\begin{abstract}
-%the formatting guidelines for ACM SIG Proceedings.
-%It complements the document \textit{Author's Guide to Preparing
-%ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
-%source file has been written with the intention of being
-%compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-%
-%The developers have tried to include every imaginable sort
-%of ``bells and whistles", such as a subtitle, footnotes on
-%title, subtitle and authors, as well as in the text, and
-%every optional component (e.g. Acknowledgments, Additional
-%Authors, Appendices), not to mention examples of
-%equations, theorems, tables and figures.
-%
-%To make best use of this sample document, run it through \LaTeX\
-%and BibTeX, and compare this source code with the printed
-%output produced by the dvi file.
 
-We will do things... they will be awesome
-\end{abstract}
+%\begin{abstract}
+%In this paper we detail our initial idea for a distributed trivia game.
+%We will explain general game play idea's as well as an example of the
+%possible architecture for our system.
+%\end{abstract}
 
-%% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%%%A category including the fourth, optional field follows...
-%
-%\terms{Theory}
+\section{Overview}
+Our idea for the P3 project is a trivia game built for a distributed system, which we're calling Distrivia.
+The premise of the program is to deliver multiple-choice trivia questions to the players in the form of rounds.
+Ten questions will be delivered for each round.
+Players are connected up in groups of 20 players, with each player's score dependent on the speed in which they answer each question.
+Once each player has completed the round, the leader board for the round will display the scores for each player for that round.
+After which, the players will join new rounds to compete against other players.
+Distrivia will also keep a tally of their global score (possibly an average), which will determine how well the player competes on a whole.
+This global score could give the player a unique symbol after their name on leader boards or perhaps a distinct color.
 
-\keywords{ Distributed Systems, Mobile Clients, RIT } % NOT required for Proceedings
+The trivia questions will come from many different aspects of academia and at varying level of difficulty
+This will assure that there is an equal chance for players to get questions correct and compete.
 
-stuff \cite{BLAS}
-\section{Conclusions}
+We would also like to implement a way for players to create a private game so they can compete with friends.
+This will be accomplished by the initial player naming the game, and the other players joining the game with the name.
+Private games allow users to compete with people the know which will allow the game to be more interactive.
+
+\section{Implementation}
+We will be creating software, initially, for desktops, laptops, and android phones.
+The software for desktops/laptops will be implemented in a web browser.
+If there is time to implement it, we want to create an application for the iPhone as well.
+The applications for all platforms will look identical and allow the players to have the same functionality, independent of which device they are using to play Distrivia.
+
+\subsection{Clients}
+The client will be pretty straightforward.
+If you have never played Distrivia before, the game will prompt for the player to create a player name.
+After which, it will allow the user to request to play a game.
+Once the server has grouped 20 players together, the round will start and the screen will show the question followed by 4 selectable answers.
+Once the user has selected their answer, they can hit the Submit button at the bottom to submit their answer for that question.
+At that point, the player's answer is sent to the server, their new score along with their next question is sent back to the player.
+At the bottom of the screen, the player will be able to select from thumbs up/thumbs down buttons if they particularly like or dislike a question.
+This will be particularly useful if we have time to allow users to create their own questions to add the to the database.
+Once a questions dislike ratio is too high, the question will no longer be asked.
+
+  \includegraphics[scale=0.3]{design-pictures/login.png}
+  \includegraphics[scale=0.3]{design-pictures/joingame.png}
+  \includegraphics[scale=0.3]{design-pictures/quiz.png}
+  \includegraphics[scale=0.3]{design-pictures/leaderboard.png}
+
+\subsection{Backend}
+The server has four key layers involved.
+First, there will be load balancer that accepts all messages from the players.
+It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
+This ensures that if any of the servers were to go down, that the system would still run.
+It also maintains highest speeds for server response.
+The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
+These messages will be in the form of http messages.
+The web server communicates directly with the database to perform whatever actions need to be done.
+The third layer is represented by these synchronous databases that hold all the actual data for the software.
+This would include round information, player information, and all the questions for the application.
+The fourth and final layer would be some sort of master process that does the actual synchronization between the databases so that they all contain repetitive data for reliable communication.
+
+\begin{center}
+  \includegraphics[scale=0.3]{design-pictures/database.png}
+\end{center}
 
@@
 % produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
+%/\bibliographystyle{abbrv}
+%\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file

### 2011-03-21 papers/phase-zero/paper.tex
Fix project setup in eclipse, should be able to import now.
Added Sam's grammar fixes to the latex version of the paper.

@@
 This will be accomplished by the initial player naming the game, and the other players joining the game with the name.
-Private games allow users to compete with people the know which will allow the game to be more interactive.
+Private games allow users to compete with people they know which will allow the game to be more interactive.
 
@@
 The server has four key layers involved.
-First, there will be load balancer that accepts all messages from the players.
+First, there will be a load balancer that accepts all messages from the players.
 It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
@@
 This would include round information, player information, and all the questions for the application.
-The fourth and final layer would be some sort of master process that does the actual synchronization between the databases so that they all contain repetitive data for reliable communication.
+The fourth and final layer would be some sort of master process that does the
+actual synchronization between the databases so that they all contain redudant data for reliable communication.
 

### 2011-03-21 src/clients/android/src/edu/rit/cs/distrivia/QuestinActivity.java
Added basic log in menu for android app

@@ -2,12 +2,38 @@ package edu.rit.cs.distrivia;
 
 import android.app.Activity;
 import android.os.Bundle;
+import android.view.View;
+import android.view.View.OnClickListener;
+import android.widget.Button;
+import android.widget.EditText;
+import android.widget.Toast;
 
 public class QuestinActivity extends Activity {
+	private EditText uname;
+	private EditText pass;
+	
     /** Called when the activity is first created. */
     @Override
     public void onCreate(Bundle savedInstanceState) {
         super.onCreate(savedInstanceState);
         setContentView(R.layout.main);
+        
+        Button login = (Button)findViewById( R.id.login_button );
+		uname = (EditText)findViewById( R.id.login_input_username );
+		pass = (EditText)findViewById( R.id.login_input_password );
+
+		login.setOnClickListener( new OnClickListener(){
+			@Override
+			public void onClick( View v ){
+				String name = uname.getText().toString().trim();
+				String paswd = pass.getText().toString().trim();
+
+				if( !name.equals( "" ) && !paswd.equals( "" ) ){
+					Toast.makeText( getApplicationContext(), "Welcome back, " + uname.getText().toString(), 10 ).show();
+				}else{
+					Toast.makeText( getApplicationContext(), "Incorrect Login", 10 ).show();
+				}
+			}
+		} );
     }
 }

### 2011-03-21 src/setup-node.sh
Add script to setup a Amazon EC2 instance for development.

@@ -1,0 +1,36 @@
+#!/bin/sh
+
+#
+# This script installs all dependencies for the distivia backend on an EC2 instance.
+#
+#  Dependencies:
+#    * Riak        - masterless data base store
+#    * protobuf    - Required by python riak client
+#    * python-riak - python riak client
+#    * flask       - Web app framework for python
+#    * git         - Version control for our application
+#
+#
+#
+
+# Install Riak Server
+wget http://downloads.basho.com/riak/CURRENT/riak-0.14.0-1.el5.x86_64.rpm
+sudo yum -y install --nogpgcheck riak-0.14.0-1.el5.x86_64.rpm
+
+# Install Protocol buffers library C/C++/Python
+wget ftp://ftp.pbone.net/mirror/archive.fedoraproject.org/fedora/linux/updates/testing/12/x86_64/protobuf-2.3.0-1.fc12.i686.rpm
+sudo yum -y install --nogpgcheck protobuf-2.3.0-1.fc12.i686.rpm
+
+# Install python flask library
+sudo easy_install flask
+
+# Install python riak client library
+sudo easy_install riak
+
+# Install git commandline client
+sudo yum -y install git
+git clone git://github.com/bgianfo/distributed-systems.git
+
+# Remove left over package files
+rm -rf riak-0.14.0-1.el5.x86_64.rpm
+rm -rf protobuf-2.3.0-1.fc12.i686.rpm

### 2011-03-24 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java
Fix two syntax bugs, woops!

@@ -31,26 +31,26 @@ public class DistriviaAPI {
     private static HttpContext localContext = new BasicHttpContext();
     final private static String API_URL = "http://distrivia.com";
     final private static String API_ERROR = "err";
-    final private static String API_SUCCESS = "suc"
+    final private static String API_SUCCESS = "suc";
 
     /**
      * API call to login to Distrivia with a specific user name.
-     *
+     * 
      * @param userName
      *            The user name to attempt to login to distrivia with.
-     *
+     * 
      * @return The authorization users token on success, otherwise null on
      *         authentication failure.
      */
     public static String login(String userName) {
         String url = new String(API_URL);
-        url += "/login/" + username;
+        url += "/login/" + userName;
 
         HttpPut op = new HttpPut(url);
         HttpResponse response = executeRequest(op);
         String data = responseToString(response);
 
-        if ( data == API_ERROR ) {
+        if (data == API_ERROR) {
             return null;
         } else {
             return data;
@@ -59,7 +59,7 @@ public class DistriviaAPI {
 
     /**
      * API Call to register a new user
-     *
+     * 
      * @param username
      *            The user name to register with the service.
      * @return True on register success, false on register failure.
@@ -79,13 +79,13 @@ public class DistriviaAPI {
 
     /**
      * API call to get the next multiple point question in a game.
-     *
+     * 
      * @param authToken
      *            The authorization token for this session, obtained at user
      *            login.
      * @param gameId
      *            The identification string for this game.
-     *
+     * 
      * @return The next question in the game, or null if the game is over.
      */
     public static Question nextQuestion(final String authToken,
@@ -113,7 +113,7 @@ public class DistriviaAPI {
 
     /**
      * API call to answer a given question that has been posed to a user.
-     *
+     * 
      * @param authToken
      *            The authorization token for this session, obtained at user
      *            login.
@@ -125,7 +125,7 @@ public class DistriviaAPI {
      * @param answerTime_ms
      *            The time in mili-seconds it took the user to answer the
      *            question.
-     *
+     * 
      * @return Return true if answer went through successfully, otherwise return
      *         false on error. Error could be, wrong authorization token,
      *         incorrect gameId, impossible answerTIme etc...
@@ -147,13 +147,13 @@ public class DistriviaAPI {
 
     /**
      * API call to obtain the current leader board for a given game.
-     *
+     * 
      * @param authToken
      *            The authorization token for this session, obtained at user
      *            login.
      * @param gameId
[…]

### 2011-03-25 src/clients/android/src/edu/rit/cs/distrivia/api/Leaderboard.java
Fix up some Java Doc's and remove un-needed functionality

@@ -7,71 +7,81 @@ import org.json.JSONArray;
 import org.json.JSONException;
 import org.json.JSONObject;
 
+/**
+ * Object that represents the Game's Score Board
+ */
 public class Leaderboard {
-    
+
     private List<String> userLeader;
     private List<Integer> scoreLeader;
-    
+
     // Prevent construction without factory
-    private Leaderboard () {}
-    
+    private Leaderboard() {
+    }
+
     /**
      * Factory method to create a Leader board from JSON.
      * 
-     * @param json The JSON leader board object to create from.
+     * @param json
+     *            The JSON leader board object to create from.
      * 
      * @return The leader board object create from the JSON
      */
-    public static Leaderboard create( JSONObject json ) {
-        
-        Leaderboard board = new Leaderboard();
-        
+    public static Leaderboard create(final JSONObject json) {
+
+        final Leaderboard board = new Leaderboard();
+
         board.userLeader = new ArrayList<String>();
         board.scoreLeader = new ArrayList<Integer>();
-        
+
         try {
-            JSONArray arr = json.getJSONArray("arr");
-            
-            for( int i = 0; i < arr.length(); i++ ) {
-                JSONObject user = arr.getJSONObject(i);
-                
-                String uname = user.getString("uname");
-                Integer score = user.getInt("score");
-                
+            final JSONArray arr = json.getJSONArray("arr");
+
+            for (int i = 0; i < arr.length(); i++) {
+                final JSONObject user = arr.getJSONObject(i);
+
+                final String uname = user.getString("uname");
+                final Integer score = user.getInt("score");
+
                 board.userLeader.add(uname);
                 board.scoreLeader.add(score);
             }
-            
-        } catch (JSONException e) {
+
+        } catch (final JSONException e) {
         }
-        
+
         return board;
     }
-     
+
     /**
      * Getter for individual leader board users.
-     * @param i The index into the leader board to return.
+     * 
+     * @param i
+     *            The index into the leader board to return.
      * @return The i-th position user in the leader board.
-     */   
-    public String getUser( int i ) {
+     */
+    public String getUser(final int i) {
         return userLeader.get(i);
     }
-    
+
     /**
      * Getter for individual leader board scores.
-     * @param i The index into the leader board to return.
+     * 
+     * @param i
+     *            The index into the leader board to return.
      * @return The i-th position score in the leader board.
      */
-    public int getScore( int i ) {
+    public int getScore(final int i) {
[…]

### 2011-03-25 src/clients/android/src/edu/rit/cs/distrivia/api/Question.java

@@ -3,72 +3,83 @@ package edu.rit.cs.distrivia.api;
 import org.json.JSONException;
 import org.json.JSONObject;
 
+/**
+ *
+ */
 public class Question {
-    
+
     private String question;
     private String choiceA;
     private String choiceB;
     private String choiceC;
     private String choiceD;
-    
+
     // Prevent construction without factory
-    private Question() {}
-    
+    private Question() {
+    }
+
     /**
-     * Factory method to create a question from JSON. 
-     * @param arr The JSON object from the server.
+     * Factory method to create a question from JSON.
+     * 
+     * @param arr
+     *            The JSON object from the server.
      * @return A properly initialized question
      */
-    public static Question create( JSONObject arr ) {
-        Question q = new Question();
+    public static Question create(final JSONObject arr) {
+        final Question q = new Question();
         try {
-            q.setQuestion( arr.getString("question") );
-            q.setChoiceA( arr.getString("a") );
-            q.setChoiceB( arr.getString("b") );
-            q.setChoiceC( arr.getString("c") );
-            q.setChoiceD( arr.getString("d") );
-        } catch (JSONException e) {
+            q.question = arr.getString("question");
+            q.choiceA = arr.getString("a");
+            q.choiceB = arr.getString("b");
+            q.choiceC = arr.getString("c");
+            q.choiceD = arr.getString("d");
+        } catch (final JSONException e) {
         }
         return q;
     }
 
+    /**
+     * Getter for the question text.
+     * 
+     * @return A String containing the question text
+     */
     public String getQuestion() {
         return question;
     }
 
-    public void setQuestion(String question) {
-        this.question = question;
-    }
-
+    /**
+     * Getter for the "A" choice for this question.
+     * 
+     * @return This choices text String.
+     */
     public String getChoiceA() {
         return choiceA;
     }
 
-    public void setChoiceA(String choiceA) {
-        this.choiceA = choiceA;
-    }
-
+    /**
+     * Getter for the "B" choice for this question.
+     * 
+     * @return This choices text String.
+     */
     public String getChoiceB() {
         return choiceB;
     }
 
-    public void setChoiceB(String choiceB) {
-        this.choiceB = choiceB;
-    }
-
+    /**
+     * Getter for the "C" choice for this question.
+     * 
+     * @return This choices text String.
+     */
     public String getChoiceC() {
         return choiceC;
     }
 
[…]

### 2011-03-25 papers/phase-zero/paper.tex
Lowercased 'of' in RIT label in latex file
remove synchronizer, add Riak

@@
 Brian Gianforcaro \\
-       \affaddr{Rochester Institue Of Technology}\\
+       \affaddr{Rochester Institue of Technology}\\
        \email{bjg1955@rit.edu}
@@
 Steven Glazer \\
-       \affaddr{Rochester Institue Of Technology}\\
+       \affaddr{Rochester Institue of Technology}\\
        \email{sfg6126@rit.edu}
@@
 Samuel Milton \\
-       \affaddr{Rochester Institue Of Technology}\\
+       \affaddr{Rochester Institue of Technology}\\
        \email{srm2997@rit.edu}
@@
 This would include round information, player information, and all the questions for the application.
-The fourth and final layer would be some sort of master process that does the
-actual synchronization between the databases so that they all contain redudant data for reliable communication.
-
+Currently we are looking at using Riak \cite{riak} for our database engine.
+Riak has the unique ability to perform automatic masterless replication and
+syncrhonization between all nodes of a database cluster. With this architecture 
+all backend nodes except for one could fail and our system would remain
+operational.
 \begin{center}

### 2011-03-25 papers/phase-zero/paper.tex
Fix spelling, add new image from sam to the paper, fix formatting.

--- 2011-03-21 papers/phase-zero/paper.tex
@@
 
-\subsection{Clients}
+%\subsection{Clients}
 The client will be pretty straightforward.
@@
 
-\subsection{Backend}
+%\subsection{Backend}
 The server has four key layers involved.
@@
 This would include round information, player information, and all the questions for the application.
-The fourth and final layer would be some sort of master process that does the
-actual synchronization between the databases so that they all contain redudant data for reliable communication.
-
+Currently we are looking at using Riak for our database engine.
+Riak has the unique ability to perform automatic master less replication and
+synchronization between all nodes of a database cluster. With this architecture 
+all back end nodes except for one could fail and our system would remain
+operational.
 \begin{center}
-  \includegraphics[scale=0.3]{design-pictures/database.png}
+  \includegraphics[scale=0.35]{design-pictures/database2.png}
 \end{center}
@@
 % produce the bibliography for the citations in your paper.
-%/\bibliographystyle{abbrv}
+%\bibliographystyle{abbrv}
 %\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case

### 2011-03-25 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java
Implement sever join, fix next Q in server + client.
- Add an initial implementation for joining a random game.

- Fix the '/game/<id>/next' route, by fixing an edge case
  when using the previous question id to find the next.

- Fix the nextQuestion implementation in the android
  DistriviaAPI class.

- Add id to Question object, unpack it correctly

@@ -78,22 +78,41 @@ public class DistriviaAPI {
     }
 
     /**
-     * API call to get the next multiple point question in a game.
+     * API call to get the initial multiple choice question in a game.
      * 
      * @param authToken
      *            The authorization token for this session, obtained at user
      *            login.
      * @param gameId
      *            The identification string for this game.
+     * @return The next question in the game, or null if the game is over, or
+     *         error.
+     */
+    public static Question firstQuestion(final String authToken,
+            final String gameId) {
+        return nextQuestion(authToken, gameId, "0");
+    }
+
+    /**
+     * API call to get the next multiple choice question in a game.
+     * 
+     * @param authToken
+     *            The authorization token for this session, obtained at user
+     *            login.
+     * @param gameId
+     *            The identification string for this game.
+     * @param prevId
+     *            The previous question id, just pass "0" if this is the initial
+     *            question fetch.
      * 
      * @return The next question in the game, or null if the game is over.
      */
     public static Question nextQuestion(final String authToken,
-            final String gameId) {
+            final String gameId, final String prevId) {
 
         String url = new String(API_URL);
 
-        url += "/game/" + gameId + "/next";
+        url += "/game/" + gameId + "/next/" + prevId;
 
         url += "?authToken=" + authToken;
 

### 2011-03-25 src/clients/android/src/edu/rit/cs/distrivia/api/Question.java

@@ -8,6 +8,7 @@ import org.json.JSONObject;
  */
 public class Question {
 
+    private String id;
     private String question;
     private String choiceA;
     private String choiceB;
@@ -33,9 +34,14 @@ public class Question {
             q.choiceB = arr.getString("b");
             q.choiceC = arr.getString("c");
             q.choiceD = arr.getString("d");
+            q.id = arr.getString("id");
         } catch (final JSONException e) {
         }
         return q;
+    }
+
+    public String id() {
+        return id;
     }
 
     /**

### 2011-03-25 src/server/distrivia.py

@@ -29,10 +29,11 @@ QUESTION_LIMIT = 20
 #
 # Utility functions
 #
+
 def isAuthed():
     """
-    Read the request and automatically check if he auth token is valid
-    and "logged-in". 
+    Read the request and automatically check if he auth
+    token is valid and "logged-in".
 
     Return True if so, False if not.
     """
@@ -120,18 +121,53 @@ def newGame():
     Create a new game"""
     return "NOT IMPLEMEMTED"
 
-
-
 @app.route('/game/join')
 def joinGame():
     """GET /game/join
 
     Join a currently open game if available,
     otherwise create a new one"""
-    return "NOT IMPLEMEMTED"
+
+    # Failure on authentication error
+    if not isAuthed():
+        return API_ERROR
+
+    user  = request.form['user']
+    if user == "":
+        return API_ERROR
+
+    # Initialize arguments, riak variables and buckets
+    token = request.form['authToken']
+    client = g.db
+    gamesBucket = client.bucket("games")
 
 
+    # Map function to inspect tables and grab non full games
+    mapfn = """ function(iterm) {
+                    var data = JSON.parse( item.values[0].data );
+                    if ( data.users.length < 20 ) {
+                        return [[item.key, data]];
+                    }
+                    return [];
+                }
+            """
+    query = client.add("games")
+    query.map( mapfn )
 
+    for result in query.run():
+        key, data  = result[0], result[1]
+
+        # Add user to the game
+        data["users"].append( token )
+        # Add user to the leader board
+        data["leaderboard"][user] = 0
+
+        game = gamesBucket.get(key)
+        game.set_data( data );
+        game.store()
+        return key
+
+    return API_ERROR
 
 @app.route('/game/<id>/next/<prevId>')
 def nextQuestion(id,prevId):
@@ -153,14 +189,19 @@ def nextQuestion(id,prevId):
         # Get the list of questions for this game
         gameData = game.get_data();
         questions = gameData["questions"]
-        qIndex = questions.index( prevId )
 
-        # Failure on this game being over
-        if qIndex == QUESTION_LIMIT:
-            return API_ERROR:
+        nextQuestion = None
+        if prevId == "0":
+            nextQuestion = questions[0]
+        else:
+            qIndex = questions.index( prevId )
 
-        # Fetch and construct the next question object
-        nextQuestion = questions[qIndex+1]
+            # Failure on this game being over
+            if qIndex == QUESTION_LIMIT:
+                return API_ERROR:
[…]

### 2011-04-06 papers/phase-one/paper.tex
Setup and add phase-one document latex paper...

--- 2011-03-25 papers/phase-zero/paper.tex
@@
 
-\section{Overview}
-Our idea for the P3 project is a trivia game built for a distributed system, which we're calling Distrivia.
-The premise of the program is to deliver multiple-choice trivia questions to the players in the form of rounds.
-Ten questions will be delivered for each round.
-Players are connected up in groups of 20 players, with each player's score dependent on the speed in which they answer each question.
-Once each player has completed the round, the leader board for the round will display the scores for each player for that round.
-After which, the players will join new rounds to compete against other players.
-Distrivia will also keep a tally of their global score (possibly an average), which will determine how well the player competes on a whole.
-This global score could give the player a unique symbol after their name on leader boards or perhaps a distinct color.
+\section{What We've Done}
+So far, our work has mainly focused on getting everything setup to work as a
+distributed system. Getting the ground work done (for example servers and load
+distributers running) has provided us a way to quickly develop the clients and
+server as well as provided us with a way to reliably connect the servers to the
+clients.
 
-The trivia questions will come from many different aspects of academia and at varying level of difficulty
-This will assure that there is an equal chance for players to get questions correct and compete.
+\subsection{Servers}
+Currently, we have 4 servers running. One server is being used as a web-monitor
+host. We are able to login to the web-monitor to see the status of all our
+servers, databases, and load distributers. This will help us manage if the
+services are running and allow us to track down any problems, if they arise.
+The other three servers are all running our server application and hosting the
+databases. Each server contains the server application that responds to clients
+as well as the Riak databases. Riak auto-synchronizes the databases between the
+3 servers. If we were to add a server, we would just need to updatrver as well
+as provided us with a way to reliably connect the servers to the clients.
 
-We would also like to implement a way for players to create a private game so they can compete with friends.
-This will be accomplished by the initial player naming the game, and the other players joining the game with the name.
-Private games allow users to compete with people they know which will allow the game to be more interactive.
+\subsection {Traffic}
+We have two load distributers set up. Both distributers are currently
+configured to divide the requests among the 3 active servers. The duplicate
+distributers allow for a load distributer to go down and we would still be able
+to serve requests to the servers. These load distributers are selected by the
+clients using round robin DNS where distrivia.lame.ws will select either load
+distributer that is up at random. This provides us will stability for access to
+the servers. The load distributers are set up the attempt to connect to a
+server twice before deeming it dead and removing it from its list of servers to
+direct clients towards.
 
-\section{Implementation}
-We will be creating software, initially, for desktops, laptops, and android phones.
-The software for desktops/laptops will be implemented in a web browser.
-If there is time to implement it, we want to create an application for the iPhone as well.
-The applications for all platforms will look identical and allow the players to have the same functionality, independent of which device they are using to play Distrivia.
+\subsection {Clients}
+Our focus for clients has been on a web-based client and an android
+application. Both clients have most of the their screens completed. The
+web-based client will be run from desktop platforms and laptop platforms. The
+android client will run on any android phone and does not use any unique
+services that require specific hardware.
 
-%\subsection{Clients}
-The client will be pretty straightforward.
-If you have never played Distrivia before, the game will prompt for the player to create a player name.
-After which, it will allow the user to request to play a game.
-Once the server has grouped 20 players together, the round will start and the screen will show the question followed by 4 selectable answers.
-Once the user has selected their answer, they can hit the Submit button at the bottom to submit their answer for that question.
-At that point, the player's answer is sent to the server, their new score along with their next question is sent back to the player.
-At the bottom of the screen, the player will be able to select from thumbs up/thumbs down buttons if they particularly like or dislike a question.
-This will be particularly useful if we have time to allow users to create their own questions to add the to the database.
-Once a questions dislike ratio is too high, the question will no longer be asked.
+\section{What's Left}
+\subsection{Web Client}
+Joining/playing private games
+In-game leaderboard
+Finish connecting to actual serversver API
+Implement useful user warnings
 
-  \includegraphics[scale=0.3]{design-pictures/login.png}
-  \includegraphics[scale=0.3]{design-pictures/joingame.png}
-  \includegraphics[scale=0.3]{design-pictures/quiz.png}
-  \includegraphics[scale=0.3]{design-pictures/leaderboard.png}
+\subsection{Android}
+Connecting to server API
+Registration
+Private games
+Leaderboards
+Allowing users to control screens
 
-%\subsection{Backend}
-The server has four key layers involved.
-First, there will be a load balancer that accepts all messages from the players.
-It does not need to read the contents of the message, it simply distributes the message on to the most reliable server with the lowest load.
-This ensures that if any of the servers were to go down, that the system would still run.
-It also maintains highest speeds for server response.
-The message is passed to a web server from the load balancer, which will read the contents of the message and respond appropriately.
-These messages will be in the form of http messages.
-The web server communicates directly with the database to perform whatever actions need to be done.
-The third layer is represented by these synchronous databases that hold all the actual data for the software.
-This would include round information, player information, and all the questions for the application.
-Currently we are looking at using Riak for our database engine.
-Riak has the unique ability to perform automatic master less replication and
-synchronization between all nodes of a database cluster. With this architecture 
-all back end nodes except for one could fail and our system would remain
-operational.
-\begin{center}
-  \includegraphics[scale=0.35]{design-pictures/database2.png}
-\end{center}
+\subsection{Server}
+Passwords
+Private game joining
+Global leaderboard
+Finish setting up SSL on load distributers
+Set up 2 hot spares
+
+\section {Meeting the Requirements}
+-3 Devices (Android, Desktop, Laptop)
+-Reliable / Flexible communication (Multiple servers, multiple load
+distributers, 2 hot spares, proper communication to user)
+-Coordination/Cooperation (Synchronous Databases and Rounds consisting of many
+players)
+-Replication / Availability / Consistency (Riak handles synchronizing databases
+among servers. Load distributers provide availability)
+- Naming / Service Discovery
+- Fault tolerance / Handling of partial failures
+- Security (SSL)
+- Scalability (add new nodes and add to riak cluster and it's all set)
+- Use of an interesting distributed algorithm
 

### 2011-04-07 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java
Implemented scrollable leaderboard

@@ -19,7 +19,7 @@ import android.widget.Toast;
 public class JoinActivity extends Activity {
 	
     /** Called when the activity is first created. */
-    @Override
+	@Override
     public void onCreate(final Bundle savedInstanceState) {
         super.onCreate(savedInstanceState);
         requestWindowFeature(Window.FEATURE_NO_TITLE);

### 2011-04-07 src/clients/android/src/edu/rit/cs/distrivia/LeaderboardActivity.java

@@ -13,8 +13,6 @@ import android.widget.TextView;
  */
 public class LeaderboardActivity extends Activity {
 
-    //private String authToken;
-    //private String gameId;
 	TableLayout leaderTable;
 
     /** Called when the activity is first created. */
@@ -30,19 +28,17 @@ public class LeaderboardActivity extends Activity {
     }
     
     private void loadTable() {
-    	TableRow row = new TableRow(getApplicationContext());
-    	//LinearLayout rowLayout = new LinearLayout(getApplicationContext());
-    	//rowLayout.setOrientation(LinearLayout.HORIZONTAL);
-    	TextView name = new TextView(getApplicationContext());
-    	name.setText("Prof1");
-    	name.setWidth(200);
-    	TextView score = new TextView(getApplicationContext());
-    	score.setText("10000");
-    	row.addView(name);
-    	row.addView(score);
-    	//row.addView(rowLayout);
-    	leaderTable.addView(row);
-    	
+	    for (int i=0; i < 30; i++) {
+	    	TableRow row = new TableRow(getApplicationContext());
+	    	TextView name = new TextView(getApplicationContext());
+	    	name.setText("Prof1");
+	    	name.setWidth(200);
+	    	TextView score = new TextView(getApplicationContext());
+	    	score.setText("10000");
+	    	row.addView(name);
+	    	row.addView(score);
+	    	leaderTable.addView(row);
+	    }	
     }
 
 }

### 2011-04-07 papers/phase-one/paper.tex
Add sam's new section, and section on security.

@@
 
-\section{What We've Done}
+\section {What We've Done}
 So far, our work has mainly focused on getting everything setup to work as a
 distributed system. Getting the ground work done (for example servers and load
-distributers running) has provided us a way to quickly develop the clients and
-server as well as provided us with a way to reliably connect the servers to the
-clients.
-
-\subsection{Servers}
+distributers running) has provided us a way to quickly develop the clients
+and server as well as provided us with a way to reliably connect the servers to
+the clients.
+\subsection {Servers}
 Currently, we have 4 servers running. One server is being used as a web-monitor
 host. We are able to login to the web-monitor to see the status of all our
-servers, databases, and load distributers. This will help us manage if the
-services are running and allow us to track down any problems, if they arise.
-The other three servers are all running our server application and hosting the
-databases. Each server contains the server application that responds to clients
-as well as the Riak databases. Riak auto-synchronizes the databases between the
-3 servers. If we were to add a server, we would just need to updatrver as well
-as provided us with a way to reliably connect the servers to the clients.
+servers, databases, and load distributers. This will help us manage if the services
+are running and allow us to track down any problems, if they arise. The other three
+servers are all running our server application and hosting the databases.
+Each server contains the server application that responds to clients as well as
+the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 3 servers. If
+we were to add a server, we would just need to update Riak and it would sync the
+databases to any additional servers as well. These servers, therefore, all contain
+the same information. If any servers go down, the distributed system would still
+run fine. We could have all servers go down except one and still be reliably
+handling requests.
+\subsection {Traffic}
+We have two load distributers set up. Both distributers are currently configured to
+divide the requests among the 3 active servers. The duplicate distributers allow
+for a load distributer to go down and we would still be able to serve requests
+to the servers. These load distributers are selected by the clients using round
+robin DNS where distrivia.lame.ws will select either load distributer that is
+up at random. This provides us will stability for access to the servers. The
+load distributers are set up the attempt to connect to a server twice before
+deeming it dead and removing it from its list of servers to direct clients towards.
+\subsection {Messages}
+We are currently using https protocol for our messages. This provides a secure
+and usable message system that we have conformed our client and server APIs to use.
+The actual message content is in the form of JSON objections \cite{json} 
+\subsection {Clients}
+Our focus for clients has been on a web-based client and an android application.
+Both clients have most of the their screens completed. The web-based client will
+be run from desktop platforms and laptop platforms. The android client will run
+on any android phone and does not use any unique services that require specific
+hardware. The web client is nearly fully-functional. It currently can login/register
+players, join public games, and compete in public games. The android client has
+he UI done for all the different activities. The android client successfully registers
+and logs in players.
 
-\subsection {Traffic}
-We have two load distributers set up. Both distributers are currently
-configured to divide the requests among the 3 active servers. The duplicate
-distributers allow for a load distributer to go down and we would still be able
-to serve requests to the servers. These load distributers are selected by the
-clients using round robin DNS where distrivia.lame.ws will select either load
-distributer that is up at random. This provides us will stability for access to
-the servers. The load distributers are set up the attempt to connect to a
-server twice before deeming it dead and removing it from its list of servers to
-direct clients towards.
-
-\subsection {Clients}
-Our focus for clients has been on a web-based client and an android
-application. Both clients have most of the their screens completed. The
-web-based client will be run from desktop platforms and laptop platforms. The
-android client will run on any android phone and does not use any unique
-services that require specific hardware.
-
-\section{What's Left}
-\subsection{Web Client}
+\section {What's Left}
+\subsection {Web Client}
  Joining/playing private games
  In-game leaderboard
-Finish connecting to actual serversver API
+ inish connecting to actual server API
  Implement useful user warnings
-
-\subsection{Android}
-Connecting to server API
-Registration
-Private games
-Leaderboards
-Allowing users to control screens
-
-\subsection{Server}
-Passwords
+\subsection {Android}
+So far, the only connection to the server that the android client has is when it
+registers/logs in. We still need to connect the rest of the android client to
+the server API to make sure all the communication between the android client
+and the server are working. This includes joining public/private rounds,
+competing in these rounds, and viewing leaderboards. While the UI is nearly
+finished on the android client, nearly all of the connections to the servers
+has yet to be done. Additionally, the android client needs to have more user
+feedback and increased ability for the users to control which activity they
+are in.
+\subsection {Server}
 Private game joining
 Global leaderboard
-Finish setting up SSL on load distributers
-Set up 2 hot spares
 
 \section {Meeting the Requirements}
--3 Devices (Android, Desktop, Laptop)
--Reliable / Flexible communication (Multiple servers, multiple load
-distributers, 2 hot spares, proper communication to user)
--Coordination/Cooperation (Synchronous Databases and Rounds consisting of many
-players)
--Replication / Availability / Consistency (Riak handles synchronizing databases
-among servers. Load distributers provide availability)
-- Naming / Service Discovery
-- Fault tolerance / Handling of partial failures
-- Security (SSL)
-- Scalability (add new nodes and add to riak cluster and it's all set)
+
+Our system has two unique clients. One of them is designed for the Android platform as an app.
+The other is a web client which is specifically being tested on Desktop and Laptop
+browsers, however it may work on many handheld web browsers as well.
+
+Our system supports having any number of servers and allowing any subset of them to fail.
+We are using Riak, which supports a ''shared nothing' architecture.
+We can add a new server by joining it to our database and starting the web server.
+This can be done as many times as needed, allowing us to scale up our system.
+These same principles also give us great fault tolerance, since any server is capable of running independently.
+As long as one server is still up, the service will be available.
+
+We use round robin DNS to allow our clients to be completely ignorant of our servers.
+Load distributors can be added and removed from the DNS server and the clients will be completely ignorant of this and unaffected.
+The load distributors in turn know about our data servers and do their best to distribute the load across them.
+When a new server is added, it is just added to our load distributor configuration file and clients can start using it.
+When a server fails, the distributors will stop directing traffic to it.
+
+- Coordination/Cooperation (Synchronous Databases and Rounds consisting of many players)
+- Replication / Availability / Consistency (Riak handles synchronizing databases among servers. Load distributers provide availability)
+  < Needs stuff on Riak>
+
+ Our team is taking a very proactive stance towards security. All of our machines are properly fire walled so that
+ outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
+ Our load balancer's automatically redirect http:// to https:// and once you are in https:// at the load balancer, SSL continues all the
+ way back to our actual web application back end serving responses over a SSL wrapped socket. This way no passwords are ever
+ sent in clear text. Our group even found a SSL certificate authority who was willing to sign our SSL certificate for free. This gives
+ us actual fully functional, authenticate able SSL infrastructure. In order to make sure that our system properly secures user information,
+ we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using
+ the cryptographically secure hashing function designed for passwords known as bcyrpt \cite{bcrypt}.
+
 - Use of an interesting distributed algorithm
@@
 % produce the bibliography for the citations in your paper.
-%\bibliographystyle{abbrv}
-%\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
+\bibliographystyle{abbrv}
+\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file

### 2011-04-07 papers/phase-one/paper.tex
Added 'Whats Left' for web client to phase one paper

@@
 \subsection {Web Client}
- Joining/playing private games
- In-game leaderboard
- inish connecting to actual server API
- Implement useful user warnings
+A lof of the main features of the web client are completed.
+However, there are stil a few remaining features that need to be implemented.
+The first is private games.
+Joining them has only been stubbed out with no functionality.
+The game playing routinees from public games should be compatible with private games, but may need a few tweeks as well.
+Next, while it currently supports a universal leaderboard, it also needs to be able to display one ingame.
+With the recent API changes, there are a few existing features which need to have thir API calls adjusted slightly.
+Another feature that needs to be finished is displaying useful warnings and error messages.
+While progress has been made on them and a reporting system has been built, messages still need to be fed into it.
+Lastly, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response, alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
 \subsection {Android}

### 2011-04-08 papers/phase-one/paper.tex
Write a bunch on messages, riak, and hot spares

--- 2011-04-07 papers/phase-one/paper.tex
@@
 \subsection {Servers}
-Currently, we have 4 servers running. One server is being used as a web-monitor
+Currently, we have 6 servers running. One server is being used as a web-monitor
 host. We are able to login to the web-monitor to see the status of all our
 servers, databases, and load distributers. This will help us manage if the services
-are running and allow us to track down any problems, if they arise. The other three
+are running and allow us to track down any problems, if they arise. Three
 servers are all running our server application and hosting the databases.
+We also have two final servers that we have setup as hot spares in the event
+of partial or total failure.
 Each server contains the server application that responds to clients as well as
-the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 3 servers. If
-we were to add a server, we would just need to update Riak and it would sync the
-databases to any additional servers as well. These servers, therefore, all contain
-the same information. If any servers go down, the distributed system would still
-run fine. We could have all servers go down except one and still be reliably
-handling requests.
+the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 5 servers.
+Note that the hot spares are setup to be part of the database cluster so they
+have a full copy of the database on hand, however they don't accept any reads
+or writes directly.
+With this configuratoin if we were to add a server, we would just need to update 
+Riak and it would sync the databases to any additional servers as well. These servers,
+therefore, all contain the same information. If any servers go down, the distributed
+system would still run fine. We could have all servers go down except one and still
+be reliably handling requests.
 \subsection {Traffic}
@@
 deeming it dead and removing it from its list of servers to direct clients towards.
-\subsection {Messages}
-We are currently using https protocol for our messages. This provides a secure
-and usable message system that we have conformed our client and server APIs to use.
-The actual message content is in the form of JSON objections \cite{json} 
+
 \subsection {Clients}
@@
 players, join public games, and compete in public games. The android client has
-he UI done for all the different activities. The android client successfully registers
-and logs in players.
+he UI done for all the different activities. The android client can successfully register
+and log players into games. We are actively adding features to both clients daily.
 
+\subsection {Messages}
+We are currently using https protocol for our messages. This provides a secure
+and usable messaging system that we have designed our client and server APIs to use.
+The actual messages are sent and received in two way's. Initially a user session key is
+genereated using the UUID \cite{uuid} algorithm and returned to the user on sucessful
+authenticaton. This session key is then passed back to the server with every in coming
+message. Messages are sent to the server using POST and GET request methods supported
+by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
+JSON is a small, easily parsable format, representing objects in a human readable format as
+they would be represented in JavaScript. With the web client the JSON object returned from
+the server is instantly useable, however for the android client we have to parse the JSON object
+into a native java object. The Android SDK provides libraries to do this, located in the
+org.json \cite{orgjson} package namespace.
 \section {What's Left}
@@
 Our system supports having any number of servers and allowing any subset of them to fail.
-We are using Riak, which supports a ''shared nothing' architecture.
-We can add a new server by joining it to our database and starting the web server.
-This can be done as many times as needed, allowing us to scale up our system.
-These same principles also give us great fault tolerance, since any server is capable of running independently.
-As long as one server is still up, the service will be available.
+We are using Riak, which supports a 'shared nothing' architecture.  We can add a new server
+by joining it to our database and starting the web server.  This can be done as many times
+as needed, allowing us to scale up our system.  These same principles also give us great fault
+tolerance, since any server is capable of running independently.  As long as one server is still
+up, the service will be available.
 
-We use round robin DNS to allow our clients to be completely ignorant of our servers.
-Load distributors can be added and removed from the DNS server and the clients will be completely ignorant of this and unaffected.
-The load distributors in turn know about our data servers and do their best to distribute the load across them.
-When a new server is added, it is just added to our load distributor configuration file and clients can start using it.
-When a server fails, the distributors will stop directing traffic to it.
+We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load distributors
+can be added and removed from the DNS server and the clients will be completely ignorant of this
+and unaffected.  The load distributors in turn know aboutour data servers and do their best to
+distribute the load across them.  When a new server is added, it is just added to our load distributor
+configuration file and clients can start using it.  When a server fails, the distributors will stop directing
+traffic to it.
 
-- Coordination/Cooperation (Synchronous Databases and Rounds consisting of many players)
-- Replication / Availability / Consistency (Riak handles synchronizing databases among servers. Load distributers provide availability)
-  < Needs stuff on Riak>
+We are currently using Riak as our database backend. We chose Riak for multiple
+reasons, but the biggest was it's focus on  scalability, fault-tolerance,
+availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
+database, it supports full masterless replication. In Riak every node can
+server client requests and they are propogated to the rest of the cluster.
+In our system we have made sure that this replication occurs's between nodes
+on Amazon EC2's internal Gigabit ethernet so it is as fast as possible. Riak
+also has the unique property that if all of the nodes but one fail, the single
+node can still accept both reads and writes to the database. When the other
+nodes return to operational state from failure, all changes will automatically
+be propogated to all of the nodes. This feature is the basis for our ability to
+support and recorver from partial failures. In the event that two Riak nodes accept
+writes from two seperate clients modifying the same data and Riak is unable
+to resolve the conflict the user is given both versions and allowed to resolve
+the conflict them selves. However we have configured our installation so this
+can not occur, we have specified that every available node must agree on a
+write before it is commited. Given the relatively small number of nodes (five)
+that will take part in this agreement, we decided that the possible overhead
+was acceptable for the increased level of consistency it gives us.
 
@@
 
-- Use of an interesting distributed algorithm
-
-\newpage
 %

### 2011-04-08 papers/phase-one/paper.tex
Changes to paper

@@
 distributed system. Getting the ground work done (for example servers and load
-distributers running) has provided us a way to quickly develop the clients
+sharers running) has provided us a way to quickly develop the clients
 and server as well as provided us with a way to reliably connect the servers to
@@
 host. We are able to login to the web-monitor to see the status of all our
-servers, databases, and load distributers. This will help us manage if the services
+servers, databases, and load sharers. This will help us manage if the services
 are running and allow us to track down any problems, if they arise. Three
@@
 or writes directly.
-With this configuratoin if we were to add a server, we would just need to update 
+With this configuration if we were to add a server, we would just need to update 
 Riak and it would sync the databases to any additional servers as well. These servers,
@@
 \subsection {Traffic}
-We have two load distributers set up. Both distributers are currently configured to
-divide the requests among the 3 active servers. The duplicate distributers allow
+We have two load sharers set up. Both sharers are currently configured to
+divide the requests among the three active servers. The duplicate sharers allow
 for a load distributer to go down and we would still be able to serve requests
-to the servers. These load distributers are selected by the clients using round
+to the servers. These load sharers are selected by the clients using round
 robin DNS where distrivia.lame.ws will select either load distributer that is
 up at random. This provides us will stability for access to the servers. The
-load distributers are set up the attempt to connect to a server twice before
+load sharers are setup to attempt to connect to a server twice before
 deeming it dead and removing it from its list of servers to direct clients towards.
@@
 \subsection {Messages}
-We are currently using https protocol for our messages. This provides a secure
+We are currently using the https protocol for our messages. This provides a secure
 and usable messaging system that we have designed our client and server APIs to use.
 The actual messages are sent and received in two way's. Initially a user session key is
-genereated using the UUID \cite{uuid} algorithm and returned to the user on sucessful
-authenticaton. This session key is then passed back to the server with every in coming
+generated using the UUID \cite{uuid} algorithm and returned to the user on successful
+authentication. This session key is then passed back to the server with every in coming
 message. Messages are sent to the server using POST and GET request methods supported
 by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
-JSON is a small, easily parsable format, representing objects in a human readable format as
+JSON is a small, easily parseable format, representing objects in a human readable format as
 they would be represented in JavaScript. With the web client the JSON object returned from
-the server is instantly useable, however for the android client we have to parse the JSON object
-into a native java object. The Android SDK provides libraries to do this, located in the
-org.json \cite{orgjson} package namespace.
+the server is instantly usable, however for the android client we have to parse the JSON object
+into a native Java object. The Android SDK provides libraries to do this, located in the
+org.json \cite{orgjson} package name space.
 \section {What's Left}
+\subsection {Server}
+The server is currently almost feature complete, but still needs a lot of
+testing. The only features it does not currently support is any sort of notion
+of a private game. Client registration, and login are all supported. A client can
+join a game, retrieve questions for that game, and answer questions. Both a
+global leader board and individual per game leader board can also be requested.
+As a group we have already found several inconsistencies and things we would
+like to change with how server API requests are structured. We have also thought of
+way's we can combine multiple requests into one, reducing the possible latency
+and overall communication time of multiple requests. To fix these
+inconsistencies members of the group worked to create a formal specification
+for the request protocol of each possible request. This allows the server and client
+programmers to work towards a common goal with out either making inappropriate
+assumptions about how the system will work. We are currently in the middle
+of refactoring the server to use the new requests detailed in the API.
+
 \subsection {Web Client}
-A lof of the main features of the web client are completed.
-However, there are stil a few remaining features that need to be implemented.
+A lot of the main features of the web client are completed.
+However, there are still a few remaining features that need to be implemented.
 The first is private games.
 Joining them has only been stubbed out with no functionality.
-The game playing routinees from public games should be compatible with private games, but may need a few tweeks as well.
-Next, while it currently supports a universal leaderboard, it also needs to be able to display one ingame.
-With the recent API changes, there are a few existing features which need to have thir API calls adjusted slightly.
+The game playing routines from public games should be compatible with private games, but may need a few tweaks as well.
+Next, while it currently supports a universal leader board, it also needs to be able to display one in game.
+With the recent API changes, there are a few existing features which need to have their API calls adjusted slightly.
 Another feature that needs to be finished is displaying useful warnings and error messages.
 While progress has been made on them and a reporting system has been built, messages still need to be fed into it.
-Lastly, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response, alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
+Lastly, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
+alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
 \subsection {Android}
@@
 and the server are working. This includes joining public/private rounds,
-competing in these rounds, and viewing leaderboards. While the UI is nearly
+competing in these rounds, and viewing leader boards. While the UI is nearly
 finished on the android client, nearly all of the connections to the servers
@@
 are in.
-\subsection {Server}
-Private game joining
-Global leaderboard
-
 \section {Meeting the Requirements}
@@
 The other is a web client which is specifically being tested on Desktop and Laptop
-browsers, however it may work on many handheld web browsers as well.
+browsers, however it may work on many hand held web browsers as well.
 
@@
 can be added and removed from the DNS server and the clients will be completely ignorant of this
-and unaffected.  The load distributors in turn know aboutour data servers and do their best to
+and unaffected.  The load sharers in turn know about our data servers and do their best to
 distribute the load across them.  When a new server is added, it is just added to our load distributor
@@
 availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
-database, it supports full masterless replication. In Riak every node can
-server client requests and they are propogated to the rest of the cluster.
-In our system we have made sure that this replication occurs's between nodes
+database, it supports full master less replication. In Riak every node can
+server client requests and they are propagated to the rest of the cluster.
+In our system we have made sure that this replication occurs between nodes
 on Amazon EC2's internal Gigabit ethernet so it is as fast as possible. Riak
@@
 nodes return to operational state from failure, all changes will automatically
-be propogated to all of the nodes. This feature is the basis for our ability to
-support and recorver from partial failures. In the event that two Riak nodes accept
-writes from two seperate clients modifying the same data and Riak is unable
+be propagated to all of the nodes. This feature is the basis for our ability to
+support and recover from partial failures. In the event that two Riak nodes accept
+writes from two separate clients modifying the same data and Riak is unable
 to resolve the conflict the user is given both versions and allowed to resolve
@@
 can not occur, we have specified that every available node must agree on a
-write before it is commited. Given the relatively small number of nodes (five)
+write before it is committed. Given the relatively small number of nodes (five)
 that will take part in this agreement, we decided that the possible overhead

### 2011-04-08 papers/phase-one/paper.tex
Add section about NGINX and EC2
Minor grammer edits to phase 1 paper

@@
 
-We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load distributors
+We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load sharers
 can be added and removed from the DNS server and the clients will be completely ignorant of this
 and unaffected.  The load sharers in turn know about our data servers and do their best to
-distribute the load across them.  When a new server is added, it is just added to our load distributor
-configuration file and clients can start using it.  When a server fails, the distributors will stop directing
+distribute the load across them.  When a new server is added, it is just added to our load sharer
+configuration file and clients can start using it.  When a server fails, the sharers will stop directing
 traffic to it.
@@
 availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
-database, it supports full master less replication. In Riak every node can
-server client requests and they are propagated to the rest of the cluster.
+database, it supports full masterless replication. In Riak every node can
+serve client requests and they are propagated to the rest of the cluster.
 In our system we have made sure that this replication occurs between nodes
@@
 
-Our team is taking a very proactive stance towards security. All of our machines are properly fire walled so that
+Our team is taking a very proactive stance towards security. All of our machines are properly firewalled so that
 outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
@@
 sent in clear text. Our group even found a SSL certificate authority who was willing to sign our SSL certificate for free. This gives
-us actual fully functional, authenticate able SSL infrastructure. In order to make sure that our system properly secures user information,
+us actual fully functional, authenticatable SSL infrastructure. In order to make sure that our system properly secures user information,
 we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/GameActivityBase.java
Committing alot of work towards the round activity.

@@ -10,19 +10,27 @@ import edu.rit.cs.distrivia.model.GameData;
  */
 public class GameActivityBase extends Activity {
 
-    private GameData gd;
+    public GameData gdata;
     private final String GAME_DATA = "game_data";
 
     @Override
     public void onCreate(final Bundle savedInstance) {
         super.onCreate(savedInstance);
-        this.gd = (GameData) getIntent().getExtras().getSerializable(GAME_DATA);
+        this.gdata = (GameData) getIntent().getExtras().getSerializable(
+                GAME_DATA);
     }
 
     @Override
     public void startActivity(final Intent i) {
-        i.putExtra(GAME_DATA, gd);
+        i.putExtra(GAME_DATA, gdata);
         super.startActivity(i);
     }
 
+    public GameData gameData() {
+        return gdata;
+    }
+
+    public void setGameData(GameData gd) {
+        this.gdata = gd;
+    }
 }

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/RoundActivity.java

@@ -1,9 +1,10 @@
 package edu.rit.cs.distrivia;
 
-import android.app.Activity;
 import android.content.Intent;
 import android.graphics.Color;
 import android.os.Bundle;
+import android.os.Handler;
+import android.os.Message;
 import android.os.SystemClock;
 import android.view.View;
 import android.view.View.OnClickListener;
@@ -12,16 +13,13 @@ import android.widget.Button;
 import android.widget.TextView;
 import android.widget.Toast;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
-import edu.rit.cs.distrivia.api.DistriviaAPIException;
 import edu.rit.cs.distrivia.api.Question;
-import edu.rit.cs.distrivia.model.GameData;
 
 /**
  * Activity for players to answer questions during a round.
  */
-public class RoundActivity extends Activity {
+public class RoundActivity extends GameActivityBase {
 
-    private GameData gdata;
     private long startTime = 0;
     private long stopTime = 0;
     private String selection = null;
@@ -31,9 +29,25 @@ public class RoundActivity extends Activity {
     private Button answerC;
     private Button answerD;
 
+    private final Handler loadHandler = new Handler() {
+        @Override
+        public void handleMessage(Message msg) {
+            if (gameData().isDone()) {
+                Intent i = new Intent();
+                i.setClassName("edu.rit.cs.distrivia",
+                        "edu.rit.cs.distrivia.LeaderboardActivity");
+                startActivity(i);
+            } else {
+                setupButtons(gameData().getQuestion());
+            }
+        }
+    };
+
     OnClickListener answerListener = new OnClickListener() {
         @Override
         public void onClick(final View v) {
+            stopTime = SystemClock.elapsedRealtime();
+
             deselectAll();
             final Button answer = (Button) v;
             answer.setSelected(true);
@@ -46,7 +60,6 @@ public class RoundActivity extends Activity {
                 selection = "c";
             else if (answer == answerD)
                 selection = "d";
-            stopTime = SystemClock.elapsedRealtime();
         }
     };
 
@@ -57,31 +70,18 @@ public class RoundActivity extends Activity {
         requestWindowFeature(Window.FEATURE_NO_TITLE);
         setContentView(R.layout.round);
 
-        // Intent in = getIntent();
-        // Serializable obj = in.getSerializableExtra(GameData.class.getName());
-        // GameData gameData = (GameData) obj;
-        // authToken = gameData.getAuthToken();
[…]

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java

@@ -28,8 +28,6 @@ import org.apache.http.impl.conn.SingleClientConnManager;
 import org.apache.http.message.BasicNameValuePair;
 import org.apache.http.params.BasicHttpParams;
 import org.apache.http.params.HttpParams;
-import org.json.JSONException;
-import org.json.JSONObject;
 
 import android.util.Log;
 import edu.rit.cs.distrivia.model.GameData;
@@ -152,101 +150,35 @@ public class DistriviaAPI {
     }
 
     /**
-     * API call to get the initial multiple choice question in a game.
-     * 
-     * @param authToken
-     *            The authorization token for this session, obtained at user
-     *            login.
-     * @param gameId
-     *            The identification string for this game.
-     * @return The next question in the game, or null if the game is over, or
-     *         error.
-     * @throws Exception
-     */
-    public static Question firstQuestion(final String authToken,
-            final String gameId) throws Exception {
-        return nextQuestion(authToken, gameId, "0");
-    }
-
-    /**
      * API call to get the next multiple choice question in a game.
      * 
-     * @param authToken
-     *            The authorization token for this session, obtained at user
-     *            login.
-     * @param gameId
-     *            The identification string for this game.
-     * @param prevId
-     *            The previous question id, just pass "0" if this is the initial
-     *            question fetch.
+     * @param gd
+     * @param answer
+     * @param time
      * 
      * @return The next question in the game, or null if the game is over.
      * @throws Exception
      */
-    public static Question nextQuestion(final String authToken,
-            final String gameId, final String prevId) throws Exception {
-
-        List<NameValuePair> params = new ArrayList<NameValuePair>();
-        params.add(new BasicNameValuePair("authToken", authToken));
+    public static GameData answer(final GameData gd, final String answer,
+            long time) throws Exception {
 
         String url = new String(API_URL);
-        url += "/game/" + gameId + "/next/" + prevId;
-
-        String data = post(url, params);
-
-        // Decompose JSON response into a Question object
-        Question nextQ = null;
-        try {
-            JSONObject json = new JSONObject(data);
-            nextQ = Question.create(json);
-        } catch (JSONException e) {
-            throw new DistriviaAPIException("Question request was malformed: ");
-        }
-
-        return nextQ;
-    }
-
-    /**
[…]

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/api/JSON.java

@@ -6,7 +6,7 @@ import org.json.JSONArray;
 import org.json.JSONException;
 import org.json.JSONObject;
 
-/*
+/**
  * Stores response information from a server request
  */
 public class JSON {
@@ -17,12 +17,19 @@ public class JSON {
 
     private final JSONObject json;
 
-    public JSON(String server_data) throws JSONException {
+    /**
+     * @param server_data
+     *            The string data to be parsed into json
+     * @throws JSONException
+     */
+    public JSON(final String server_data) throws JSONException {
         json = new JSONObject(server_data);
     }
 
     /**
      * Gets the status code of the request
+     * 
+     * @return
      */
     public int status() throws JSONException {
         return json.getInt("status");
@@ -31,7 +38,7 @@ public class JSON {
     /** Comparator for sorting the leader board */
     static class LeaderComparator implements Comparator<String[]> {
         @Override
-        public int compare(String[] o1, String[] o2) {
+        public int compare(final String[] o1, final String[] o2) {
             final int SCORE = 1;
             return Integer.parseInt(o2[SCORE]) - Integer.parseInt(o1[SCORE]);
         }
@@ -43,10 +50,10 @@ public class JSON {
     @SuppressWarnings("unchecked")
     public String[][] leaderboard() throws JSONException {
 
-        String[][] board = new String[json.length()][json.length()];
-        JSONArray a = json.names();
+        final String[][] board = new String[json.length()][json.length()];
+        final JSONArray a = json.names();
         for (int i = 0; i < a.length(); i++) {
-            String key = a.getString(i);
+            final String key = a.getString(i);
             board[i][0] = key;
             board[i][1] = json.getString(key);
         }
@@ -95,7 +102,7 @@ public class JSON {
      * Gets all the response options, in order
      */
     public String[] answers() throws JSONException {
-        String[] ans = new String[4];
+        final String[] ans = new String[4];
         ans[0] = a();
         ans[1] = b();
         ans[2] = c();
@@ -124,12 +131,12 @@ public class JSON {
         return json.getString("id");
     }
 
-    public static void main(String args[]) {
+    public static void main(final String args[]) {
         try {
-            JSON b = new JSON(
+            final JSON b = new JSON(
[…]

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/api/Question.java

@@ -1,7 +1,6 @@
 package edu.rit.cs.distrivia.api;
 
 import org.json.JSONException;
-import org.json.JSONObject;
 
 /**
  *
@@ -22,20 +21,21 @@ public class Question {
     /**
      * Factory method to create a question from JSON.
      * 
-     * @param arr
+     * @param parser
      *            The JSON object from the server.
      * @return A properly initialized question
      */
-    public static Question create(final JSONObject arr) {
+    public static Question create(JSON parser) {
         final Question q = new Question();
         try {
-            q.question = arr.getString("question");
-            q.choiceA = arr.getString("a");
-            q.choiceB = arr.getString("b");
-            q.choiceC = arr.getString("c");
-            q.choiceD = arr.getString("d");
-            q.id = arr.getString("id");
-        } catch (final JSONException e) {
+            q.question = parser.question();
+            q.choiceA = parser.a();
+            q.choiceB = parser.b();
+            q.choiceC = parser.c();
+            q.choiceD = parser.d();
+            q.id = parser.qid();
+        } catch (JSONException e) {
+            e.printStackTrace();
         }
         return q;
     }

### 2011-04-16 src/clients/android/src/edu/rit/cs/distrivia/model/GameData.java

@@ -2,6 +2,8 @@ package edu.rit.cs.distrivia.model;
 
 import java.io.Serializable;
 
+import edu.rit.cs.distrivia.api.Question;
+
 /**
  *
  */
@@ -12,6 +14,8 @@ public class GameData implements Serializable {
     private final String userName;
     private String gameID;
     private String status;
+    private int score;
+    private Question q;
 
     /**
      * Constuct a semi-immutable GameData object
@@ -77,5 +81,29 @@ public class GameData implements Serializable {
 
     public boolean isWaiting() {
         return status.equals("waiting");
+    }
+
+    public String getCurrentQid() {
+        if (q != null) {
+            return q.id();
+        } else {
+            return "0";
+        }
+    }
+
+    public int getScore() {
+        return score;
+    }
+
+    public void setScore(int score) {
+        this.score = score;
+    }
+
+    public void setQuestion(Question q) {
+        this.q = q;
+    }
+
+    public Question getQuestion() {
+        return this.q;
     }
 }

### 2011-04-16 papers/phase-two/paper.tex
Preliminary writeup for phase-two

--- 2011-04-08 papers/phase-one/paper.tex
@@
 \section {What We've Done}
-So far, our work has mainly focused on getting everything setup to work as a
-distributed system. Getting the ground work done (for example servers and load
-sharers running) has provided us a way to quickly develop the clients
-and server as well as provided us with a way to reliably connect the servers to
-the clients.
+Much of our system has been implemented and is in the debugging phase.
+The server apps and the web client are nearly complete with some revisions happening as necessary.
+The extent of what has been finished for each part of our system is explained below.
 \subsection {Servers}
-Currently, we have 6 servers running. One server is being used as a web-monitor
+Currently, we have 6 servers running on Amazon's Elastic Compute Cloud \cite{aec}. One server is being used as a web-monitor
 host. We are able to login to the web-monitor to see the status of all our
@@
 have a full copy of the database on hand, however they don't accept any reads
-or writes directly.
+or writes directly. This allows for them to immediately be ready for read/writes in the event that the original servers are down.
 With this configuration if we were to add a server, we would just need to update 
@@
 We have two load sharers set up. Both sharers are currently configured to
-divide the requests among the three active servers. The duplicate sharers allow
+divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
 for a load distributer to go down and we would still be able to serve requests
@@
 deeming it dead and removing it from its list of servers to direct clients towards.
+Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
+for our load sharing needs.
 
@@
 Our focus for clients has been on a web-based client and an android application.
-Both clients have most of the their screens completed. The web-based client will
+Both clients have most of the the workings completed. The web-based client will
 be run from desktop platforms and laptop platforms. The android client will run
-on any android phone and does not use any unique services that require specific
+on any android phone running OS 2.1 or higher and does not use any unique services that require specific
 hardware. The web client is nearly fully-functional. It currently can login/register
-players, join public games, and compete in public games. The android client has
-he UI done for all the different activities. The android client can successfully register
-and log players into games. We are actively adding features to both clients daily.
+players, view leaderboards, join public games, and compete in public games. The android client has UI done for all the different activities. The android client can successfully register
+and log players into games, view leaderboards, and join public games. We are actively adding features to both clients, daily.
 
@@
 However, there are still a few remaining features that need to be implemented.
-The first is private games.
-Joining them has only been stubbed out with no functionality.
-The game playing routines from public games should be compatible with private games, but may need a few tweaks as well.
-Next, while it currently supports a universal leader board, it also needs to be able to display one in game.
-With the recent API changes, there are a few existing features which need to have their API calls adjusted slightly.
-Another feature that needs to be finished is displaying useful warnings and error messages.
-While progress has been made on them and a reporting system has been built, messages still need to be fed into it.
-Lastly, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
+While private games are implemented on the server, 
+Also, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
 alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
 \subsection {Android}
+EVERYTHING
 So far, the only connection to the server that the android client has is when it
@@
 outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
-Our load balancer's automatically redirect http:// to https:// and once you are in https:// at the load balancer, SSL continues all the
+Our load sharer's automatically redirect http:// to https:// and once you are in https:// at the load sharer, SSL continues all the
 way back to our actual web application back end serving responses over a SSL wrapped socket. This way no passwords are ever
@@
 
+\newpage
 %

### 2011-04-16 papers/phase-two/paper.tex
Further updates to phase-two paper

@@
 be reliably handling requests.
+
+\subsection {Server Applications}
+The server is currently almost feature complete, but still needs a lot of
+testing. Client registration, and login are all supported. A client can
+join a game, retrieve questions for that game, and answer questions. Both a
+global leader board and individual per game leader board can also be requested.
+We recently refactored our API to be more universal.
+The servers and clients now work on a more consistent basis where the clients all expect the same information and use the same calls.
+
 \subsection {Traffic}
@@
 org.json \cite{orgjson} package name space.
+
 \section {What's Left}
 \subsection {Server}
-The server is currently almost feature complete, but still needs a lot of
-testing. The only features it does not currently support is any sort of notion
-of a private game. Client registration, and login are all supported. A client can
-join a game, retrieve questions for that game, and answer questions. Both a
-global leader board and individual per game leader board can also be requested.
-As a group we have already found several inconsistencies and things we would
-like to change with how server API requests are structured. We have also thought of
-way's we can combine multiple requests into one, reducing the possible latency
-and overall communication time of multiple requests. To fix these
-inconsistencies members of the group worked to create a formal specification
-for the request protocol of each possible request. This allows the server and client
-programmers to work towards a common goal with out either making inappropriate
-assumptions about how the system will work. We are currently in the middle
-of refactoring the server to use the new requests detailed in the API.
-
+The server is nearly completed. The server application just needs to have some tweaks and further testing.
 \subsection {Web Client}
@@
 \subsection {Android}
-EVERYTHING
-So far, the only connection to the server that the android client has is when it
-registers/logs in. We still need to connect the rest of the android client to
-the server API to make sure all the communication between the android client
-and the server are working. This includes joining public/private rounds,
-competing in these rounds, and viewing leader boards. While the UI is nearly
-finished on the android client, nearly all of the connections to the servers
-has yet to be done. Additionally, the android client needs to have more user
-feedback and increased ability for the users to control which activity they
-are in.
+We've started to thread the network calls to correctly register UI updates to the application.
+This is completed for most of the activities.
+There are really two big things left to implement on the android client: private games and competing in a round.
+Competing in a round is nearly finished, we just need to refresh the questions/answers and post the users answers to the server.
+Besides these two things, we just need to solidify the user interface, make it work with the back button with popping activities off the stack and other minor updates.
+
 \section {Meeting the Requirements}

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/GameActivityBase.java
Big update to the android client. Play now works.
- Refactor alot of the code to use the new features of
  GameActivityBase.

- Thread several parts of the user interface.

- Add some javadocs

- Remove dead or unused code

@@ -3,6 +3,9 @@ package edu.rit.cs.distrivia;
 import android.app.Activity;
 import android.content.Intent;
 import android.os.Bundle;
+import android.os.Handler;
+import android.os.Message;
+import android.widget.Toast;
 import edu.rit.cs.distrivia.model.GameData;
 
 /**
@@ -10,8 +13,55 @@ import edu.rit.cs.distrivia.model.GameData;
  */
 public class GameActivityBase extends Activity {
 
-    public GameData gdata;
+    /**  */
+    public final String LOGIN_ACTIVITY = "LoginActivity";
+    /**  */
+    public final String JOIN_ACTIVITY = "JoinActivity";
+    /**  */
+    public final String ROUND_ACTIVITY = "RoundActivity";
+    /**  */
+    public final String LEADERBOARD_ACTIVITY = "LeaderboardActivity";
+    /**  */
+    public final String ACTIVITY_ROOT = "edu.rit.cs.distrivia";
+
+    /** Game data storage for this activity */
+    public GameData gdata = null;
     private final String GAME_DATA = "game_data";
+
+    /** Handler to move onto the next Activity on successful login. */
+    private final Handler startHandler = new Handler() {
+        @Override
+        public void handleMessage(final Message msg) {
+            String className = msg.getData().getString("class");
+            Intent intent = new Intent();
+            intent.setClassName(ACTIVITY_ROOT, ACTIVITY_ROOT + "." + className);
+            startActivity(intent);
+        }
+    };
+
+    /** Handler to make toast notifications from the Networking thread. */
+    private final Handler toastHandler = new Handler() {
+        @Override
+        public void handleMessage(final Message msg) {
+            // Cancel the loading dialog since something obviously happened.
+            String txtmsg = msg.getData().getString("msg");
+            Toast.makeText(getApplicationContext(), txtmsg, 10).show();
+        }
+    };
+
+    /**
+     * Start the next activity
+     * 
+     * @param className
+     *            The class name to launch.
+     */
+    public void startActivity(final String className) {
+        Bundle data = new Bundle();
+        data.putString("class", className);
+        Message msg = new Message();
+        msg.setData(data);
+        startHandler.sendMessage(msg);
+    }
 
     @Override
     public void onCreate(final Bundle savedInstance) {
@@ -26,10 +76,33 @@ public class GameActivityBase extends Activity {
         super.startActivity(i);
     }
 
+    /**
+     * Toast the given text to the user, in the UI thread.
[…]

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java

@@ -1,8 +1,5 @@
 package edu.rit.cs.distrivia;
 
-import android.app.Activity;
-import android.content.Context;
-import android.content.Intent;
 import android.os.Bundle;
 import android.os.SystemClock;
 import android.view.View;
@@ -12,16 +9,14 @@ import android.widget.Button;
 import android.widget.EditText;
 import android.widget.LinearLayout;
 import android.widget.TextView;
-import android.widget.Toast;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
-import edu.rit.cs.distrivia.model.GameData;
 
 /**
  * Activity for players to answer questions during a round.
  */
-public class JoinActivity extends Activity {
+public class JoinActivity extends GameActivityBase {
 
-    GameData gd;
+    private final int UPDATE_MS = 5000;
 
     /** Called when the activity is first created. */
     @Override
@@ -29,32 +24,28 @@ public class JoinActivity extends Activity {
         super.onCreate(savedInstanceState);
         requestWindowFeature(Window.FEATURE_NO_TITLE);
         setContentView(R.layout.join);
-        gd = (GameData) getIntent().getExtras().getSerializable("game_data");
 
-        final Button joinPublicButton = (Button) findViewById(R.id.join_public_button);
-        final Button joinPrivateButton = (Button) findViewById(R.id.join_private_button);
-        final Button viewLeaderboardButton = (Button) findViewById(R.id.view_leaderboard_button);
-
+        final Button pubButton = (Button) findViewById(R.id.join_public_button);
+        final Button priButton = (Button) findViewById(R.id.join_private_button);
+        final Button lbButton = (Button) findViewById(R.id.view_leaderboard_button);
         final TextView playersLabel = (TextView) findViewById(R.id.num_players_text);
-
         final EditText privateName = (EditText) findViewById(R.id.private_name_text);
         final EditText privatePass = (EditText) findViewById(R.id.private_pass_text);
-
         final LinearLayout publicLayout = (LinearLayout) findViewById(R.id.public_layout);
         final LinearLayout privateLayout = (LinearLayout) findViewById(R.id.private_layout);
 
-        joinPublicButton.setOnClickListener(new OnClickListener() {
+        pubButton.setOnClickListener(new OnClickListener() {
             @Override
             public void onClick(final View v) {
                 privateLayout.setVisibility(View.GONE);
-                viewLeaderboardButton.setVisibility(View.GONE);
+                lbButton.setVisibility(View.GONE);
[…]

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/LeaderboardActivity.java

@@ -1,23 +1,21 @@
 package edu.rit.cs.distrivia;
 
-import android.app.Activity;
 import android.os.Bundle;
 import android.util.Log;
 import android.view.Window;
 import android.widget.TableLayout;
 import android.widget.TableRow;
 import android.widget.TextView;
-import android.widget.Toast;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
-import edu.rit.cs.distrivia.model.GameData;
 
 /**
  * Activity for players to answer questions during a round.
  */
-public class LeaderboardActivity extends Activity {
-
+public class LeaderboardActivity extends GameActivityBase {
+    final int USER = 0;
+    final int SCORE = 1;
+    final int NAME_WIDTH = 200;
     TableLayout leaderTable;
-    GameData gd;
 
     /** Called when the activity is first created. */
     @Override
@@ -26,36 +24,32 @@ public class LeaderboardActivity extends Activity {
         requestWindowFeature(Window.FEATURE_NO_TITLE);
         setContentView(R.layout.leaderboard);
 
-        gd = (GameData) getIntent().getExtras().getSerializable("game_data");
-
         leaderTable = (TableLayout) findViewById(R.id.leader_table);
         leaderTable.setStretchAllColumns(true);
         loadTable();
     }
 
     private void loadTable() {
-        final int USER = 0;
-        final int SCORE = 1;
+
         String[][] board = null;
         try {
-            board = DistriviaAPI.leaderBoard(gd);
+            board = DistriviaAPI.leaderBoard(gameData());
         } catch (Exception e) {
-            Toast.makeText(getApplicationContext(), "The network is DOWN!", 100)
-                    .show();
             Log.d("Load leaderboard: ", e.getMessage());
+            makeToast("The network is DOWN!");
             return;
         }
-        if (board == null) {
-            return;
-        }
+
         for (int i = 0; i < board.length; i++) {
             if (!board[i][USER].equals("status")) {
                 TableRow row = new TableRow(getApplicationContext());
                 TextView name = new TextView(getApplicationContext());
-                name.setText(board[i][USER]);
-                name.setWidth(200);
                 TextView score = new TextView(getApplicationContext());
+
+                name.setText(board[i][USER]);
+                name.setWidth(NAME_WIDTH);
                 score.setText(board[i][SCORE]);
+
                 row.addView(name);
                 row.addView(score);
                 leaderTable.addView(row);

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/LoginActivity.java

@@ -7,6 +7,7 @@ import android.content.SharedPreferences;
 import android.os.Bundle;
 import android.os.Handler;
 import android.os.Message;
+import android.util.Log;
 import android.view.KeyEvent;
 import android.view.View;
 import android.view.View.OnClickListener;
@@ -143,6 +144,7 @@ public class LoginActivity extends Activity {
         try {
             authToken = DistriviaAPI.login(name, passwd);
         } catch (Exception e) {
+            Log.d("login error:", e.getMessage());
             makeToast("Service is down, please try again later");
             return;
         }

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/RoundActivity.java

@@ -1,6 +1,5 @@
 package edu.rit.cs.distrivia;
 
-import android.content.Intent;
 import android.graphics.Color;
 import android.os.Bundle;
 import android.os.Handler;
@@ -13,7 +12,8 @@ import android.widget.Button;
 import android.widget.TextView;
 import android.widget.Toast;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
-import edu.rit.cs.distrivia.api.Question;
+import edu.rit.cs.distrivia.model.GameData;
+import edu.rit.cs.distrivia.model.Question;
 
 /**
  * Activity for players to answer questions during a round.
@@ -33,10 +33,7 @@ public class RoundActivity extends GameActivityBase {
         @Override
         public void handleMessage(Message msg) {
             if (gameData().isDone()) {
-                Intent i = new Intent();
-                i.setClassName("edu.rit.cs.distrivia",
-                        "edu.rit.cs.distrivia.LeaderboardActivity");
-                startActivity(i);
+                startActivity(LEADERBOARD_ACTIVITY);
             } else {
                 setupButtons(gameData().getQuestion());
             }
@@ -81,7 +78,6 @@ public class RoundActivity extends GameActivityBase {
             public void onClick(View v) {
                 if (selection != null) {
                     submitAndLoad();
-
                 } else {
                     Toast.makeText(v.getContext(), "Please select an answer",
                             10).show();
@@ -96,18 +92,18 @@ public class RoundActivity extends GameActivityBase {
 
         setupButtons(gameData().getQuestion());
 
-        // Store time which the screen stopped rendering.
-        startTime = SystemClock.elapsedRealtime();
     }
 
     private void submitAndLoad() {
-        final long decisionTime = stopTime - startTime;
+        final long time = stopTime - startTime;
         new Thread() {
             @Override
             public void run() {
+                // Submit answer/get next question
                 try {
-                    setGameData(DistriviaAPI.answer(gdata, selection,
-                            decisionTime));
+                    GameData gd = gameData();
+                    gd = DistriviaAPI.answer(gd, selection, time);
+                    setGameData(gd);
                 } catch (final Exception e) {
                     e.printStackTrace();
                     return;
@@ -128,6 +124,8 @@ public class RoundActivity extends GameActivityBase {
         answerC.setText("C: " + q.getChoiceC());
         answerD.setText("D: " + q.getChoiceD());
         deselectAll();
[…]

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java

@@ -17,7 +17,6 @@ import org.apache.http.NameValuePair;
 import org.apache.http.client.ClientProtocolException;
 import org.apache.http.client.HttpClient;
 import org.apache.http.client.entity.UrlEncodedFormEntity;
-import org.apache.http.client.methods.HttpGet;
 import org.apache.http.client.methods.HttpPost;
 import org.apache.http.client.methods.HttpRequestBase;
 import org.apache.http.conn.scheme.Scheme;
@@ -31,6 +30,7 @@ import org.apache.http.params.HttpParams;
 
 import android.util.Log;
 import edu.rit.cs.distrivia.model.GameData;
+import edu.rit.cs.distrivia.model.Question;
 
 /**
  * Main utility class which can talk to the Distrivia web service over
@@ -139,14 +139,13 @@ public class DistriviaAPI {
         String data = post(url, params);
         JSON jsonParser = new JSON(data);
 
-        // if ( jsonParser.status() == ) {
-
         gdata.setGameId(jsonParser.gameid());
         gdata.setStatus(jsonParser.gamestatus());
 
-        return gdata;
-        // }
+        Question q = Question.create(jsonParser);
+        gdata.setQuestion(q);
 
+        return gdata;
     }
 
     /**
@@ -184,14 +183,11 @@ public class DistriviaAPI {
     /**
      * API call to obtain the current leader board for a given game.
      * 
-     * @param authToken
-     *            The authorization token for this session, obtained at user
-     *            login.
-     * @param gameId
-     *            The unique identification string for the current game.
+     * @param gdata
      * 
      * @return The game leader board at the time of the query, or null if the
      *         gameId does not exist, or the user is not properly logged in.
+     * 
      * @throws Exception
      */
     public static String[][] leaderBoard(final GameData gdata) throws Exception {
@@ -217,13 +213,6 @@ public class DistriviaAPI {
         if (params != null) {
             op.setEntity(new UrlEncodedFormEntity(params));
         }
-        HttpResponse response = executeRequest(op);
-        String data = responseToString(response);
-        return data;
-    }
-
-    private static String get(final String url) throws Exception {
-        HttpGet op = new HttpGet(url);
         HttpResponse response = executeRequest(op);
         String data = responseToString(response);
         return data;

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/api/JSON.java

@@ -29,7 +29,9 @@ public class JSON {
     /**
      * Gets the status code of the request
      * 
-     * @return
+     * @return The status code
+     * 
+     * @throws JSONException
      */
     public int status() throws JSONException {
         return json.getInt("status");
@@ -45,9 +47,13 @@ public class JSON {
     }
 
     /**
-     * Gets an array of leaderboard data
+     * Gets an array of leader board data
+     * 
+     * @return Sorted leader board in 2D array format. The first position is the
+     *         Username, the score is the second position.
+     * 
+     * @throws JSONException
      */
-    @SuppressWarnings("unchecked")
     public String[][] leaderboard() throws JSONException {
 
         final String[][] board = new String[json.length()][json.length()];

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/model/GameData.java

@@ -2,7 +2,6 @@ package edu.rit.cs.distrivia.model;
 
 import java.io.Serializable;
 
-import edu.rit.cs.distrivia.api.Question;
 
 /**
  *
@@ -18,7 +17,7 @@ public class GameData implements Serializable {
     private Question q;
 
     /**
-     * Constuct a semi-immutable GameData object
+     * Construct a GameData object
      * 
      * @param authToken
      *            Auth token logged in with
@@ -67,22 +66,37 @@ public class GameData implements Serializable {
         return authToken;
     }
 
-    public void setStatus(String gamestatus) {
+    /**
+     * @param gamestatus
+     */
+    public void setStatus(final String gamestatus) {
         status = gamestatus;
     }
 
+    /**
+     * @return True if the game is just starting
+     */
     public boolean hasStarted() {
         return status.equals("started");
     }
 
+    /**
+     * @return True if game is done, false other wise.
+     */
     public boolean isDone() {
         return status.equals("done");
     }
 
+    /**
+     * @return true if waiting, false other wise
+     */
     public boolean isWaiting() {
         return status.equals("waiting");
     }
 
+    /**
+     * @return the current question id
+     */
     public String getCurrentQid() {
         if (q != null) {
             return q.id();
@@ -91,18 +105,35 @@ public class GameData implements Serializable {
         }
     }
 
+    /**
+     * @return The current score in the game
+     */
     public int getScore() {
         return score;
     }
 
-    public void setScore(int score) {
+    /**
+     * @param score
+     */
+    public void setScore(final int score) {
         this.score = score;
     }
 
-    public void setQuestion(Question q) {
+    /**
+     * Set the current question in the game object.
+     * 
+     * @param q
+     *            The question to update with
+     */
+    public void setQuestion(final Question q) {
         this.q = q;
     }
 
+    /**
+     * Get current question
+     * 
+     * @return Return the question object
+     */
     public Question getQuestion() {
         return this.q;
     }

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/model/Leaderboard.java

@@ -1,4 +1,4 @@
-package edu.rit.cs.distrivia.api;
+package edu.rit.cs.distrivia.model;
 
 import java.util.ArrayList;
 import java.util.List;

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/model/Question.java

@@ -1,11 +1,20 @@
-package edu.rit.cs.distrivia.api;
+package edu.rit.cs.distrivia.model;
+
+import java.io.Serializable;
 
 import org.json.JSONException;
+
+import edu.rit.cs.distrivia.api.JSON;
 
 /**
  *
  */
-public class Question {
+public class Question implements Serializable {
+
+    /**
+     * Serializeable UID
+     */
+    private static final long serialVersionUID = 2103199974823935456L;
 
     private String id;
     private String question;
@@ -25,7 +34,7 @@ public class Question {
      *            The JSON object from the server.
      * @return A properly initialized question
      */
-    public static Question create(JSON parser) {
+    public static Question create(final JSON parser) {
         final Question q = new Question();
         try {
             q.question = parser.question();
@@ -34,7 +43,7 @@ public class Question {
             q.choiceC = parser.c();
             q.choiceD = parser.d();
             q.id = parser.qid();
-        } catch (JSONException e) {
+        } catch (final JSONException e) {
             e.printStackTrace();
         }
         return q;

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java
Add progress bar to android app, fix login buttons on back.

@@ -108,4 +108,5 @@ public class JoinActivity extends GameActivityBase {
             }
         }.start();
     }
+
 }

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/LoginActivity.java

@@ -82,7 +82,7 @@ public class LoginActivity extends Activity {
         loginBut.setOnClickListener(new OnClickListener() {
             @Override
             public void onClick(final View v) {
-                disableButtons();
+                toggleButtons();
                 launchEvent(ButtonAction.LOGIN_EVENT);
             }
         });
@@ -91,7 +91,7 @@ public class LoginActivity extends Activity {
         registerBut.setOnClickListener(new OnClickListener() {
             @Override
             public void onClick(final View v) {
-                disableButtons();
+                toggleButtons();
                 launchEvent(ButtonAction.REGISTER_EVENT);
             }
         });
@@ -102,7 +102,7 @@ public class LoginActivity extends Activity {
             public boolean onKey(View v, int keyCode, KeyEvent event) {
                 if ((event.getAction() == KeyEvent.ACTION_DOWN)
                         && (keyCode == KeyEvent.KEYCODE_ENTER)) {
-                    disableButtons();
+                    toggleButtons();
                     launchEvent(ButtonAction.LOGIN_EVENT);
                     return true;
                 }
@@ -111,11 +111,13 @@ public class LoginActivity extends Activity {
         });
     }
 
-    private void disableButtons() {
-        loginBut.setEnabled(false);
-        registerBut.setEnabled(false);
-        loginBut.invalidate();
-        registerBut.invalidate();
+    private void toggleButtons() {
+        if (loginBut != null) {
+            loginBut.setEnabled(!loginBut.isEnabled());
+            registerBut.setEnabled(!registerBut.isEnabled());
+            loginBut.invalidate();
+            registerBut.invalidate();
+        }
     }
 
     private void launchEvent(final ButtonAction action) {
@@ -207,5 +209,22 @@ public class LoginActivity extends Activity {
         Message msg = new Message();
         msg.setData(data);
         toastHandler.sendMessage(msg);
+    }
+
+    /**
+     * @param bd
+     */
+    @Override
+    public void onResume() {
+        super.onResume();
+        if (!loginBut.isEnabled()) {
+            toggleButtons();
+        }
+    }
+
+    @Override
+    public void onBackPressed() {
+        super.onBackPressed();
+        toggleButtons();
     }
 }

### 2011-04-17 src/clients/android/src/edu/rit/cs/distrivia/RoundActivity.java

@@ -9,6 +9,7 @@ import android.view.View;
 import android.view.View.OnClickListener;
 import android.view.Window;
 import android.widget.Button;
+import android.widget.ProgressBar;
 import android.widget.TextView;
 import android.widget.Toast;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
@@ -28,6 +29,7 @@ public class RoundActivity extends GameActivityBase {
     private Button answerB;
     private Button answerC;
     private Button answerD;
+    private ProgressBar pbar;
 
     private final Handler loadHandler = new Handler() {
         @Override
@@ -40,11 +42,25 @@ public class RoundActivity extends GameActivityBase {
         }
     };
 
+    private final Handler pbarHandler = new Handler() {
+        public void handlemessage(Message msg) {
+
+        }
+    };
+
+    private final Runnable updateProgress = new Runnable() {
+        @Override
+        public void run() {
+            pbar.incrementProgressBy(1000);
+            pbarHandler.postDelayed(updateProgress, 500);
+        }
+    };
+
     OnClickListener answerListener = new OnClickListener() {
         @Override
         public void onClick(final View v) {
             stopTime = SystemClock.elapsedRealtime();
-
+            pbarHandler.removeCallbacks(updateProgress);
             deselectAll();
             final Button answer = (Button) v;
             answer.setSelected(true);
@@ -67,11 +83,14 @@ public class RoundActivity extends GameActivityBase {
         requestWindowFeature(Window.FEATURE_NO_TITLE);
         setContentView(R.layout.round);
 
+        pbar = (ProgressBar) findViewById(R.id.seekBar);
+        pbar.setMax(10000);
         question = (TextView) findViewById(R.id.question);
         answerA = (Button) findViewById(R.id.answer1_button);
         answerB = (Button) findViewById(R.id.answer2_button);
         answerC = (Button) findViewById(R.id.answer3_button);
         answerD = (Button) findViewById(R.id.answer4_button);
+
         Button submit = (Button) findViewById(R.id.answer_submit_button);
         submit.setOnClickListener(new OnClickListener() {
             @Override
@@ -126,6 +145,10 @@ public class RoundActivity extends GameActivityBase {
         deselectAll();
         // Store time which the screen stopped rendering.
         startTime = SystemClock.elapsedRealtime();
+
+        pbar.setProgress(0);
+        pbarHandler.removeCallbacks(updateProgress);
+        pbarHandler.postDelayed(updateProgress, 1000);
     }
 
     /**

### 2011-04-20 src/clients/iphone/distrivia/Classes/GameData.h
Add simple stupid game data object to be passed around.

@@ -1,0 +1,31 @@
+//
+//  GameData.h
+//  distrivia
+//
+//  Created by Brian Gianforcaro on 4/20/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import <Foundation/Foundation.h>
+
+
+@interface GameData : NSObject {
+ NSString * status;
+ NSString * token;
+ NSString * username;
+ int score;
+}
+- (BOOL) hasStarted;
+
+- (BOOL) isDone;
+
+- (int) getScore;
+
+- (NSString*) getUser;
+
+- (void) setScore:(int)score;
+
+- (void) setStatus:(NSString*) status;
+
+- (void) setUser:(NSString*) user;
+@end

### 2011-04-20 src/clients/iphone/distrivia/Classes/GameData.m

@@ -1,0 +1,53 @@
+//
+//  GameData.m
+//  distrivia
+//
+//  Created by Brian Gianforcaro on 4/20/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import "GameData.h"
+
+
+@implementation GameData
+
+- (id) init {
+    
+    status = nil;
+    username = nil;
+    score = 0;
+    
+    
+    return self;
+}
+
+- (BOOL) hasStarted {
+    return [status isEqualToString:@"starting"];
+}
+
+- (BOOL) isDone {
+    return [status isEqual:@"done"];
+}
+
+- (int) getScore {
+    return score;
+}
+
+- (NSString*) getUser {
+    return username;
+}
+
+- (void) setScore:(int) newScore {
+    score = newScore;
+}
+
+- (void) setStatus:(NSString*) newStatus {
+    [newStatus retain];
+    status = newStatus;
+}
+
+- (void) setUser:(NSString*) user {
+    [user retain];
+    username = user;
+}
+@end

### 2011-04-20 src/clients/iphone/distrivia/DistriviaAPI.h
Start the framework for a API which let's the user just call the API methods with a delegate.

@@ -1,0 +1,20 @@
+//
+//  DistriviaAPI.h
+//  distrivia
+//
+//  Created by Brian Gianforcaro on 4/20/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import <Foundation/Foundation.h>
+
+@class GameData;
+
+
+@interface DistriviaAPI : NSObject
+
++ (BOOL) loginWithData:(GameData*)gd user: (NSString*) userName pass: (NSString*)pass delegate:(id) loginDelegate;
+
++ (NSMutableURLRequest*) createPost:(NSString*) post urlFrag: (NSString*) urlFragment;
+
+@end

### 2011-04-20 src/clients/iphone/distrivia/DistriviaAPI.m

@@ -1,0 +1,57 @@
+//
+//  DistriviaAPI.m
+//  distrivia
+//
+//  Created by Brian Gianforcaro on 4/20/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import "DistriviaAPI.h"
+#import "GameData.h"
+
+@implementation DistriviaAPI
+
+const static NSString* API_URL = @"https://distrivia.lame.ws";
+
++ (BOOL) loginWithData:(GameData*) gd user:(NSString*) userName pass:(NSString*) pass delegate:(id) loginDelegate{ 
+    
+    NSString* fragment = [NSString stringWithFormat: @"/login/%@", userName];
+    
+    NSString* post = [NSString stringWithFormat:@"&pass=%@", pass];
+    
+    NSURLRequest* request = [DistriviaAPI createPost: post urlFrag: fragment];
+    
+    NSURLConnection *conn = [[NSURLConnection alloc]initWithRequest:request delegate: loginDelegate];
+    
+    
+    if ( conn ) {
+        return true;
+    } else {
+        return false;
+    }
+}
+
++ (NSMutableURLRequest*) createPost:(NSString*) post urlFrag: (NSString*)urlFragment {
+    
+    // Combine host url with API fragment 
+    NSURL* url = [NSURL URLWithString: 
+                    [NSString stringWithFormat:@"%@%@", API_URL, urlFragment]];
+    
+    // URL Encode our post data
+    NSData* data = [post dataUsingEncoding: NSASCIIStringEncoding 
+                             allowLossyConversion: YES];
+    NSString* len = [NSString stringWithFormat:@"%d",[data length]];
+    
+    NSMutableURLRequest *request = [[[NSMutableURLRequest alloc] init] autorelease];
+
+    [request setURL: url];
+    [request setHTTPMethod:@"POST"];
+    [request setHTTPBody:data];
+    [request setValue:len forHTTPHeaderField:@"Content-Length"];
+    [request setValue:@"application/x-www-form-urlencoded" 
+             forHTTPHeaderField:@"Current-Type"];
+    
+
+    return request;
+}
+@end

### 2011-04-20 src/clients/iphone/distrivia/Classes/GameData.h
Make game data stuff private

@@ -10,10 +10,11 @@
 
 
 @interface GameData : NSObject {
- NSString * status;
- NSString * token;
- NSString * username;
- int score;
+@private
+    NSString * status;
+    NSString * token;
+    NSString * username;
+    int score;
 }
 - (BOOL) hasStarted;
 

### 2011-04-21 src/clients/android/src/edu/rit/cs/distrivia/LeaderboardActivity.java
Added Create/Join Private Buttons to Android and fixed bug in exiting global leaderboard to stop updateThread

@@ -76,7 +76,9 @@ public class LeaderboardActivity extends GameActivityBase {
             @Override
             public void onClick(View v) {
                 // Stop I/O thread
-                updateThread.stop();
+            	if (updateThread != null) {
+            		updateThread.stop();
+            	}
 
                 GameData gd = gameData();
                 gd.setLoadLocal(false);

### 2011-04-21 src/clients/android/src/edu/rit/cs/distrivia/LeaderboardActivity.java
Attempt to pimp the leaderboard a little bit.

@@ -6,10 +6,12 @@ import android.os.Handler;
 import android.os.Message;
 import android.os.SystemClock;
 import android.util.Log;
+import android.view.Gravity;
 import android.view.View;
 import android.view.View.OnClickListener;
 import android.view.Window;
 import android.widget.Button;
+import android.widget.ImageView;
 import android.widget.TableLayout;
 import android.widget.TableRow;
 import android.widget.TextView;
@@ -38,17 +40,40 @@ public class LeaderboardActivity extends GameActivityBase {
             for (int i = 0; i < board.length; i++) {
                 if (!board[i][USER].equals("status")) {
                     TableRow row = new TableRow(getApplicationContext());
+
+                    if (i % 2 == 0) {
+                        row.setBackgroundResource(R.drawable.black);
+                    } else {
+                        row.setBackgroundResource(R.drawable.gray);
+                    }
                     TextView name = new TextView(getApplicationContext());
                     TextView score = new TextView(getApplicationContext());
 
                     name.setText(board[i][USER]);
                     name.setWidth(NAME_WIDTH);
+                    name.setTextSize(25);
+                    name.setGravity(Gravity.CENTER_VERTICAL);
                     score.setText(board[i][SCORE]);
+                    score.setTextSize(25);
+                    score.setGravity(Gravity.CENTER_VERTICAL);
                     if (board[i][USER].equals(userName)) {
                         name.setTextColor(Color.GREEN);
                         score.setTextColor(Color.GREEN);
                     }
 
+                    ImageView iv = new ImageView(getBaseContext());
+
+                    iv.setImageDrawable(getResources().getDrawable(
+                            R.drawable.user));
+
+                    /*
+                     * LayoutParams p = new LayoutParams(); p.width =
+                     * android.view.ViewGroup.LayoutParams.FILL_PARENT;
+                     * name.setLayoutParams(p); iv.setLayoutParams(p); //
+                     * score.setLayoutParams(p);
+                     */
+                    iv.setPadding(4, 0, 4, 0);
+                    row.addView(iv);
                     row.addView(name);
                     row.addView(score);
                     leaderTable.addView(row);
@@ -66,7 +91,7 @@ public class LeaderboardActivity extends GameActivityBase {
 
         final Button okBut = (Button) findViewById(R.id.lead_complete);
         leaderTable = (TableLayout) findViewById(R.id.leader_table);
-        leaderTable.setStretchAllColumns(true);
[…]

### 2011-04-21 papers/phase-two/paper.tex
Minor edit, unversal to universally consistent.
Added Readme for Phase 2
Updated paper to reflect changes this week and to involve iPhone client

@@
 %\begin{abstract}
-%In this paper we detail our initial idea for a distributed trivia game.
-%We will explain general game play idea's as well as an example of the
-%possible architecture for our system.
+%In this paper we detail our current progress on our distributed trivia game.
+%We will explain what has been done so far, what we need to do, and how we
+%have met the requirements for the project. We also discuss the architecture
+%for our system.
 %\end{abstract}
@@
 Much of our system has been implemented and is in the debugging phase.
-The server apps and the web client are nearly complete with some revisions happening as necessary.
+The server apps, web client, and android client are nearly complete with some revisions happening as necessary.
+We have also started development on an application for the iPhone platform.
 The extent of what has been finished for each part of our system is explained below.
+
+\subsection{Architecture Overview }
+\begin{figure}[h!]
+  \centering
+    \includegraphics[scale=0.4]{diagram.png}
+   \caption{High level overview of the system}
+ \end{figure}
+
 \subsection {Servers}
@@
 global leader board and individual per game leader board can also be requested.
-We recently refactored our API to be more universal.
+We recently refactored our API to be more universally consistent.
 The servers and clients now work on a more consistent basis where the clients all expect the same information and use the same calls.
@@
 on any android phone running OS 2.1 or higher and does not use any unique services that require specific
-hardware. The web client is nearly fully-functional. It currently can login/register
-players, view leaderboards, join public games, and compete in public games. The android client has UI done for all the different activities. The android client can successfully register
-and log players into games, view leaderboards, and join public games. We are actively adding features to both clients, daily.
+hardware. Both clients are nearly fully-functional. They can, currently, login/register
+players, view leaderboards, join public games, and compete in public games. We are actively adding features to both clients, daily.
+We have also started development on an iPhone application for distrivia. This client does not yet communicate with the server, but 
+it does implement nearly all the views seen in the other clients. We have been setting up the network communication for the iPhone
+platform as well.
 
@@
 \subsection {Android}
-We've started to thread the network calls to correctly register UI updates to the application.
-This is completed for most of the activities.
-There are really two big things left to implement on the android client: private games and competing in a round.
-Competing in a round is nearly finished, we just need to refresh the questions/answers and post the users answers to the server.
-Besides these two things, we just need to solidify the user interface, make it work with the back button with popping activities off the stack and other minor updates.
+Private gameplay is the largest thing left for the android client. Besides this we've just been fixing bugs and cleaning up the UI.
+\subsection {iPhone}
+The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
+to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
+and competing in rounds.
 
@@
 
-Our system has two unique clients. One of them is designed for the Android platform as an app.
-The other is a web client which is specifically being tested on Desktop and Laptop
+Our system has three unique clients. One of them is designed for the Android platform as an app.
+Another is designed for the iPhone platform as a native app.
+The third is a web client, which is specifically being tested on Desktop and Laptop
 browsers, however it may work on many hand held web browsers as well.

### 2011-04-21 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java
Added private API Calls and drastically changed join screen to accomodate all functions of private games

@@ -5,9 +5,11 @@ import android.os.SystemClock;
 import android.view.View;
 import android.view.View.OnClickListener;
 import android.view.Window;
+import android.widget.ArrayAdapter;
 import android.widget.Button;
 import android.widget.EditText;
 import android.widget.LinearLayout;
+import android.widget.Spinner;
 import android.widget.TextView;
 import edu.rit.cs.distrivia.api.DistriviaAPI;
 
@@ -32,7 +34,13 @@ public class JoinActivity extends GameActivityBase {
         final EditText privateName = (EditText) findViewById(R.id.private_name_text);
         final EditText privatePass = (EditText) findViewById(R.id.private_pass_text);
         final LinearLayout publicLayout = (LinearLayout) findViewById(R.id.public_layout);
-        final LinearLayout privateLayout = (LinearLayout) findViewById(R.id.private_layout);
+        final LinearLayout privateLayout = (LinearLayout) findViewById(R.id.private_layout); 
+        final Spinner spinner = (Spinner) findViewById(R.id.private_qnum_spin);
+        
+        ArrayAdapter<CharSequence> adapter = ArrayAdapter.createFromResource(
+                this, R.array.qnum_array, android.R.layout.simple_spinner_item);
+        adapter.setDropDownViewResource(android.R.layout.simple_spinner_dropdown_item);
+        spinner.setAdapter(adapter);
 
         pubButton.setOnClickListener(new OnClickListener() {
             @Override

### 2011-04-21 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java

@@ -128,15 +128,18 @@ public class DistriviaAPI {
      * Joins Private Round
      * 
      * @param gdata
+     * @param gameName
+     * @param pass
      * @return The game id string
      * @throws Exception
      */
-    public static GameData joinPrivate(GameData gdata) throws Exception {
+    public static GameData joinPrivate(GameData gdata, String gameName, String pass) throws Exception {
         String url = new String();
-        url += "/private/join";
+        url += "/private/join/"+gameName;
 
         List<NameValuePair> params = new ArrayList<NameValuePair>();
         params.add(new BasicNameValuePair("authToken", gdata.getAuthToken()));
+        params.add(new BasicNameValuePair("password", pass));
         params.add(new BasicNameValuePair("user", gdata.getUserName()));
 
         String data = post(url, params);
@@ -145,6 +148,52 @@ public class DistriviaAPI {
         gdata.setGameId(jsonParser.gameid());
 
         return gdata;
+    }
+    
+    /**
+     * Creates Private Round
+     * 
+     * @param gdata
+     * @param gameName
+     * @param pass
+     * @param numQs
+     * @return The game id string
+     * @throws Exception
+     */
+    public static GameData createPrivate(GameData gdata, String gameName, String pass, int numQs) throws Exception {
+        String url = new String();
+        url += "/private/create/"+numQs;
+
+        List<NameValuePair> params = new ArrayList<NameValuePair>();
+        params.add(new BasicNameValuePair("authToken", gdata.getAuthToken()));
+        params.add(new BasicNameValuePair("name", gameName));
+        params.add(new BasicNameValuePair("password", pass));
+        params.add(new BasicNameValuePair("user", gdata.getUserName()));
+
+        String data = post(url, params);
+        JSON jsonParser = new JSON(data);
+
+        gdata.setGameId(jsonParser.gameid());
+
+        return gdata;
+    }
+    
+    /**
+     * Starts Private Round
+     * 
+     * @param gdata
+     * @return True if game started, false otherwise
+     * @throws Exception
+     */
+    public static boolean startPrivate(GameData gdata) throws Exception {
+        String url = new String();
+        url += "/private/start/"+gdata.getGameID();
+
+        List<NameValuePair> params = new ArrayList<NameValuePair>();
+        params.add(new BasicNameValuePair("authToken", gdata.getAuthToken()));
+
+        String data = post(url, params);
+        return data.equals("ok");
     }
 
     /**

### 2011-04-21 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java
Added a question (will add more) and tweaked the Android Spinner

@@ -41,6 +41,7 @@ public class JoinActivity extends GameActivityBase {
                 this, R.array.qnum_array, android.R.layout.simple_spinner_item);
         adapter.setDropDownViewResource(android.R.layout.simple_spinner_dropdown_item);
         spinner.setAdapter(adapter);
+        spinner.setSelection(1);
 
         pubButton.setOnClickListener(new OnClickListener() {
             @Override

### 2011-04-21 src/server/db/insert-questions.py

@@ -7,6 +7,8 @@ client = riak.RiakClient()
 # 
 # Questions are from: 
 # http://www.diva-girl-parties-and-stuff.com/art-trivia.html
+# and
+# http://www.appsychology.com/HowPass/MC%20quizes/MCquizeshome.htm
 #
 
 questions = client.bucket('questions')
@@ -192,3 +194,15 @@ q = {
 entry = questions.new( "art-15", data = q )
 entry.store()
 
+
+q = {
+ "question" : "Computer programs capable of doing things that require intelligence when done by people are associated with",
+ "a" : "Artificial Intelligence",
+ "b" : "Proxemics",
+ "c" : "Cerebronic",
+ "d" : "Computerized Creativity",
+ "answer" : "a"
+}
+
+entry = questions.new( "art-15", data = q )
+entry.store()

### 2011-04-21 src/server/db/insert-questions.py
Added more cognition questions

@@ -204,5 +204,161 @@ q = {
  "answer" : "a"
 }
 
-entry = questions.new( "art-15", data = q )
+entry = questions.new( "cog-1", data = q )
+entry.store()
+
+
+q = {
+ "question" : "__________ is the study of the meaning of words and language",
+ "a" : "Linguistics",
+ "b" : "Encoding",
+ "c" : "Semantics",
+ "d" : "Syntax",
+ "answer" : "c"
+}
+
+entry = questions.new( "cog-2", data = q )
+entry.store()
+
+
+q = {
+ "question" : "Representations used in thinking include",
+ "a" : "Mnemonic devices",
+ "b" : "Kinesthesis",
+ "c" : "Concepts",
+ "d" : "Primarily figments of the imagination",
+ "answer" : "c"
+}
+
+entry = questions.new( "cog-3", data = q )
+entry.store()
+
+
+q = {
+ "question" : "Basic speech sounds are called",
+ "a" : "Morphemes",
+ "b" : "Syllables",
+ "c" : "Phonemes",
+ "d" : "Syntax",
+ "answer" : "c"
+}
+
+entry = questions.new( "cog-4", data = q )
+entry.store()
+
+
+q = {
+ "question" : "A solution that correctly states the requirements for success in solving a problem but not in sufficient detail for further action is called a(n) ________ solution",
+ "a" : "Heuristic",
+ "b" : "General",
+ "c" : "Functional",
+ "d" : "Specific",
+ "answer" : "b"
+}
+
+entry = questions.new( "cog-5", data = q )
+entry.store()
+
+
+q = {
+ "question" : "Fluency, flexibility, and originality would be most characteristic of which type of thought?",
+ "a" : "Convergent thinking",
+ "b" : "Mechanical problem-solving",
+ "c" : "Rote problem-solving",
+ "d" : "Brainstorming",
+ "answer" : "d"
+}
+
+entry = questions.new( "cog-6", data = q )
+entry.store()
+
+
+q = {
+ "question" : "What type of concept is \'uncle\'",
+ "a" : "Conjunctive",
+ "b" : "Relational",
+ "c" : "Relative",
+ "d" : "Disjunctive",
+ "answer" : "b"
+}
+
+entry = questions.new( "cog-7", data = q )
+entry.store()
+
+
+q = {
+ "question" : "The inability to see new uses for familiar objects is termed",
+ "a" : "Non-flexible thinking",
[…]

### 2011-04-21 src/clients/iphone/distrivia/Classes/JoinViewController.h
Fancied up join screen for iphone and added stuff to get keyboards to drop and added another activity indicator

@@ -13,17 +13,27 @@
 
 @interface JoinViewController : UIViewController <RoundViewControllerDelegate> {
 
-	IBOutlet UIButton	*pubButton;
-    IBOutlet UIButton   *priButton;
-    IBOutlet UIButton   *leadButton;
+	IBOutlet UIButton	*pubBut;
+    IBOutlet UIButton   *priJoinBut;
+    IBOutlet UIButton   *priCreateBut;
+    IBOutlet UIButton   *leadBut;
+    IBOutlet UITextField    *nameField;
+    IBOutlet UITextField    *passField;
+    IBOutlet UIActivityIndicatorView    *activeIndicate;
 	
 }
 
 @property (nonatomic, assign) id <JoinViewControllerDelegate> delegate;
-@property (nonatomic, retain) IBOutlet UIButton *pubButton;
-@property (nonatomic, retain) IBOutlet UIButton *priButton;
-@property (nonatomic, retain) IBOutlet UIButton *leadButton;
+@property (nonatomic, retain) IBOutlet UIButton *pubBut;
+@property (nonatomic, retain) IBOutlet UIButton *priJoinBut;
+@property (nonatomic, retain) IBOutlet UIButton *priCreateBut;
+@property (nonatomic, retain) IBOutlet UIButton *leadBut;
+@property (nonatomic, retain) IBOutlet UITextField *nameField;
+@property (nonatomic, retain) IBOutlet UITextField *passField;
+@property (nonatomic, retain) IBOutlet UIActivityIndicatorView *activeIndicate;
 
 - (IBAction) joinPublic:(id)sender;
+- (IBAction) textFieldDoneEditing:(id)sender;
+- (IBAction) backgroundTap:(id)sender;
 
 @end

### 2011-04-21 src/clients/iphone/distrivia/Classes/JoinViewController.m

@@ -12,9 +12,13 @@
 @implementation JoinViewController
 
 @synthesize delegate;
-@synthesize pubButton;
-@synthesize priButton;
-@synthesize leadButton;
+@synthesize pubBut;
+@synthesize priJoinBut;
+@synthesize priCreateBut;
+@synthesize leadBut;
+@synthesize nameField;
+@synthesize passField;
+@synthesize activeIndicate;
 
 // The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
 /*
@@ -33,16 +37,18 @@
     UIImage *buttonImageNormal = [UIImage imageNamed:@"whiteButton.png"];
     UIImage *stretchableButtonImageNormal = [buttonImageNormal stretchableImageWithLeftCapWidth:12 
                                                                                    topCapHeight:0];
-    [priButton setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
-    [pubButton setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
-    [leadButton setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
+    [priJoinBut setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
+    [priCreateBut setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
+    [pubBut setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
+    [leadBut setBackgroundImage:stretchableButtonImageNormal forState:UIControlStateNormal];
     
     UIImage *buttonImagePressed = [UIImage imageNamed:@"blueButton.png"];
     UIImage *stretchableButtonImagePressed = [buttonImagePressed stretchableImageWithLeftCapWidth:12 
                                                                                      topCapHeight:0];
-    [priButton setBackgroundImage:stretchableButtonImagePressed forState:UIControlStateHighlighted];
-    [pubButton setBackgroundImage:stretchableButtonImagePressed forState:UIControlStateHighlighted];
-    [leadButton setBackgroundImage:stretchableButtonImagePressed forState:UIControlStateHighlighted];
+    [priJoinBut setBackgroundImage:stretchableButtonImagePressed forState:UIControlStateHighlighted];
[…]

### 2011-04-21 src/clients/iphone/distrivia/Classes/LeaderboardViewController.h
Oops, forgot to add the leaderboard stuff

@@ -1,0 +1,16 @@
+//
+//  LeaderboardViewController.h
+//  distrivia
+//
+//  Created by Sticky Glazer on 4/21/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import <UIKit/UIKit.h>
+
+
+@interface LeaderboardViewController : UIViewController {
+
+}
+
+@end

### 2011-04-21 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -1,0 +1,59 @@
+//
+//  LeaderboardViewController.m
+//  distrivia
+//
+//  Created by Sticky Glazer on 4/21/11.
+//  Copyright 2011 Rochester Institute of Technology. All rights reserved.
+//
+
+#import "LeaderboardViewController.h"
+
+
+@implementation LeaderboardViewController
+
+// The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
+/*
+- (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
+    self = [super initWithNibName:nibNameOrNil bundle:nibBundleOrNil];
+    if (self) {
+        // Custom initialization.
+    }
+    return self;
+}
+*/
+
+/*
+// Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
+- (void)viewDidLoad {
+    [super viewDidLoad];
+}
+*/
+
+/*
+// Override to allow orientations other than the default portrait orientation.
+- (BOOL)shouldAutorotateToInterfaceOrientation:(UIInterfaceOrientation)interfaceOrientation {
+    // Return YES for supported orientations.
+    return (interfaceOrientation == UIInterfaceOrientationPortrait);
+}
+*/
+
+- (void)didReceiveMemoryWarning {
+    // Releases the view if it doesn't have a superview.
+    [super didReceiveMemoryWarning];
+    
+    // Release any cached data, images, etc. that aren't in use.
+}
+
+- (void)viewDidUnload {
+    [super viewDidUnload];
+    // Release any retained subviews of the main view.
+    // e.g. self.myOutlet = nil;
+}
+
+
+- (void)dealloc {
+    [super dealloc];
+}
+
+
+@end

### 2011-04-21 src/clients/iphone/distrivia/Classes/JoinViewController.h
Various updates for iphone including leaderboard format and how the buttons in a round react

@@ -8,6 +8,7 @@
 
 #import <UIKit/UIKit.h>
 #import "RoundViewController.h"
+#import "LeaderboardViewController.h"
 
 @protocol JoinViewControllerDelegate;
 
@@ -33,6 +34,7 @@
 @property (nonatomic, retain) IBOutlet UIActivityIndicatorView *activeIndicate;
 
 - (IBAction) joinPublic:(id)sender;
+- (IBAction) viewLeaderboard:(id)sender;
 - (IBAction) textFieldDoneEditing:(id)sender;
 - (IBAction) backgroundTap:(id)sender;
 

### 2011-04-21 src/clients/iphone/distrivia/Classes/JoinViewController.m

@@ -61,6 +61,16 @@
 }
 */
 
+- (IBAction) viewLeaderboard:(id)sender {
+	LeaderboardViewController *controller = [[LeaderboardViewController alloc]
+											 initWithNibName:@"LeaderboardView" 
+											 bundle:nil];
+	controller.modalTransitionStyle = UIModalTransitionStyleCoverVertical;
+	[self presentModalViewController:controller animated:YES];
+	
+	[controller release];
+}
+
 - (IBAction)joinPublic:(id)sender {
 	RoundViewController *controller = [[RoundViewController alloc] initWithNibName:@"RoundView" bundle:nil];
 	controller.delegate = self;

### 2011-04-21 src/clients/iphone/distrivia/Classes/LeaderboardViewController.h

@@ -10,7 +10,10 @@
 
 
 @interface LeaderboardViewController : UIViewController {
-
+	IBOutlet UITableView	*boardView;
+	
 }
+
+@property (retain, nonatomic) IBOutlet UITableView *boardView;
 
 @end

### 2011-04-21 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -11,6 +11,8 @@
 
 @implementation LeaderboardViewController
 
+@synthesize boardView;
+
 // The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
 /*
 - (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
@@ -22,12 +24,12 @@
 }
 */
 
-/*
+
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
     [super viewDidLoad];
 }
-*/
+
 
 /*
 // Override to allow orientations other than the default portrait orientation.
@@ -45,13 +47,14 @@
 }
 
 - (void)viewDidUnload {
+	self.boardView = nil;
     [super viewDidUnload];
     // Release any retained subviews of the main view.
-    // e.g. self.myOutlet = nil;
 }
 
 
 - (void)dealloc {
+	[boardView release];
     [super dealloc];
 }
 

### 2011-04-21 src/clients/iphone/distrivia/Classes/RoundViewController.h

@@ -12,9 +12,24 @@
 
 @interface RoundViewController : UIViewController {
 
+	IBOutlet UILabel	*question;
+	IBOutlet UIButton	*aBut;
+	IBOutlet UIButton	*bBut;
+	IBOutlet UIButton	*cBut;
+	IBOutlet UIButton	*dBut;
+	
+	
 }
 
 @property (nonatomic, assign) id <RoundViewControllerDelegate> delegate;
+@property (nonatomic, retain) IBOutlet UILabel *question;
+@property (nonatomic, retain) IBOutlet UIButton *aBut;
+@property (nonatomic, retain) IBOutlet UIButton *bBut;
+@property (nonatomic, retain) IBOutlet UIButton *cBut;
+@property (nonatomic, retain) IBOutlet UIButton *dBut;
+
+- (IBAction) answerSelected:(id)sender;
+- (void) deselectAll;
 
 
 @end

### 2011-04-21 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -12,6 +12,11 @@
 @implementation RoundViewController
 
 @synthesize delegate;
+@synthesize question;
+@synthesize aBut;
+@synthesize bBut;
+@synthesize cBut;
+@synthesize dBut;
 
 // The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
 /*
@@ -24,12 +29,13 @@
 }
 */
 
-/*
+
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
+	[self deselectAll];
     [super viewDidLoad];
 }
-*/
+
 
 /*
 // Override to allow orientations other than the default portrait orientation.
@@ -38,6 +44,29 @@
     return (interfaceOrientation == UIInterfaceOrientationPortrait);
 }
 */
+
+- (IBAction) answerSelected:(id)sender {
+	[self deselectAll];
+	if (sender == aBut) {
+		[aBut setBackgroundColor:[UIColor greenColor]];
+	}
+	else if (sender == bBut) {
+		[bBut setBackgroundColor:[UIColor greenColor]];
+	}
+	else if (sender == cBut) {
+		[cBut setBackgroundColor:[UIColor greenColor]];
+	}
+	else if (sender == dBut) {
+		[dBut setBackgroundColor:[UIColor greenColor]];
+	}
+}
+
+- (void) deselectAll {
+	[aBut setBackgroundColor:[UIColor grayColor]];
+	[bBut setBackgroundColor:[UIColor grayColor]];
+	[cBut setBackgroundColor:[UIColor grayColor]];
+	[dBut setBackgroundColor:[UIColor grayColor]];
+}
 
 - (void)didReceiveMemoryWarning {
     // Releases the view if it doesn't have a superview.
@@ -49,11 +78,21 @@
 - (void)viewDidUnload {
     // Release any retained subviews of the main view.
 	self.delegate = nil;
+	self.question = nil;
+	self.aBut = nil;
+	self.bBut = nil;
+	self.cBut = nil;
+	self.dBut = nil;
     [super viewDidUnload];
 }
 
 
 - (void)dealloc {
+	[question release];
+	[aBut release];
+	[bBut release];
+	[cBut release];
+	[dBut release];
     [super dealloc];
 }
 

### 2011-04-22 papers/phase-two/paper.tex
Fix double the
Updated Whats Left for web client

@@
 However, there are still a few remaining features that need to be implemented.
-While private games are implemented on the server, 
-Also, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
-alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
+The only major feature remaining is private games, which are largely unstarted, although it will reuse most of the public game code.
+In addition to this, buttons should be disabled when clicked to prevent users from spamming the server with repeat messages.
 \subsection {Android}

### 2011-04-22 papers/phase-two/paper.tex
Minor tweaks. Caps Android, fix bcrypt spellling add Monit

@@
 Much of our system has been implemented and is in the debugging phase.
-The server apps, web client, and android client are nearly complete with some revisions happening as necessary.
+The server application, web client, and Android client are nearly complete with some revisions happening as necessary.
 We have also started development on an application for the iPhone platform.
@@
 Currently, we have 6 servers running on Amazon's Elastic Compute Cloud \cite{aec}. One server is being used as a web-monitor
-host. We are able to login to the web-monitor to see the status of all our
-servers, databases, and load sharers. This will help us manage if the services
+host running Monit\cite{monit}. We are able to login to the web-monitor to see the status of all our
+servers, databases, and load sharers. This will help us manage whether or not the services
 are running and allow us to track down any problems, if they arise. Three
@@
 \subsection {Clients}
-Our focus for clients has been on a web-based client and an android application.
-Both clients have most of the the workings completed. The web-based client will
-be run from desktop platforms and laptop platforms. The android client will run
-on any android phone running OS 2.1 or higher and does not use any unique services that require specific
+Our focus for clients has been on a web-based client and an Android application.
+Both clients have most of the workings completed. The web-based client will
+be run from desktop platforms and laptop platforms. The Android client will run
+on any Android phone running OS 2.1 or higher and does not use any unique services that require specific
 hardware. Both clients are nearly fully-functional. They can, currently, login/register
@@
 they would be represented in JavaScript. With the web client the JSON object returned from
-the server is instantly usable, however for the android client we have to parse the JSON object
+the server is instantly usable, however for the Android client we have to parse the JSON object
 into a native Java object. The Android SDK provides libraries to do this, located in the
@@
 \subsection {Android}
-Private gameplay is the largest thing left for the android client. Besides this we've just been fixing bugs and cleaning up the UI.
+Private gameplay is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the UI.
 \subsection {iPhone}
@@
 we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using
-the cryptographically secure hashing function designed for passwords known as bcyrpt \cite{bcrypt}.
+the cryptographically secure hashing function designed for passwords known as bcrypt \cite{bcrypt}.
 

### 2011-04-22 papers/phase-two/paper.tex
Fix typos, add more about round robin dns, UI -> user interface

@@
 Brian Gianforcaro \\
-       \affaddr{Rochester Institue of Technology}\\
+       \affaddr{Rochester Institute of Technology}\\
        \email{bjg1955@rit.edu}
@@
 Steven Glazer \\
-       \affaddr{Rochester Institue of Technology}\\
+       \affaddr{Rochester Institute of Technology}\\
        \email{sfg6126@rit.edu}
@@
 Samuel Milton \\
-       \affaddr{Rochester Institue of Technology}\\
+       \affaddr{Rochester Institute of Technology}\\
        \email{srm2997@rit.edu}
@@
 robin DNS where distrivia.lame.ws will select either load distributer that is
-up at random. This provides us will stability for access to the servers. The
-load sharers are setup to attempt to connect to a server twice before
-deeming it dead and removing it from its list of servers to direct clients towards.
+up at random. If a load distributer should go down or become unreachable the
+DNS service will no longer serve that hosts DNS record until it is again
+reachable. This provides us with stability for accessing the servers. The
+load sharers are setup to attempt to connect to a server twice in a one second
+period before deeming it dead and removing it from its list of servers to direct clients towards.
 Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
@@
 The actual messages are sent and received in two way's. Initially a user session key is
-generated using the UUID \cite{uuid} algorithm and returned to the user on successful
+generated using the UUID\cite{uuid} algorithm and returned to the user on successful
 authentication. This session key is then passed back to the server with every in coming
@@
 \subsection {Android}
-Private gameplay is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the UI.
+Private game play is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the
+user interface.
 \subsection {iPhone}
-The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
+The iPhone application just started development in the last couple days. We
+have built most of the user interface but need to connect all of the actions
 to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
@@
 
-Our system has three unique clients. One of them is designed for the Android platform as an app.
-Another is designed for the iPhone platform as a native app.
+Our system has three unique clients. One of them is designed for the Android
+platform as an application.
+Another is designed for the iPhone platform as a native application.
 The third is a web client, which is specifically being tested on Desktop and Laptop

### 2011-04-22 src/server/distrivia.py
Fix typo in flask roue template

@@ -481,7 +481,7 @@ def private_join_game():
     else:
         return json.dumps({"status":3})
 
-@app.route('/private/create/<int:numqestions>', methods=["POST"])
+@app.route('/private/create/<int:numquestions>', methods=["POST"])
 def private_new_create(numquestions):
     """
     URL /private/create

### 2011-04-22 src/server/server.py
Auto update on new file changes

@@ -1,6 +1,7 @@
 from tornado.wsgi import WSGIContainer
 from tornado.httpserver import HTTPServer
 from tornado.ioloop import IOLoop
+import tornado.autoreload
 import tornado.options
 from distrivia import app
 
@@ -19,4 +20,5 @@ tornado.options.parse_command_line()
 wsgiApp = WSGIContainer(app)
 http_server = HTTPServer(wsgiApp, ssl_options=ssl_files)
 http_server.listen(443)
-IOLoop.instance().start()
+ioloop = IOLoop.instance()
+tornado.autoreload.start(ioloop)

### 2011-04-22 src/clients/web/distrivia.js
Fixed leaderboard after games on web client. Started private games too

@@ -87,6 +87,7 @@ function Hide(){
       board_shown = false;
       byId('game_list').innerHTML = "";
    }
+   window.clearInterval(updater);
 }
 // End Hide()
 
@@ -141,7 +142,7 @@ function Cancel(){
 /*
  * Polls the server while waiting to join a game
  */
-function CheckStatus(){
+function CheckStatus( postgame ){
    var xr = XML();
 
    xr.onreadystatechange = function(){
@@ -160,7 +161,9 @@ function CheckStatus(){
             }
             list.innerHTML = scores;
                
-            if( data.gamestatus == 'waiting' ){
+            if( postgame ){
+               // Do nothing at postgame
+            }else if( data.gamestatus == 'waiting' ){
                // Game hasn't started
                // TODO (probably nothing)
 
@@ -172,7 +175,6 @@ function CheckStatus(){
 
             }else if( data.gamestatus == 'done' ){
                // Game is finished
-               // TODO
                window.clearInterval(updater);
             }
 
@@ -230,8 +232,13 @@ function Next(){
                      byId('game_list').innerHTML = scores;
                   }else if( data.gamestatus == 'done' ){
                      swap( game, join );
-//                     var scoreb = byId('game_board');
-//                     $(scoreb).animate({width:"hide"});
+                     var scores = "";
+                     for( key in data.leaderboard ){
+                        scores += "<li class='board_item'><div class='board_left'>" + key + "</div>";
+                        scores += "<div class='board_right'>" + data.leaderboard[key] + "</div></li>";
+                     }
+                     byId('game_list').innerHTML = scores;
+                     updater = window.setInterval("CheckStatus(true)",5000);
                   }
                }else{
                   // TODO Check status code
@@ -357,9 +364,81 @@ function Home(){
 
 
 /*
+ * Creates a private game
+ */
+function Make(){
+   var xr = XML();
+   var xml_n = ++xr_n;
+   xr.onreadystatechange = function(){
+      if( xr.readyState == 4 && xml_n == xr_n ){
+         if( xr.status == 200 ){
+           try{
+              var data = jsonify( xr.responseText );
+               
+               if( data.status == -1 ){
+                  swap( join, login );
+                  errMsg( "Your session expired." );
+               }else if( data.status == 1 ){
+                  $( byId('num_q') ).hide("slow");
+                  $( byId('gconfirm') ).hide("slow");
[…]

### 2011-04-22 src/server/server.py
Revert autoreload

@@ -20,5 +20,4 @@ tornado.options.parse_command_line()
 wsgiApp = WSGIContainer(app)
 http_server = HTTPServer(wsgiApp, ssl_options=ssl_files)
 http_server.listen(443)
-ioloop = IOLoop.instance()
-tornado.autoreload.start(ioloop)
+IOLoop.instance().start()

### 2011-04-23 src/server/distrivia.py
Updated joining private game status codes on backend

@@ -477,9 +477,9 @@ def private_join_game():
                 game.store()
                 return json.dumps({ "id": key, "status":1 })
 
-        return json.dumps({"status":3})
+        return json.dumps({"status":-3})
     else:
-        return json.dumps({"status":3})
+        return json.dumps({"status":-2})
 
 @app.route('/private/create/<int:numquestions>', methods=["POST"])
 def private_new_create(numquestions):

### 2011-04-23 papers/phase-two/paper.tex

@@
 reachable. This provides us with stability for accessing the servers. The
-load sharers are setup to attempt to connect to a server twice in a one second
+load sharers are set up to attempt to connect to a server twice in a one second
 period before deeming it dead and removing it from its list of servers to direct clients towards.

### 2011-04-23 src/clients/android/src/edu/rit/cs/distrivia/JoinActivity.java
Started implementing create/join game for Android. Getting error messages, will check out later. I'm sure I did something wrong

@@ -28,7 +28,8 @@ public class JoinActivity extends GameActivityBase {
         setContentView(R.layout.join);
 
         final Button pubButton = (Button) findViewById(R.id.join_public_button);
-        final Button priButton = (Button) findViewById(R.id.join_private_button);
+        final Button priJoinButton = (Button) findViewById(R.id.join_private_button);
+        final Button priCreateButton = (Button) findViewById(R.id.create_private_button);
         final Button lbButton = (Button) findViewById(R.id.view_leaderboard_button);
         final TextView playersLabel = (TextView) findViewById(R.id.num_players_text);
         final EditText privateName = (EditText) findViewById(R.id.private_name_text);
@@ -54,7 +55,7 @@ public class JoinActivity extends GameActivityBase {
             }
         });
 
-        priButton.setOnClickListener(new OnClickListener() {
+        priJoinButton.setOnClickListener(new OnClickListener() {
             @Override
             public void onClick(final View v) {
                 String name = privateName.getText().toString().trim();
@@ -62,14 +63,31 @@ public class JoinActivity extends GameActivityBase {
                 if (!name.equals("") && !pass.equals("")) {
                     publicLayout.setVisibility(View.GONE);
                     v.setEnabled(false);
-                    v.invalidate();
-                    playersLabel.setText("Players: 10/20");
-                    startActivity(ROUND_ACTIVITY);
-                    finish();
+                    priCreateButton.setEnabled(false);
+                    playersLabel.setText("Waiting to join private game...");
+                    joinPrivate(name, pass);
                 } else {
                     makeToast("Enter name and pass");
                 }
             }
+        });
+        
+        priCreateButton.setOnClickListener(new OnClickListener() {
+        	@Override
+        	public void onClick(final View v) {
+        		String name = privateName.getText().toString().trim();
+                String pass = privatePass.getText().toString().trim();
+                if (!name.equals("") && !pass.equals("")) {
+                    publicLayout.setVisibility(View.GONE);
+                    v.setEnabled(false);
+                    priJoinButton.setEnabled(false);
+                    playersLabel.setText("Press Start Game when you're ready to begin...");
+                    int numQs = Integer.parseInt((String)spinner.getSelectedItem());
+                    createPrivate(name, pass, numQs);
+                } else {
+                    makeToast("Enter name and pass");
+                }
+        	}
         });
 
[…]

### 2011-05-03 src/clients/iphone/distrivia/Classes/DistriviaAPI.h
iPhone: Fixed the answer submissions for the round so it successfully competes in a round. Also made the progress bar update with the time left to answer for points

@@ -19,7 +19,7 @@
 + (BOOL) registerWithData:(GameData*)gd user:(NSString*)userName pass:(NSString*)pass;
 + (BOOL) joinPublicWithData:(GameData*)gd;
 + (BOOL) statusWithData:(GameData*)gd;
-+ (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(double)time;
++ (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(int)time;
 
 + (NSMutableURLRequest*) createPost:(NSString*)post urlFrag:(NSString*)urlFragment;
 

### 2011-05-03 src/clients/iphone/distrivia/Classes/DistriviaAPI.m

@@ -173,10 +173,10 @@ const static NSString* API_ERROR=@"err";
 }
 
 // Commits user's answer to the server and gets the next information
-+ (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(double)time {
++ (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(int)time {
     NSString* fragment = [NSString stringWithFormat: @"/game/%@/question/%@", [gd gameId], [[gd question] qid]];
     NSLog(@"API Answer Submission: %@", fragment);
-    NSString* timeString = [NSString stringWithFormat:@"%f", time];
+    NSString* timeString = [NSString stringWithFormat:@"%d", time];
     NSLog(@"API Time: %@", timeString);
     NSString* post = [NSString stringWithFormat:@"authToken=%@&user=%@&time=%@&a=%@", [gd getToken], 
                       [gd username], timeString, answer];

### 2011-05-03 src/clients/iphone/distrivia/Classes/RoundViewController.h

@@ -51,6 +51,8 @@
 - (void) submitAnswer;
 - (void) submitAnswerFailed;
 - (void) nextQuestion;
+- (void) updateProgress;
+- (void) progressUpdater;
 
 
 @end

### 2011-05-03 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -96,7 +96,7 @@
     [score setText:newScore];
     [self deselectAll];
     [self setStartTime:[[NSDate alloc] init]];
-    
+    [NSThread detachNewThreadSelector:@selector(progressUpdater) toTarget:self withObject:nil];
 }
 
 - (void) deselectAll {
@@ -108,8 +108,10 @@
 
 - (void) submitAnswer {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
+    int timeTaken = [[NSNumber numberWithFloat:[endTime timeIntervalSinceDate:startTime]] intValue];
+    NSLog(@"Time Taken: %d", timeTaken);
     if ([DistriviaAPI answerWithData:[rootController gd] answer:selection 
-                           timeTaken:[endTime timeIntervalSinceDate:startTime]]) {
+                           timeTaken:timeTaken]) {
         [self performSelectorOnMainThread:@selector(nextQuestion) withObject:nil waitUntilDone:NO];
     } else {
         [self performSelectorOnMainThread:@selector(submitAnswerFailed) withObject:nil waitUntilDone:NO];
@@ -133,6 +135,21 @@
                                       otherButtonTitles: nil];
     [e show];
     [e release];
+}
+
+- (void) progressUpdater {
+    NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
+    for (int i = 0; i<22; i++) {
+        [self performSelectorOnMainThread:@selector(updateProgress) withObject:nil waitUntilDone:NO];
+        [NSThread sleepForTimeInterval:0.25];
+    }
+    [pool release];
+}
+
+- (void) updateProgress {
+    NSDate *now = [[NSDate alloc] init];
+    [pBar setProgress:[now timeIntervalSinceDate:startTime]/5.0];
+    [now release];
 }
 
 - (void)didReceiveMemoryWarning {

### 2011-05-03 src/clients/iphone/distrivia/Classes/RoundViewController.m
iPhone: progress bar now pauses once selection is made and updates on new selection

@@ -76,6 +76,7 @@
 		[dBut setBackgroundColor:[UIColor greenColor]];
         [self setSelection:@"d"];
 	}
+    [self updateProgress];
 }
 
 - (IBAction) submitPressed:(id)sender {
@@ -100,6 +101,7 @@
 }
 
 - (void) deselectAll {
+    self.selection = nil;
 	[aBut setBackgroundColor:[UIColor grayColor]];
 	[bBut setBackgroundColor:[UIColor grayColor]];
 	[cBut setBackgroundColor:[UIColor grayColor]];
@@ -140,7 +142,9 @@
 - (void) progressUpdater {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     for (int i = 0; i<22; i++) {
-        [self performSelectorOnMainThread:@selector(updateProgress) withObject:nil waitUntilDone:NO];
+        if (selection == nil) {
+            [self performSelectorOnMainThread:@selector(updateProgress) withObject:nil waitUntilDone:NO];
+        }
         [NSThread sleepForTimeInterval:0.25];
     }
     [pool release];

### 2011-05-03 src/clients/iphone/distrivia/Classes/DistriviaAPI.m
iPhone: Updates score during round play

@@ -175,11 +175,9 @@ const static NSString* API_ERROR=@"err";
 // Commits user's answer to the server and gets the next information
 + (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(int)time {
     NSString* fragment = [NSString stringWithFormat: @"/game/%@/question/%@", [gd gameId], [[gd question] qid]];
-    NSLog(@"API Answer Submission: %@", fragment);
-    NSString* timeString = [NSString stringWithFormat:@"%d", time];
-    NSLog(@"API Time: %@", timeString);
-    NSString* post = [NSString stringWithFormat:@"authToken=%@&user=%@&time=%@&a=%@", [gd getToken], 
-                      [gd username], timeString, answer];
+    //NSString* timeString = [NSString stringWithFormat:@"%d", time];
+    NSString* post = [NSString stringWithFormat:@"authToken=%@&user=%@&time=%d&a=%@", [gd getToken], 
+                      [gd username], time, answer];
     NSLog(@"API Post: %@", post);
     NSURLRequest* request = [DistriviaAPI createPost:post urlFrag:fragment];
     NSError* error = nil;
@@ -201,8 +199,10 @@ const static NSString* API_ERROR=@"err";
             if ([gd hasStarted]) {
                 Question *q = [[Question alloc] initWithDict:items];
                 [gd setQuestion:q];
-                NSLog(@"API Question: %@", [[gd question] question]);
                 [q release];
+                [gd setScore:[[[items objectForKey:@"leaderboard"] objectForKey:[gd username]] intValue]];
+            } else{
+                //Set Leaderboard
             }
             success = true;
         } else {

### 2011-05-03 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -58,7 +58,6 @@
 
 - (IBAction) answerSelected:(id)sender {
     [self setEndTime:[[NSDate alloc] init]];
-    NSLog(@"Time: %f", [endTime timeIntervalSinceDate:startTime]/1);
 	[self deselectAll];
 	if (sender == aBut) {
 		[aBut setBackgroundColor:[UIColor greenColor]];
@@ -111,7 +110,6 @@
 - (void) submitAnswer {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     int timeTaken = [[NSNumber numberWithFloat:[endTime timeIntervalSinceDate:startTime]] intValue];
-    NSLog(@"Time Taken: %d", timeTaken);
     if ([DistriviaAPI answerWithData:[rootController gd] answer:selection 
                            timeTaken:timeTaken]) {
         [self performSelectorOnMainThread:@selector(nextQuestion) withObject:nil waitUntilDone:NO];

### 2011-05-04 src/clients/iphone/distrivia/Classes/RoundViewController.h
iPhone: Change score color depending on correctness and complete round

@@ -53,6 +53,7 @@
 - (void) nextQuestion;
 - (void) updateProgress;
 - (void) progressUpdater;
+- (void) roundFinished;
 
 
 @end

### 2011-05-04 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -93,6 +93,11 @@
     [cBut setTitle:[q choiceC] forState:UIControlStateNormal];
     [dBut setTitle:[q choiceD] forState:UIControlStateNormal];
     NSString *newScore = [NSString stringWithFormat:@"%d", [[rootController gd] getScore]];
+    if ([newScore isEqualToString:[score text]]) {
+        [score setTextColor:[UIColor redColor]];
+    } else {
+        [score setTextColor:[UIColor greenColor]];
+    }
     [score setText:newScore];
     [self deselectAll];
     [self setStartTime:[[NSDate alloc] init]];
@@ -109,10 +114,15 @@
 
 - (void) submitAnswer {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
-    int timeTaken = [[NSNumber numberWithFloat:[endTime timeIntervalSinceDate:startTime]] intValue];
+    int timeTaken = [[NSNumber numberWithFloat:[endTime timeIntervalSinceDate:startTime]*1000] intValue];
     if ([DistriviaAPI answerWithData:[rootController gd] answer:selection 
                            timeTaken:timeTaken]) {
-        [self performSelectorOnMainThread:@selector(nextQuestion) withObject:nil waitUntilDone:NO];
+        if ([[rootController gd] hasStarted]) {
+            [self performSelectorOnMainThread:@selector(nextQuestion) withObject:nil waitUntilDone:NO];
+        } else {
+            [self performSelectorOnMainThread:@selector(roundFinished) withObject:nil waitUntilDone:NO];
+        }
+
     } else {
         [self performSelectorOnMainThread:@selector(submitAnswerFailed) withObject:nil waitUntilDone:NO];
     }
@@ -152,6 +162,11 @@
     NSDate *now = [[NSDate alloc] init];
     [pBar setProgress:[now timeIntervalSinceDate:startTime]/5.0];
     [now release];
+}
+         
+- (void) roundFinished {
+    [activeIndicate stopAnimating];
+    [rootController switchToView:[rootController LEADERBOARD]];
 }
 
 - (void)didReceiveMemoryWarning {

### 2011-05-04 src/clients/iphone/distrivia/Classes/DistriviaAPI.h
iPhone: Global Leaderboard functionality to API and to Leaderboard View. Not in correct order yet. But displays to the screen just fine. Looks exactly like Android version

@@ -20,6 +20,7 @@
 + (BOOL) joinPublicWithData:(GameData*)gd;
 + (BOOL) statusWithData:(GameData*)gd;
 + (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(int)time;
++ (BOOL) globalLeaderboardWithData:(GameData*)gd;
 
 + (NSMutableURLRequest*) createPost:(NSString*)post urlFrag:(NSString*)urlFragment;
 

### 2011-05-04 src/clients/iphone/distrivia/Classes/DistriviaAPI.m

@@ -175,7 +175,6 @@ const static NSString* API_ERROR=@"err";
 // Commits user's answer to the server and gets the next information
 + (BOOL) answerWithData:(GameData*)gd answer:(NSString*)answer timeTaken:(int)time {
     NSString* fragment = [NSString stringWithFormat: @"/game/%@/question/%@", [gd gameId], [[gd question] qid]];
-    //NSString* timeString = [NSString stringWithFormat:@"%d", time];
     NSString* post = [NSString stringWithFormat:@"authToken=%@&user=%@&time=%d&a=%@", [gd getToken], 
                       [gd username], time, answer];
     NSLog(@"API Post: %@", post);
@@ -202,8 +201,39 @@ const static NSString* API_ERROR=@"err";
                 [q release];
                 [gd setScore:[[[items objectForKey:@"leaderboard"] objectForKey:[gd username]] intValue]];
             } else{
-                //Set Leaderboard
+                [gd setLeaderboard:[items objectForKey:@"leaderboard"]];
             }
+            success = true;
+        } else {
+            NSLog(@"API Error");
+        }
+        [response release];
+    }
+    return success;
+}
+
+
+
++ (BOOL) globalLeaderboardWithData:(GameData*)gd {
+    NSString* fragment = [NSString stringWithFormat: @"/leaderboard/0", [gd getToken]];
+    NSString* post = [NSString stringWithFormat:@"authToken=%@", [gd getToken]];
+    NSURLRequest* request = [DistriviaAPI createPost:post urlFrag:fragment];
+    NSError* error = nil;
+    NSData* data = [NSURLConnection sendSynchronousRequest:request returningResponse:nil error: &error];    
+    BOOL success = false;
+    
+    if ( !data ) {
+        NSLog(@"Connection Error: %@", [error localizedDescription]);
+    } else {
+        NSString* response = [[NSString alloc] initWithData: data
+                                                   encoding: NSUTF8StringEncoding];
+        NSRange textRange;
+        textRange =[API_ERROR rangeOfString: response];
+        if ( textRange.location == NSNotFound ) {
+            NSLog(@"Successful response: %@", response);
+            JSONDecoder *jsonKitDecoder = [JSONDecoder decoder];
+            NSDictionary *items = [jsonKitDecoder objectWithData:data];
+            [gd setLeaderboard:items];
             success = true;
         } else {
             NSLog(@"API Error");

### 2011-05-04 src/clients/iphone/distrivia/Classes/GameData.h

@@ -16,6 +16,7 @@
     NSString* token;
     NSString* username;
     NSString* gameId;
+    NSDictionary* leaderboard;
     Question* question;
     int score;
 }
@@ -23,6 +24,7 @@
 @property (retain, nonatomic) Question *question;
 @property (retain, nonatomic) NSString *username;
 @property (retain, nonatomic) NSString *gameId;
+@property (retain, nonatomic) NSDictionary *leaderboard;
 
 - (BOOL) hasStarted;
 - (BOOL) isDone;

### 2011-05-04 src/clients/iphone/distrivia/Classes/GameData.m

@@ -14,12 +14,12 @@
 @synthesize question;
 @synthesize username;
 @synthesize gameId;
+@synthesize leaderboard;
 
 - (id) init {
     self = [super init];
     self.status = nil;
     self.token = nil;
-    //self.gameId = nil;
     self.score = 0;
     
     return self;
@@ -41,10 +41,6 @@
     return token;
 }
 
-//- (NSString*) getGameId {
-//    return gameId;
-//}
-
 - (void) setScore:(int) newScore {
     score = newScore;
 }
@@ -58,10 +54,5 @@
     [apiToken retain];
     token = apiToken;
 }
-
-//- (void) setGameId:(NSString*) newId {
-//    [gameId retain];
-//    gameId = newId;
-//}
 
 @end

### 2011-05-04 src/clients/iphone/distrivia/Classes/JoinViewController.h

@@ -42,6 +42,10 @@
 
 - (void) joinPublic;
 - (void) joinPublicFailed;
+- (void) leaderboard;
+- (void) startRound;
+- (void) leaderboardFailed;
+- (void) startLeaderboard;
 - (void) toggleButtons;
 
 @end

### 2011-05-04 src/clients/iphone/distrivia/Classes/JoinViewController.m

@@ -57,7 +57,9 @@
 }
 
 - (IBAction) viewLeaderboardPressed:(id)sender {
-	[rootController switchToView:[rootController LEADERBOARD]];
+    [self toggleButtons];
+    [activeIndicate startAnimating];
+    [NSThread detachNewThreadSelector:@selector(leaderboard) toTarget:self withObject:nil];
 }
 
 - (IBAction)joinPublicPressed:(id)sender {
@@ -73,6 +75,16 @@
 - (IBAction) backgroundTap:(id)sender {
     [nameField resignFirstResponder];
     [passField resignFirstResponder];
+}
+
+- (void) leaderboard {
+    NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
+    if ([DistriviaAPI globalLeaderboardWithData:[rootController gd]]) {
+        [self performSelectorOnMainThread:@selector(startLeaderboard) withObject:nil waitUntilDone:NO];
+    } else {
+        [self performSelectorOnMainThread:@selector(leaderboardFailed) withObject:nil waitUntilDone:NO];
+    }
+    [pool release];
 }
 
 - (void) joinPublic {
@@ -94,7 +106,14 @@
 
 - (void) startRound {
     [activeIndicate stopAnimating];
+    [self toggleButtons];
     [rootController switchToView:[rootController ROUND]];
+}
+
+- (void) startLeaderboard {
+    [activeIndicate stopAnimating];
+    [self toggleButtons];
+    [rootController switchToView:[rootController LEADERBOARD]];
 }
 
 - (void) joinPublicFailed {
@@ -102,6 +121,17 @@
     [activeIndicate stopAnimating];
     UIAlertView *e = [[UIAlertView alloc] initWithTitle: @"Join Public failed" 
                                                 message: @"Could not join public game"
+                                               delegate: self cancelButtonTitle: @"Ok" 
+                                      otherButtonTitles: nil];
+    [e show];
+    [e release];
+}
+
+- (void) leaderboardFailed {
+    [self toggleButtons];
+    [activeIndicate stopAnimating];
+    UIAlertView *e = [[UIAlertView alloc] initWithTitle: @"Global Leaderboard Failed" 
+                                                message: @"Could not load leaderboard"
                                                delegate: self cancelButtonTitle: @"Ok" 
                                       otherButtonTitles: nil];
     [e show];

### 2011-05-04 src/clients/iphone/distrivia/Classes/LeaderboardViewController.h

@@ -10,13 +10,16 @@
 
 @class RootViewController;
 
-@interface LeaderboardViewController : UIViewController {
+@interface LeaderboardViewController : UIViewController 
+    <UITableViewDelegate, UITableViewDataSource> {
 	IBOutlet UITableView	*boardView;
+    NSArray                 *leadData;
 	
     RootViewController *rootController;
 }
 
 @property (retain, nonatomic) IBOutlet UITableView *boardView;
+@property (retain, nonatomic) NSArray *leadData;
 @property (retain, nonatomic) RootViewController *rootController;
 
 - (IBAction) okClicked:(id)sender;

### 2011-05-04 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -8,11 +8,14 @@
 
 #import "LeaderboardViewController.h"
 #import "RootViewController.h"
+#import "GameData.h"
+#import "DistriviaAPI.h"
 
 @implementation LeaderboardViewController
 
 @synthesize boardView;
 @synthesize rootController;
+@synthesize leadData;
 
 // The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
 /*
@@ -28,17 +31,20 @@
 
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
+    [self setLeadData:[[[rootController gd] leaderboard] allKeys]];
+    /*NSDictionary *leaderDict = [[rootController gd] leaderboard];
+    NSArray *keyArray = [leaderDict allKeys];
+    NSMutableArray *leaderArr = [[NSMutableArray alloc] init];
+    for (int i=0; i < [keyArray count]; i++) {
+        if (![[keyArray objectAtIndex:i] isEqualToString:@"status"]) {
+            [leaderArr addObject:[NSString stringWithFormat:@"%@\t%d", [keyArray objectAtIndex:i], 
+                              [[leaderDict objectForKey:[keyArray objectAtIndex:i]] intValue]]];
+        }
+    }
+    [self setLeadData:[NSArray arrayWithArray:leaderArr]];
+    [leaderArr release];*/
     [super viewDidLoad];
 }
-
-
-/*
-// Override to allow orientations other than the default portrait orientation.
-- (BOOL)shouldAutorotateToInterfaceOrientation:(UIInterfaceOrientation)interfaceOrientation {
-    // Return YES for supported orientations.
-    return (interfaceOrientation == UIInterfaceOrientationPortrait);
-}
-*/
 
 - (IBAction) okClicked:(id)sender {
     [rootController switchToView:[rootController JOIN]];
@@ -53,6 +59,7 @@
 
 - (void)viewDidUnload {
 	self.boardView = nil;
+    self.leadData = nil;
     self.rootController = nil;
     [super viewDidUnload];
     // Release any retained subviews of the main view.
@@ -61,8 +68,45 @@
 
 - (void)dealloc {
 	[boardView release];
+    [leadData release];
     [rootController release];
     [super dealloc];
+}
+
+#pragma mark -
+#pragma mark Table View Data Source Methods
[…]

### 2011-05-04 src/clients/iphone/distrivia/Classes/DistriviaAPI.m
iPhone: Sort leaderboard by score

@@ -233,6 +233,7 @@ const static NSString* API_ERROR=@"err";
             NSLog(@"Successful response: %@", response);
             JSONDecoder *jsonKitDecoder = [JSONDecoder decoder];
             NSDictionary *items = [jsonKitDecoder objectWithData:data];
+                        
             [gd setLeaderboard:items];
             success = true;
         } else {

### 2011-05-04 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -31,7 +31,18 @@
 
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
-    [self setLeadData:[[[rootController gd] leaderboard] allKeys]];
+    
+    [self setLeadData: [[[rootController gd] leaderboard] keysSortedByValueUsingComparator:^(id obj1, id obj2) {
+        if ([obj1 integerValue]  > [obj2 integerValue] ) {
+            return (NSComparisonResult)NSOrderedAscending;
+        }
+        
+        if ([obj1 integerValue]  < [obj2 integerValue] ) {
+            return (NSComparisonResult)NSOrderedDescending;
+        }
+        return (NSComparisonResult)NSOrderedSame;
+    }]];
+
     /*NSDictionary *leaderDict = [[rootController gd] leaderboard];
     NSArray *keyArray = [leaderDict allKeys];
     NSMutableArray *leaderArr = [[NSMutableArray alloc] init];
@@ -89,6 +100,7 @@
                                        reuseIdentifier:identifier] autorelease];
     }
     NSUInteger row = [indexPath row];
+    
     cell.textLabel.text = [leadData objectAtIndex:row];
     NSString *scoreText = [NSString stringWithFormat:@"%d", 
                            [[[[rootController gd] leaderboard] 

### 2011-05-04 poster/poster_landscape.tex
Add initial framework for the poster, with a lame RIT theme

\documentclass[landscape,a0paper,final,showframe]{baposter}

\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{bm}
\usepackage{xcolor}

\usepackage{graphicx}
\usepackage{multicol}

\usepackage{pgfbaselayers}
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\usepackage{helvet}
%\usepackage{bookman}
\usepackage{palatino}

\newcommand{\captionfont}{\footnotesize}

\selectcolormodel{cmyk}

\graphicspath{{images/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Some math symbols used in the text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Format 
\newcommand{\Matrix}[1]{\begin{bmatrix} #1 \end{bmatrix}}
\newcommand{\Vector}[1]{\Matrix{#1}}
\newcommand*{\SET}[1]  {\ensuremath{\mathcal{#1}}}
\newcommand*{\MAT}[1]  {\ensuremath{\mathbf{#1}}}
\newcommand*{\VEC}[1]  {\ensuremath{\bm{#1}}}
\newcommand*{\CONST}[1]{\ensuremath{\mathit{#1}}}
\newcommand*{\norm}[1]{\mathopen\| #1 \mathclose\|}% use instead of $\|x\|$
\newcommand*{\abs}[1]{\mathopen| #1 \mathclose|}% use instead of $\|x\|$
\newcommand*{\absLR}[1]{\left| #1 \right|}% use instead of $\|x\|$

\def\norm#1{\mathopen\| #1 \mathclose\|}% use instead of $\|x\|$
\newcommand{\normLR}[1]{\left\| #1 \right\|}% use instead of $\|x\|$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Multicol Settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\columnsep}{0.7em}
\setlength{\columnseprule}{0mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save space in lists. Use this after the opening of the list
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\compresslist}{%
\setlength{\itemsep}{1pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Begin of Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\typeout{Poster Starts}
%\background{
%  \begin{tikzpicture}[remember picture,overlay]%
%    \draw (current page.north west)+(-2em,-0em) node[anchor=north west] {\hspace{-2em}\includegraphics[height=1.1\textheight]{silhouettes_background}};
%  \end{tikzpicture}%
%}

\definecolor{ritorange}{rgb}{0.9529,0.4314,0.1294},
\definecolor{ritbrown}{rgb}{0.9725,0.9686,0.9294},
\definecolor{ritbrownl}{rgb}{0.9765,0.9765,0.9451},
\definecolor{white}{cmyk}{0,0,0,0.0}
\definecolor{black}{cmyk}{0,0,0.0,1.0}

\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  borderColor=black,
  headerColorOne=ritorange,
  headerColorTwo=ritorange,
  headerFontColor=white,
  boxColorOne=ritbrown,
  boxColorTwo=ritbrownl,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=shade-lr,
  background=none,
%  background=shade-tb,
%  background=plain,
  linewidth=1pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Distrivia: A Distributed Trivia Game}
  % Authors
  {\sf %Sans Serif
  % Serif
  Brian Gianforcaro, Steven Glazer, Samuel Milton\hspace{3em}
  Rochester Institute Of Technology
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    \includegraphics[scale=0.1]{logo}
  \end{minipage}}
  }

  %\tikzstyle{light shaded}=[top color=baposterBGtwo!30!white,bottom color=baposterBGone!30!white,shading=axis,shading angle=30]

  % Width of left inset image
     \newlength{\leftimgwidth}
     \setlength{\leftimgwidth}{0.78em+8.0em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position 
%%% towards an already declared box. So if you have a box attached to the 
%%% bottom, one to the top and a third one which should be in between, you 
%%% have to specify the top and bottom boxes before you specify the middle 
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    % A coloured circle useful as a bullet with an adjustably strong filling
    \newcommand{\colouredcircle}[1]{%
      \tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=baposterBGone!80!black!#1!white,line width=0.03em] (0,0) circle(0.18em);}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Contribution}{name=contribution,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   {}We introduce a method for expression invariant face recognition. A
   generative 3D Morphable Model (3DMM) is used to separate identity and
   expression components. The expression removal results in greatly increased
   recognition performance, even on difficult datasets, without a decrease in
   performance on expression-less datasets.

   It is applicable to any kind of input data, and was evaluated here on
   textureless range scans.
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Model}{name=model,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    The Model was learnt from 175 subjects. We used one neutral expression scan
    per identity and 50 expression scans of a subset of the subjects.

    The identity model is a linear model build from the neutral scans.
    \begin{align}
      \VEC f&=\VEC\mu + \MAT M_n\VEC\alpha_n\qquad.
    \end{align}
    For each of the 50 expression scans, we calculated an expression vector as
    the difference between the expression scan and the corresponding neutral
    scan of that subject.  This data is already mode-centered, if we regard the
    neutral expression as the natural mode of expression data. From these offset
    vectors an additional expression matrix $\MAT M_e$ was calculated, such that the complete linear Model is
    \begin{align}
      \VEC f&=\VEC\mu + \MAT M_n\VEC\alpha_n + \MAT M_e\VEC\alpha_e
    \end{align}
    The assumption here is, that the face and expression space are linearly
    independent, such that each face is represented by a unique set of
    coefficients.  
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Fitting}{name=fitting,column=0,below=model}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    A Robust Nonrigid ICP method was used to fit the model to the data.
    Robustness was achieved by iteratively reweighting the correspondences and
    using hard compatability test for the closest points.

    Fitting was initialized by a simple nose detector and proceeded fully
    automatic.
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Distance Measure}{name=measure,column=0,below=fitting,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   The Mahalanobis angle between the identity coefficients $\VEC{\alpha_{n}}$
   was used for classification.
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Expression Neutralization}{name=results neutralization,column=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}@{ }@{ }c@{ }c@{ }c@{ }c@{ }}
%   \includegraphics[height=0.42\linewidth]{16_1_tgt}&
%   \includegraphics[height=0.42\linewidth]{16_1_expression}&
%   \includegraphics[height=0.42\linewidth]{16_1_neutral}\\[-0.8em]
%   \smaller a) Target & \smaller b) Fit & \smaller c) Normalized\\[0.8em]
%   \includegraphics[height=0.42\linewidth]{16_6_tgt}&
%   \includegraphics[height=0.42\linewidth]{16_6_expression}&
%   \includegraphics[height=0.42\linewidth]{16_6_neutral}\\[-0.8em]
%   \smaller a) Target & \smaller b) Fit & \smaller c) Normalized
% \end{tabular}
  Expression normalisation for two scans of the same individual.  
  The robust fitting gives a good estimate (b) of the true face surface given
  the noisy measurement (a). It fills in holes and removes artifacts using
  prior knowledge from the face model. The pose and expression normalized faces
  (c) are used for face recognition.
  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Robustness}{name=robustness,column=1,below=results neutralization,span=1,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
 %  \includegraphics[height=0.42\linewidth]{56_4_tgt}&
 %  \includegraphics[height=0.42\linewidth]{23_2_tgt}&
 %  \includegraphics[height=0.42\linewidth]{5_6_tgt}\\[-0.8em]
 %                     & \smaller a) Targets & \\[0.8em]
 %  \includegraphics[height=0.42\linewidth]{56_4_expression}&
 %  \includegraphics[height=0.42\linewidth]{23_2_expression}& 
 %  \includegraphics[height=0.42\linewidth]{5_6_expression}\\[-0.8em]
 %                  & \smaller b) Fits & 
 %\end{tabular}
  The reconstruction (b) is robust against scans (a) with artifacts, noise, and
  holes.
  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}{name=results,column=2,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{multicols}{2}
        The method was evaluated on the GavabDB expression dataset which
        contains 427 Scans, with 3 neutral scans and 4 expression scans per ID.
        To test the impact of expression invariance on neutral data we used the
        UND Dataset from the Face Recognition Great Vendor Test, which contains
        953 neutral scans with one to eight scans per subject.
      \end{multicols}\vspace{-1em}
      \begin{tabular}{cc}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Expression neutralization improves results on the expression dataset
        without decreasing the accuracy on the neutral testset. Plotted is the
        ratio of correct answers to  the number of possible correct answers.
        %Note the different scales for the two graphs.
        %Our approach has a high accuracy on the neutral (UND) dataset.
        }
%      \end{multicols}\vspace{-1em}
      \\\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
      \begin{tabular}{cc}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Plotted are precision and recall for different retrieval depths. The lower
        precision of the UND database is due to the fact that some queries have no
        correct answers.}
%      \end{multicols}\vspace{-1em}
      \begin{tabular}{cc}
      \end{tabular}\\
%      \begin{multicols}{2}
        {Impostor detection is reliable, as the minimum distance to a match
        is smaller than the minimum distance to a nonmatch. }
%      \end{multicols}
\\
  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Open Questions}{name=questions,column=2,span=1,above=bottom,below=results}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    While the expression and identity space are linearly independent, there is
    some expression left in the identity model. This is because a ``neutral''
    face is interpreted differently by the subjects. We investigate the
    possibilty to build an identity/expression separated model without using
    the data labelling, based on a measure of independence.
  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \smaller 
%  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
%  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \headerbox{References}{name=references,column=3,above=funding,below=results}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   \smaller
%   \vspace{-0.4em}
%   \renewcommand{\section}[2]{\vskip 0.05em}
%     \begin{thebibliography}{1}\itemsep=-0.01em
%     \setlength{\baselineskip}{0.4em}
%     \bibitem{amberg07:nonrigid}
%       B.~Amberg, S.~Romdhani, T. Vetter.
%       \newblock {O}ptimal {S}tep {N}onrigid {ICP} {A}lgorithms for {S}urface {R}egistration
%       \newblock In {\em CVPR 2007}
%     \bibitem{amberg08:recognition}
%       B.~Amberg, R.~Knothe, T. Vetter.
%       \newblock Expression Invariant Face Recognition with a 3D Morphable Model
%       \newblock In {\em AFGR 2008}
%     \end{thebibliography}
% }%
\end{poster}%
%
\end{document}

### 2011-05-04 poster/poster_landscape.tex
Poster: Add logo's and fix rendering bugs

@@
 
-\definecolor{ritorange}{rgb}{0.9529,0.4314,0.1294},
-\definecolor{ritbrown}{rgb}{0.9725,0.9686,0.9294},
-\definecolor{ritbrownl}{rgb}{0.9765,0.9765,0.9451},
+\definecolor{ritorange}{rgb}{0.9529,0.4314,0.1294}
+\definecolor{ritbrown}{rgb}{0.9725,0.9686,0.9294}
+\definecolor{ritbrownl}{rgb}{0.9765,0.9765,0.9451}
 \definecolor{white}{cmyk}{0,0,0,0.0}
@@
   % Color style
+  bgColorOne=white,
+  bgColorTwo=white,
   borderColor=black,
@@
   boxshade=shade-lr,
-  background=none,
-%  background=shade-tb,
-%  background=plain,
+  background=plain,
   linewidth=1pt
@@
   % Serif
-  Brian Gianforcaro, Steven Glazer, Samuel Milton\hspace{3em}
-  Rochester Institute Of Technology
+  \newline
+  Brian Gianforcaro, Steven Glazer, Samuel Milton
+  - Rochester Institute Of Technology
   }
   % University logo
-  {{\begin{minipage}{16em}
+  {{\begin{minipage}{18em}
     \hfill
-    \includegraphics[scale=0.1]{logo}
+    \includegraphics[scale=0.05]{logo}
   \end{minipage}}
@@
 %      \end{multicols}
-\\
   }%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{
+  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  \smaller 
-%  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
-%  }%
+  \smaller 
+  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
+  }%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \headerbox{References}{name=references,column=3,above=funding,below=results}{
+ \headerbox{References}{name=references,column=3,above=funding,below=results}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %     \end{thebibliography}
-% }%
+ }%
 \end{poster}%

### 2011-05-04 src/clients/iphone/distrivia/Classes/GameData.m
iPhone: Fix build errors and warnings. Add nil gaurd to status methods.

@@ -18,19 +18,27 @@
 
 - (id) init {
     self = [super init];
-    self.status = nil;
-    self.token = nil;
-    self.score = 0;
+    status = nil;
+    token = nil;
+    score = 0;
     
     return self;
 }
 
 - (BOOL) hasStarted {
-    return [status isEqualToString:@"started"];
+    if ( status ) {
+        return [status isEqualToString:@"started"];
+    } else {
+        return false;
+    }
 }
 
 - (BOOL) isDone {
-    return [status isEqual:@"done"];
+    if ( status ) {
+        return [status isEqual:@"done"];   
+    } else {
+        return false;
+    }
 }
 
 - (int) getScore {
@@ -39,6 +47,10 @@
 
 - (NSString*) getToken {
     return token;
+}
+
+- (NSString*) getGameId {
+    return gameId;
 }
 
 - (void) setScore:(int) newScore {

### 2011-05-04 src/clients/iphone/distrivia/Classes/RoundViewController.m
iPhone: Attempting to fix problems with table not reloading leader data between local and global

@@ -79,9 +79,11 @@
 }
 
 - (IBAction) submitPressed:(id)sender {
-    [submitBut setEnabled:NO];
-    [activeIndicate startAnimating];
-    [NSThread detachNewThreadSelector:@selector(submitAnswer) toTarget:self withObject:nil];
+    if (selection != nil) {
+        [submitBut setEnabled:NO];
+        [activeIndicate startAnimating];
+        [NSThread detachNewThreadSelector:@selector(submitAnswer) toTarget:self withObject:nil];
+    }
 }
 
 - (void) setupDisplay {

### 2011-05-06 src/clients/iphone/distrivia/Classes/DistriviaAPI.h
iPhone: All private games functions working. Everything complete except for getting 'status' out of global leaderboard.

@@ -23,6 +23,7 @@
 + (BOOL) globalLeaderboardWithData:(GameData*)gd;
 + (BOOL) joinPrivateWithData:(GameData*)gd gameName:(NSString*)gamename passwd:(NSString*)pass;
 + (BOOL) createPrivateWithData:(GameData*)gd gameName:(NSString*)gamename passwd:(NSString*)pass numQuestions:(NSString*)numQ;
++ (BOOL) startPrivateWithData:(GameData*)gd;
 
 + (NSMutableURLRequest*) createPost:(NSString*)post urlFrag:(NSString*)urlFragment;
 

### 2011-05-06 src/clients/iphone/distrivia/Classes/DistriviaAPI.m

@@ -312,7 +312,33 @@ const static NSString* API_ERROR=@"err";
     return success;
 }
 
-
++ (BOOL) startPrivateWithData:(GameData*)gd {
+    NSString* fragment = [NSString stringWithFormat: @"/private/start/%@", [gd gameId]];
+    NSString* post = [NSString stringWithFormat:@"authToken=%@", [gd getToken]];
+    NSURLRequest* request = [DistriviaAPI createPost:post urlFrag:fragment];
+    NSError* error = nil;
+    NSData* data = [NSURLConnection sendSynchronousRequest:request returningResponse:nil error: &error];    
+    BOOL success = false;
+    
+    if ( !data ) {
+        NSLog(@"Connection Error: %@", [error localizedDescription]);
+    } else {
+        NSString* response = [[NSString alloc] initWithData: data
+                                                   encoding: NSUTF8StringEncoding];
+        NSRange textRange;
+        textRange =[API_ERROR rangeOfString: response];
+        if ( textRange.location == NSNotFound ) {
+            //NSLog(@"Successful response: %@", response);
+            if ([response isEqualToString:@"ok"]) {
+                success = true;
+            }
+        } else {
+            NSLog(@"API Error");
+        }
+        [response release];
+    }
+    return success;
+}
 
 + (NSMutableURLRequest*) createPost:(NSString*)post urlFrag:(NSString*)urlFragment {
 

### 2011-05-06 src/clients/iphone/distrivia/Classes/JoinViewController.h

@@ -49,6 +49,8 @@
 - (void) createPrivateWithParameters:(NSArray*)parameters;
 - (void) createPrivateFailed;
 - (void) privateCreated;
+- (void) startPrivate;
+- (void) startPrivateFailed;
 - (void) joinPublic;
 - (void) joinPublicFailed;
 - (void) leaderboard;

### 2011-05-06 src/clients/iphone/distrivia/Classes/JoinViewController.m

@@ -88,6 +88,12 @@
 }
 
 - (IBAction) createPrivatePressed:(id)sender {
+    if ([[priCreateBut titleForState:UIControlStateNormal] isEqualToString:@"Start" ]) {
+        [activeIndicate startAnimating];
+        [self toggleButtons];
+        [NSThread detachNewThreadSelector:@selector(startPrivate) toTarget:self withObject:nil];
+        return;
+    }
     NSString *gameName = [nameField text];
     NSString *gamePass = [passField text];
     NSString *numQ = [numField text];
@@ -173,6 +179,36 @@
 
 - (void) privateCreated {
     [activeIndicate stopAnimating];
+    [priCreateBut setTitle:@"Start" forState:UIControlStateNormal];
+    [priCreateBut setEnabled:YES];
+}
+
+- (void) startPrivate {
+    NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
+    if ([DistriviaAPI startPrivateWithData:[rootController gd]]) {
+        while (YES) {
+            if ([DistriviaAPI statusWithData:[rootController gd]] && 
+                [[rootController gd] hasStarted]) {
+                break;
+            }
+            [NSThread sleepForTimeInterval:2];
+        }
+        [self performSelectorOnMainThread:@selector(startRound) withObject:nil waitUntilDone:NO];
+    } else {
+        [self performSelectorOnMainThread:@selector(startPrivateFailed) withObject:nil waitUntilDone:NO];
+    }
+    [pool release];
+}
+
+- (void) startPrivateFailed {
+    [self toggleButtons];
+    [activeIndicate stopAnimating];
+    UIAlertView *e = [[UIAlertView alloc] initWithTitle: @"Start Private failed" 
+                                                message: @"Could not start private game"
+                                               delegate: self cancelButtonTitle: @"Ok" 
+                                      otherButtonTitles: nil];
+    [e show];
+    [e release];
 }
 
 - (void) leaderboard {

### 2011-05-06 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m
iPhone: Removed status from global leaderboard

@@ -46,13 +46,20 @@
         }
         return (NSComparisonResult)NSOrderedSame;
     }]];
-    
-    [boardView reloadData];
     if ([[rootController gd] localLeaderboard]) {
         [activeIndicate startAnimating];
         [NSThread detachNewThreadSelector:@selector(localUpdater) toTarget:self withObject:nil];
+    } else {
+        NSMutableArray *sansStatus = [[NSMutableArray alloc] init];
+        for (int i=0; i < [leadData count]; i++) {
+            if (![[leadData objectAtIndex:i] isEqualToString:@"status"]) {
+                [sansStatus addObject:[leadData objectAtIndex:i]];
+            }
+        }
+        [self setLeadData:[NSArray arrayWithArray:sansStatus]];
+        [sansStatus release];
     }
-    
+    [boardView reloadData];
     [super viewWillAppear:animated];
 }
 

### 2011-05-06 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java
Android: Fixed join private game. Now works

@@ -136,17 +136,19 @@ public class DistriviaAPI {
     public static GameData joinPrivate(GameData gdata, String gameName,
             String pass) throws Exception {
         String url = new String();
-        url += "/private/join/" + gameName;
+        url += "/private/join";
 
         List<NameValuePair> params = new ArrayList<NameValuePair>();
         params.add(new BasicNameValuePair("authToken", gdata.getAuthToken()));
         params.add(new BasicNameValuePair("password", pass));
         params.add(new BasicNameValuePair("user", gdata.getUserName()));
+        params.add(new BasicNameValuePair("name", gameName));
 
         String data = post(url, params);
-        Log.d("JOIN PRIVATE", data);
+        JSON jsonParser = new JSON(data);
 
-        gdata.setGameId(data);
+        gdata.setGameId(jsonParser.gameid());
+        Log.d("JOIN PRIVATE", data);
 
         return gdata;
     }

### 2011-05-06 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m
iPhone: Changed the leaderboard removal of 'status' to a faster/cleaner way thanks to the help of Brian

@@ -50,14 +50,9 @@
         [activeIndicate startAnimating];
         [NSThread detachNewThreadSelector:@selector(localUpdater) toTarget:self withObject:nil];
     } else {
-        NSMutableArray *sansStatus = [[NSMutableArray alloc] init];
-        for (int i=0; i < [leadData count]; i++) {
-            if (![[leadData objectAtIndex:i] isEqualToString:@"status"]) {
-                [sansStatus addObject:[leadData objectAtIndex:i]];
-            }
-        }
+        NSMutableArray *sansStatus = [NSMutableArray arrayWithArray:leadData];
+        [sansStatus removeObjectAtIndex:[leadData indexOfObject:@"status"]];
         [self setLeadData:[NSArray arrayWithArray:sansStatus]];
-        [sansStatus release];
     }
     [boardView reloadData];
     [super viewWillAppear:animated];

### 2011-05-06 src/clients/android/src/edu/rit/cs/distrivia/api/DistriviaAPI.java
Android: Fixed Private game creation. All private game methods work on Android now as well

@@ -148,7 +148,6 @@ public class DistriviaAPI {
         JSON jsonParser = new JSON(data);
 
         gdata.setGameId(jsonParser.gameid());
-        Log.d("JOIN PRIVATE", data);
 
         return gdata;
     }
@@ -175,9 +174,9 @@ public class DistriviaAPI {
         params.add(new BasicNameValuePair("user", gdata.getUserName()));
 
         String data = post(url, params);
-        Log.d("Private GameID: ", data);
+        JSON jsonParser = new JSON(data);
 
-        gdata.setGameId(data);
+        gdata.setGameId(jsonParser.gameid());
 
         return gdata;
     }

### 2011-05-06 papers/phase-three/paper.tex

--- 2011-04-23 papers/phase-two/paper.tex
@@
 
-\section {What We've Done}
-Much of our system has been implemented and is in the debugging phase.
-The server application, web client, and Android client are nearly complete with some revisions happening as necessary.
-We have also started development on an application for the iPhone platform.
-The extent of what has been finished for each part of our system is explained below.
-
-\subsection{Architecture Overview }
+\section{Project Motivation}
+\section{Architecture}
 \begin{figure}[h!]
@@
 
-\subsection {Server Applications}
+\subsection{Server Applications}
 The server is currently almost feature complete, but still needs a lot of
@@
 
-\subsection {Traffic}
+\subsection{Traffic}
 We have two load sharers set up. Both sharers are currently configured to
@@
 
-\subsection {Clients}
+\subsection{Clients}
 Our focus for clients has been on a web-based client and an Android application.
@@
 
-\subsection {Messages}
+\subsection{Messages}
 We are currently using the https protocol for our messages. This provides a secure
@@
 
-\section {What's Left}
-\subsection {Server}
-The server is nearly completed. The server application just needs to have some tweaks and further testing.
-\subsection {Web Client}
-A lot of the main features of the web client are completed.
-However, there are still a few remaining features that need to be implemented.
-The only major feature remaining is private games, which are largely unstarted, although it will reuse most of the public game code.
-In addition to this, buttons should be disabled when clicked to prevent users from spamming the server with repeat messages.
-\subsection {Android}
-Private game play is the largest thing left for the Android client. Besides this we've just been fixing bugs and cleaning up the
-user interface.
-\subsection {iPhone}
-The iPhone application just started development in the last couple days. We
-have built most of the user interface but need to connect all of the actions
-to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
-and competing in rounds.
+\section{Design}
 
-\section {Meeting the Requirements}
+\section{Implementation}
 
-Our system has three unique clients. One of them is designed for the Android
-platform as an application.
-Another is designed for the iPhone platform as a native application.
-The third is a web client, which is specifically being tested on Desktop and Laptop
-browsers, however it may work on many hand held web browsers as well.
+\section{Lessons Learned}
 
-Our system supports having any number of servers and allowing any subset of them to fail.
-We are using Riak, which supports a 'shared nothing' architecture.  We can add a new server
-by joining it to our database and starting the web server.  This can be done as many times
-as needed, allowing us to scale up our system.  These same principles also give us great fault
-tolerance, since any server is capable of running independently.  As long as one server is still
-up, the service will be available.
-
-We use round robin DNS to allow our clients to be completely ignorant of our servers.  Load sharers
-can be added and removed from the DNS server and the clients will be completely ignorant of this
-and unaffected.  The load sharers in turn know about our data servers and do their best to
-distribute the load across them.  When a new server is added, it is just added to our load sharer
-configuration file and clients can start using it.  When a server fails, the sharers will stop directing
-traffic to it.
-
-We are currently using Riak as our database backend. We chose Riak for multiple
-reasons, but the biggest was it's focus on  scalability, fault-tolerance,
-availability, and replication. Riak is a Amazon Dynamo \cite{dynamo} inspired
-database, it supports full masterless replication. In Riak every node can
-serve client requests and they are propagated to the rest of the cluster.
-In our system we have made sure that this replication occurs between nodes
-on Amazon EC2's internal Gigabit ethernet so it is as fast as possible. Riak
-also has the unique property that if all of the nodes but one fail, the single
-node can still accept both reads and writes to the database. When the other
-nodes return to operational state from failure, all changes will automatically
-be propagated to all of the nodes. This feature is the basis for our ability to
-support and recover from partial failures. In the event that two Riak nodes accept
-writes from two separate clients modifying the same data and Riak is unable
-to resolve the conflict the user is given both versions and allowed to resolve
-the conflict them selves. However we have configured our installation so this
-can not occur, we have specified that every available node must agree on a
-write before it is committed. Given the relatively small number of nodes (five)
-that will take part in this agreement, we decided that the possible overhead
-was acceptable for the increased level of consistency it gives us.
-
-Our team is taking a very proactive stance towards security. All of our machines are properly firewalled so that
-outside clients can not authenticate to our database cluster. Also we have implemented SSL through our entire infrastructure.
-Our load sharer's automatically redirect http:// to https:// and once you are in https:// at the load sharer, SSL continues all the
-way back to our actual web application back end serving responses over a SSL wrapped socket. This way no passwords are ever
-sent in clear text. Our group even found a SSL certificate authority who was willing to sign our SSL certificate for free. This gives
-us actual fully functional, authenticatable SSL infrastructure. In order to make sure that our system properly secures user information,
-we stuck with the industry standard of storing a hashed version of the users password instead of the password itself. We decided on using
-the cryptographically secure hashing function designed for passwords known as bcrypt \cite{bcrypt}.
+\section{Future Work}
 

### 2011-05-06 poster/poster_landscape.tex
Poster: Add headers to poster

@@
 \usepackage{xcolor}
-
 \usepackage{graphicx}
@@
   % Show grid to help with alignment
-  grid=no,
+  grid=yes,
   % Column spacing
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Contribution}{name=contribution,column=0,row=0}{
+  \headerbox{Project Motivation}{name=motivation,column=0,row=0}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-   {}We introduce a method for expression invariant face recognition. A
-   generative 3D Morphable Model (3DMM) is used to separate identity and
-   expression components. The expression removal results in greatly increased
-   recognition performance, even on difficult datasets, without a decrease in
-   performance on expression-less datasets.
 
-   It is applicable to any kind of input data, and was evaluated here on
-   textureless range scans.
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Model}{name=model,column=0,below=contribution}{
+  \headerbox{Architecture}{name=arch,column=0,below=motivation}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    The Model was learnt from 175 subjects. We used one neutral expression scan
-    per identity and 50 expression scans of a subset of the subjects.
 
-    The identity model is a linear model build from the neutral scans.
-    \begin{align}
-      \VEC f&=\VEC\mu + \MAT M_n\VEC\alpha_n\qquad.
-    \end{align}
-    For each of the 50 expression scans, we calculated an expression vector as
-    the difference between the expression scan and the corresponding neutral
-    scan of that subject.  This data is already mode-centered, if we regard the
-    neutral expression as the natural mode of expression data. From these offset
-    vectors an additional expression matrix $\MAT M_e$ was calculated, such that the complete linear Model is
-    \begin{align}
-      \VEC f&=\VEC\mu + \MAT M_n\VEC\alpha_n + \MAT M_e\VEC\alpha_e
-    \end{align}
-    The assumption here is, that the face and expression space are linearly
-    independent, such that each face is represented by a unique set of
-    coefficients.  
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Fitting}{name=fitting,column=0,below=model}{
+  \headerbox{Design}{name=design,column=1, span=1}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    A Robust Nonrigid ICP method was used to fit the model to the data.
-    Robustness was achieved by iteratively reweighting the correspondences and
-    using hard compatability test for the closest points.
-
-    Fitting was initialized by a simple nose detector and proceeded fully
-    automatic.
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Distance Measure}{name=measure,column=0,below=fitting,above=bottom}{
+  \headerbox{Implementation}{name=implementation,column=1,below=design}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-   The Mahalanobis angle between the identity coefficients $\VEC{\alpha_{n}}$
-   was used for classification.
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Expression Neutralization}{name=results neutralization,column=1,row=0}{
+  \headerbox{Lessons Learned}{name=lessons,column=2, row=0}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% \begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}@{ }@{ }c@{ }c@{ }c@{ }c@{ }}
-%   \includegraphics[height=0.42\linewidth]{16_1_tgt}&
-%   \includegraphics[height=0.42\linewidth]{16_1_expression}&
-%   \includegraphics[height=0.42\linewidth]{16_1_neutral}\\[-0.8em]
-%   \smaller a) Target & \smaller b) Fit & \smaller c) Normalized\\[0.8em]
-%   \includegraphics[height=0.42\linewidth]{16_6_tgt}&
-%   \includegraphics[height=0.42\linewidth]{16_6_expression}&
-%   \includegraphics[height=0.42\linewidth]{16_6_neutral}\\[-0.8em]
-%   \smaller a) Target & \smaller b) Fit & \smaller c) Normalized
-% \end{tabular}
-  Expression normalisation for two scans of the same individual.  
-  The robust fitting gives a good estimate (b) of the true face surface given
-  the noisy measurement (a). It fills in holes and removes artifacts using
-  prior knowledge from the face model. The pose and expression normalized faces
-  (c) are used for face recognition.
   }
+
+  \headerbox{Future Work}{name=future,column=2,row=0.4}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Robustness}{name=robustness,column=1,below=results neutralization,span=1,above=bottom}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- %\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
- %  \includegraphics[height=0.42\linewidth]{56_4_tgt}&
- %  \includegraphics[height=0.42\linewidth]{23_2_tgt}&
- %  \includegraphics[height=0.42\linewidth]{5_6_tgt}\\[-0.8em]
- %                     & \smaller a) Targets & \\[0.8em]
- %  \includegraphics[height=0.42\linewidth]{56_4_expression}&
- %  \includegraphics[height=0.42\linewidth]{23_2_expression}& 
- %  \includegraphics[height=0.42\linewidth]{5_6_expression}\\[-0.8em]
- %                  & \smaller b) Fits & 
- %\end{tabular}
-  The reconstruction (b) is robust against scans (a) with artifacts, noise, and
-  holes.
   }
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Results}{name=results,column=2,span=2,row=0}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-      \begin{multicols}{2}
-        The method was evaluated on the GavabDB expression dataset which
-        contains 427 Scans, with 3 neutral scans and 4 expression scans per ID.
-        To test the impact of expression invariance on neutral data we used the
-        UND Dataset from the Face Recognition Great Vendor Test, which contains
-        953 neutral scans with one to eight scans per subject.
-      \end{multicols}\vspace{-1em}
-      \begin{tabular}{cc}
-      \end{tabular}\\
-%      \begin{multicols}{2}
-        {Expression neutralization improves results on the expression dataset
-        without decreasing the accuracy on the neutral testset. Plotted is the
-        ratio of correct answers to  the number of possible correct answers.
-        %Note the different scales for the two graphs.
-        %Our approach has a high accuracy on the neutral (UND) dataset.
-        }
-%      \end{multicols}\vspace{-1em}
-      \\\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
-      \begin{tabular}{cc}
-      \end{tabular}\\
-%      \begin{multicols}{2}
-        {Plotted are precision and recall for different retrieval depths. The lower
-        precision of the UND database is due to the fact that some queries have no
-        correct answers.}
-%      \end{multicols}\vspace{-1em}
-      \begin{tabular}{cc}
-      \end{tabular}\\
-%      \begin{multicols}{2}
-        {Impostor detection is reliable, as the minimum distance to a match
-        is smaller than the minimum distance to a nonmatch. }
-%      \end{multicols}
-  }%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Open Questions}{name=questions,column=2,span=1,above=bottom,below=results}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    While the expression and identity space are linearly independent, there is
-    some expression left in the identity model. This is because a ``neutral''
-    face is interpreted differently by the subjects. We investigate the
-    possibilty to build an identity/expression separated model without using
-    the data labelling, based on a measure of independence.
-  }%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Funding}{name=funding,column=3,span=1,above=bottom}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \smaller 
-  This work was supported in part by Microsoft Research through the European PhD Scholarship Programme.
-  }%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- \headerbox{References}{name=references,column=3,above=funding,below=results}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   \smaller
-%   \vspace{-0.4em}
-%   \renewcommand{\section}[2]{\vskip 0.05em}
-%     \begin{thebibliography}{1}\itemsep=-0.01em
-%     \setlength{\baselineskip}{0.4em}
-%     \bibitem{amberg07:nonrigid}
-%       B.~Amberg, S.~Romdhani, T. Vetter.
-%       \newblock {O}ptimal {S}tep {N}onrigid {ICP} {A}lgorithms for {S}urface {R}egistration
-%       \newblock In {\em CVPR 2007}
-%     \bibitem{amberg08:recognition}
-%       B.~Amberg, R.~Knothe, T. Vetter.
-%       \newblock Expression Invariant Face Recognition with a 3D Morphable Model
-%       \newblock In {\em AFGR 2008}
-%     \end{thebibliography}
- }%
 \end{poster}%

### 2011-05-06 papers/phase-three/paper.tex

@@
 
-%\begin{abstract}
-%In this paper we detail our current progress on our distributed trivia game.
-%We will explain what has been done so far, what we need to do, and how we
-%have met the requirements for the project. We also discuss the architecture
-%for our system.
-%\end{abstract}
+\begin{abstract}
+In this paper we will discuss our decisions and detail our discoveries throughout designing a distributed trivia system.
+\end{abstract}
 
 \section{Project Motivation}
+Our motivation for this project was to build a system that would allow people to compete across multiple platforms reliably.
+High availability was a major concern for us, as it enables people to compete at all times.
+This form of trivia is a multiplayer social game.
+It takes advantage of a number of different platforms so that users can feel free to play on any device they prefer.
+The web client ensures that almost any device will be able to connect and play.
+Designing it on mobile platforms allows us to take advtange of the specific platform and lets people easily play on the go.
 \section{Architecture}
+\subsection{Servers}
+For our servers, we are using Amazon EC2 micro instances.
+These are running x86-64 Amazon Linux.
+They have 8gb of network attached storage and 613mb of memory.
+
+Each server is installed with our custom web app that services our requests.
+Each one is also equipped with an instance of Riak for maintaining our database.
+The Python web app utilizes the Flask web framework and we serve the application and all files with the Tornado web server, both of which are open source.
+We have five servers all running our server application and hosting the databases.
+Two of those are set up as hot spares in case of a failure.
+
+Currently, we are using the NGINX \cite{nginx} in a reverse proxy configuration for our load sharing needs.
+For this project there are two load balancers which are running on personal desktop computers that have reliable internet connections.
+These are set up with round robin DNS entries, courtesy of ZoneEdit.com, a free DNS management service.
+\section{Design}
 \begin{figure}[h!]
@@
  \end{figure}
-
-\subsection {Servers}
-Currently, we have 6 servers running on Amazon's Elastic Compute Cloud \cite{aec}. One server is being used as a web-monitor
-host running Monit\cite{monit}. We are able to login to the web-monitor to see the status of all our
-servers, databases, and load sharers. This will help us manage whether or not the services
-are running and allow us to track down any problems, if they arise. Three
-servers are all running our server application and hosting the databases.
-We also have two final servers that we have setup as hot spares in the event
-of partial or total failure.
-Each server contains the server application that responds to clients as well as
-the Riak \cite{riak} databases. Riak auto-synchronizes the databases between the 5 servers.
-Note that the hot spares are setup to be part of the database cluster so they
-have a full copy of the database on hand, however they don't accept any reads
-or writes directly. This allows for them to immediately be ready for read/writes in the event that the original servers are down.
-With this configuration if we were to add a server, we would just need to update 
-Riak and it would sync the databases to any additional servers as well. These servers,
-therefore, all contain the same information. If any servers go down, the distributed
-system would still run fine. We could have all servers go down except one and still
-be reliably handling requests.
+\subsection{Servers}
+For this project we deployed six servers running on Amazon's Elastic Compute Cloud \cite{aec}.
+One server is being used as a web-monitor host running Monit\cite{monit}.
+We were able to login to the web-monitor to see the status of all our servers, databases, and load sharers.
+This assisted us in managing whether or not the services were running and allowed us to track down any problems, if they arose.
+Each server contains the server application that responds to clients as well as the Riak \cite{riak} databases.
+Riak handles auto-synchronization of the databases between the five servers.
+Note that the hot spares were setup to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly.
+This allows for them to immediately be ready for read/writes in the event that the original servers are down.
+With this configuration if we were to add a server, we would just need to update Riak and it would sync the databases to any additional servers as well.
+These servers, therefore, all contain the same information.
+If any servers go down, the distributed system would still run fine.
+We could have all servers go down except one and still be reliably handling requests.
 
 \subsection{Server Applications}
-The server is currently almost feature complete, but still needs a lot of
-testing. Client registration, and login are all supported. A client can
-join a game, retrieve questions for that game, and answer questions. Both a
-global leader board and individual per game leader board can also be requested.
-We recently refactored our API to be more universally consistent.
-The servers and clients now work on a more consistent basis where the clients all expect the same information and use the same calls.
+The server application handles requests from the user via the load sharers.
+The server application supports the following features:
+\begin{itemized}
+\item Client registration
+\item Login
+\item Query games status
+\item Joining public games
+\item Joining private games
+\item Creating private games
+\item Question retrieval
+\item Question answering
+\item Global leaderboard
+\end{itemized}
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/GameData.h
iPhone: Added a bunch of commenting. Still need to do more...

@@ -2,7 +2,7 @@
 //  GameData.h
 //  distrivia
 //
-//  Created by Brian Gianforcaro on 4/20/11.
+//  Created by BitShift on 4/20/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/JoinViewController.m

@@ -2,7 +2,7 @@
 //  JoinView.m
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/19/11.
+//  Created by BitShift on 4/19/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/LeaderboardViewController.h

@@ -2,7 +2,7 @@
 //  LeaderboardViewController.h
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/21/11.
+//  Created by BitShift on 4/21/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -2,7 +2,7 @@
 //  LeaderboardViewController.m
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/21/11.
+//  Created by BitShift on 4/21/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/LoginViewController.m

@@ -2,7 +2,7 @@
 //  distriviaViewController.m
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/19/11.
+//  Created by BitShift on 4/19/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 
@@ -18,19 +18,6 @@
 @synthesize passField;
 @synthesize activeIndicate;
 @synthesize rootController;
-
-
-
-/*
-// The designated initializer. Override to perform setup that is required before the view is loaded.
-- (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
-    self = [super initWithNibName:nibNameOrNil bundle:nibBundleOrNil];
-    if (self) {
-        // Custom initialization
-    }
-    return self;
-}
-*/
 
 /*
 // Implement loadView to create a view hierarchy programmatically, without using a nib.

### 2011-05-07 src/clients/iphone/distrivia/Classes/RoundViewController.h

@@ -2,7 +2,7 @@
 //  RoundViewController.h
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/19/11.
+//  Created by BitShift on 4/19/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -2,7 +2,7 @@
 //  RoundViewController.m
 //  distrivia
 //
-//  Created by Sticky Glazer on 4/19/11.
+//  Created by BitShift on 4/19/11.
 //  Copyright 2011 Rochester Institute of Technology. All rights reserved.
 //
 

### 2011-05-07 src/clients/iphone/distrivia/Classes/JoinViewController.m
iPhone: Finished commenting the code to be understandable and helpful

@@ -25,18 +25,6 @@
 @synthesize activeIndicate;
 @synthesize rootController;
 
-// The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
-/*
-- (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
-    self = [super initWithNibName:nibNameOrNil bundle:nibBundleOrNil];
-    if (self) {
-        // Custom initialization.
-    }
-    return self;
-}
-*/
-
-
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
     UIImage *buttonImageNormal = [UIImage imageNamed:@"whiteButton.png"];
@@ -57,19 +45,23 @@
     [super viewDidLoad];
 }
 
+
 - (IBAction) viewLeaderboardPressed:(id)sender {
+    // Prepares the UI for loading the Global Leaderboard
     [self toggleButtons];
     [activeIndicate startAnimating];
     [NSThread detachNewThreadSelector:@selector(leaderboard) toTarget:self withObject:nil];
 }
 
 - (IBAction)joinPublicPressed:(id)sender {
+    // Prepares the UI for joining a public game
     [activeIndicate startAnimating];
     [self toggleButtons];
     [NSThread detachNewThreadSelector:@selector(joinPublic) toTarget:self withObject:nil];
 }
 
 - (IBAction) joinPrivatePressed:(id)sender {
+    // Prepares the UI for joining a private game
     NSString *gameName = [nameField text];
     NSString *gamePass = [passField text];
     if ([gameName length] == 0 || [gamePass length] == 0) {
@@ -88,6 +80,7 @@
 }
 
 - (IBAction) createPrivatePressed:(id)sender {
+    // Prepares the UI for creating a private game
     if ([[priCreateBut titleForState:UIControlStateNormal] isEqualToString:@"Start" ]) {
         [activeIndicate startAnimating];
         [self toggleButtons];
@@ -113,16 +106,23 @@
 }
 
 - (IBAction) textFieldDoneEditing:(id)sender {
+    // Hides keyboard when 'DONE' is pressed
     [sender resignFirstResponder];
 }
 
 - (IBAction) backgroundTap:(id)sender {
+    // Hides the keyboard on background tap
     [nameField resignFirstResponder];
     [passField resignFirstResponder];
[…]

### 2011-05-07 src/clients/iphone/distrivia/Classes/LeaderboardViewController.m

@@ -18,24 +18,13 @@
 @synthesize rootController;
 @synthesize leadData;
 
-// The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
-/*
-- (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
-    self = [super initWithNibName:nibNameOrNil bundle:nibBundleOrNil];
-    if (self) {
-        // Custom initialization.
-    }
-    return self;
-}
-*/
-
-
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
     [super viewDidLoad];
 }
 
 - (void) viewWillAppear:(BOOL)animated {
+    // Sets the leaderboard data and activates the local updater if it is the local leaderboard
     [self setLeadData: [[[rootController gd] leaderboard] keysSortedByValueUsingComparator:^(id obj1, id obj2) {
         if ([obj1 integerValue]  > [obj2 integerValue] ) {
             return (NSComparisonResult)NSOrderedAscending;
@@ -59,6 +48,7 @@
 }
 
 - (IBAction) okClicked:(id)sender {
+    // Prepares the UI for switching to the Join View
     [[rootController gd] setLocalLeaderboard:NO];
     if ([activeIndicate isAnimating]) {
         [activeIndicate stopAnimating];
@@ -67,6 +57,10 @@
 }
 
 - (void) localUpdater {
+    /*
+     Thread: Makes periodic calls to update the leaderboard information with the
+     current scores of all players in the round as they continue to compete
+     */
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     while([[rootController gd] localLeaderboard]) {
         if ([DistriviaAPI statusWithData:[rootController gd]]) {
@@ -79,6 +73,7 @@
 }
 
 - (void) updateLeaderboard {
+    // Updates the leaderboard data
     [self setLeadData: [[[rootController gd] leaderboard] keysSortedByValueUsingComparator:^(id obj1, id obj2) {
         if ([obj1 integerValue]  > [obj2 integerValue] ) {
             return (NSComparisonResult)NSOrderedAscending;
@@ -119,11 +114,13 @@
 #pragma mark -
 #pragma mark Table View Data Source Methods
 - (NSInteger) tableView:(UITableView*)tableView numberOfRowsInSection:(NSInteger)section {
[…]

### 2011-05-07 src/clients/iphone/distrivia/Classes/LoginViewController.m

@@ -19,13 +19,6 @@
 @synthesize activeIndicate;
 @synthesize rootController;
 
-/*
-// Implement loadView to create a view hierarchy programmatically, without using a nib.
-- (void)loadView {
-}
-*/
-
-
 
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
@@ -47,6 +40,8 @@
     [super viewDidLoad];
 }
 
+// Responds to the login button being pressed.
+// Completes UI Actions to log in a player
 - (IBAction) loginPressed:(id)sender {
     NSString *username = [userField text];
     NSString *passwd = [passField text];
@@ -66,6 +61,8 @@
     }
 }
 
+// Responds to the register button being pressed.
+// Completes UI Actions to register a player
 - (IBAction) registerPressed:(id)sender {
     NSString *username = [userField text];
     NSString *passwd = [passField text];
@@ -85,16 +82,19 @@
     }
 }
 
+// Releases the keyboard and logs in the user when 'DONE' is pressed
 - (IBAction) textFieldDoneEditing:(id)sender {
     [self loginPressed:sender];
     [sender resignFirstResponder];
 }
 
+// Hides the keyboard
 - (IBAction) backgroundTap:(id)sender {
     [userField resignFirstResponder];
     [passField resignFirstResponder];
 }
 
+// Thread: Calls login on network and responds to the main thread accordingly
 - (void) loginWithParameters:(NSArray*)parameters {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     NSString *username = [parameters objectAtIndex:0];
@@ -107,6 +107,7 @@
     [pool release];
 }
 
+// Thread: Calls register on network and responds to the main thread accordingly
 - (void) registerWithParameters:(NSArray *)parameters {
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     NSString *username = [parameters objectAtIndex:0];
@@ -119,6 +120,7 @@
     [pool release];
 }
 
+// Prepares the UI for switching to the Join View
 - (void) startJoin {
     [activeIndicate stopAnimating];
     NSUserDefaults *defaults = [NSUserDefaults standardUserDefaults];
@@ -126,6 +128,7 @@
     [rootController switchToView:[rootController JOIN]];
 }
 
+// Displays an Alert that the login failed
 - (void) loginFailed {
     [activeIndicate stopAnimating];
[…]

### 2011-05-07 src/clients/iphone/distrivia/Classes/RoundViewController.m

@@ -27,18 +27,6 @@
 @synthesize startTime, endTime;
 @synthesize selection;
 
-// The designated initializer.  Override if you create the controller programmatically and want to perform customization that is not appropriate for viewDidLoad.
-/*
-- (id)initWithNibName:(NSString *)nibNameOrNil bundle:(NSBundle *)nibBundleOrNil {
-    self = [super initWithNibName:nibNameOrNil bundle:nibBundleOrNil];
-    if (self) {
-        // Custom initialization.
-    }
-    return self;
-}
-*/
-
-
 // Implement viewDidLoad to do additional setup after loading the view, typically from a nib.
 - (void)viewDidLoad {
     [question setNumberOfLines:3];
@@ -56,11 +44,16 @@
 }
 
 - (void) viewDidAppear:(BOOL)animated {
+    // Sets up the round display when the view appears
     [self setupDisplay];
     [super viewDidAppear:animated];
 }
 
 - (IBAction) answerSelected:(id)sender {
+    /* 
+     Reacts to an answer being selected. Sets the selection
+     variable and changes the UI accordingly
+     */
     [self setEndTime:[[NSDate alloc] init]];
 	[self deselectAll];
 	if (sender == aBut) {
@@ -83,6 +76,7 @@
 }
 
 - (IBAction) submitPressed:(id)sender {
+    // Responds to the submit button being pressed. Sets up the UI for sending answer
     if (selection != nil) {
         [submitBut setEnabled:NO];
         [activeIndicate startAnimating];
@@ -91,6 +85,7 @@
 }
 
 - (void) setupDisplay {
+    // Sets up the view with Q/A information and current score
     [pBar setProgress:0.0];
     Question *q = [[rootController gd] question];
     [question setText:[q question]];
@@ -111,6 +106,7 @@
 }
 
 - (void) deselectAll {
+    // Deselects all answer buttons and resets selection variable
     self.selection = nil;
 	[aBut setBackgroundColor:[UIColor grayColor]];
 	[bBut setBackgroundColor:[UIColor grayColor]];
@@ -119,6 +115,10 @@
 }
 
 - (void) submitAnswer {
+    /*
+     Thread: Calls the network to submit the users answer and
+     responds accordingly
+     */
     NSAutoreleasePool *pool = [[NSAutoreleasePool alloc] init];
     int timeTaken = [[NSNumber numberWithFloat:[endTime timeIntervalSinceDate:startTime]*1000] intValue];
[…]

### 2011-05-10 papers/phase-three/paper.tex
Paper: Changes to Design and Implementation of the paper. Also finished up the abstract to give more depth. Design changes are mostly about clients and Implementation is mostly just setting up the subsections

@@
 
-%\title{ Distributed Systems: Project Description }
 \title{ Distrivia: A Distributed Trivia Game }
@@
 \begin{abstract}
-In this paper we will discuss our decisions and detail our discoveries throughout designing a distributed trivia system.
+In this paper we will discuss our decisions and detail our discoveries throughout designing a distributed trivia system, Distrivia. 
+This paper will outline our motivations behind the project, the architecture, design, implementation, lessons learned, and future work for the distributed trivia system. 
+The distrivia system was implemented on 3 platforms (web, Android, and iPhone) to provide multiple ways for players to stay connected. 
+It also utilizes advanced distributed systems algorithms and technology such as Amazon's EC2, Riak, SSL communication, round robin DNS, and NGINX load sharing. 
+All of these services provide for high availability and secure play.
 \end{abstract}
@@
 Designing it on mobile platforms allows us to take advtange of the specific platform and lets people easily play on the go.
+
 \section{Architecture}
@@
 These are set up with round robin DNS entries, courtesy of ZoneEdit.com, a free DNS management service.
+
 \section{Design}
@@
 \subsection{Clients}
-Our focus for clients has been on a web-based client and an Android application.
-Both clients have most of the workings completed. The web-based client will
-be run from desktop platforms and laptop platforms. The Android client will run
-on any Android phone running OS 2.1 or higher and does not use any unique services that require specific
-hardware. Both clients are nearly fully-functional. They can, currently, login/register
-players, view leaderboards, join public games, and compete in public games. We are actively adding features to both clients, daily.
-We have also started development on an iPhone application for distrivia. This client does not yet communicate with the server, but 
-it does implement nearly all the views seen in the other clients. We have been setting up the network communication for the iPhone
-platform as well.
+Distrivia is implemented on three distinct platforms (web, Android, and iPhone).
+The clients were designed to run without specific equipment or relying on external applications. 
+The clients can be run, once installed, from desktop computers, laptops, Androids, and iPhones out of box.
+The web client can be run from any browser that supports CSS, which is true of all modern web browsers.
+The web client can be run from any operating system that supports web browsing and has a connection to the internet (this includes mobile devices). 
+This gives users of blackberry phones and palms the ability to play, even though there is not a native app for them.
+The Android client will run on any Android platform running OS 2.1 or higher and does not use any unique services that require specific hardware.
+Likewise, the iPhone client will run on any iPhone/iPod touch platform running any iOS without the need for specific hardware.
+The Android and iPhone clients just require an active data connection either by cell signal or wireless internet.
+
+All of our clients were designed similarly.
+We tried to keep the layout as simple as possible, for the user to be able to easily navigate the game.
+The mobile clients are the most similar due to their limited screen real estate.
+This was important in allowing players to play on multiple platforms while using a layout they were used to.
+As mobile gaming continues to grow, our approach was to promote the play of Distrivia on the go. 
+Each round can be quickly played within the course of a few minutes, which makes it ideal for playing on mobile devices.
+Distrivia allows users to connect with players on any other device which gives friends the opportunity to play together without forcing them to conform to one platform.
 
@@
 
-\section{Design}
+\section{Implementation}
+\subsection{Network}
 
-\section{Implementation}
+\subsection{Clients}
+% Show images of implemented clients
+Creating native apps for the Android OS and iPhone gives the users the best performance on those devices along with the native look and feel of the device for optimal design.
+\subsubsection{Web}
+
+\subsubsection{Android}
+
+\subsubsection{iPhone}
 

### 2011-05-10 papers/phase-three/paper.tex
Updated more information on the paper. Mostly tryign to resort and make distinctions between design and implementation.

@@
 Currently, we are using the NGINX \cite{nginx} in a reverse proxy configuration for our load sharing needs.
-For this project there are two load balancers which are running on personal desktop computers that have reliable internet connections.
-These are set up with round robin DNS entries, courtesy of ZoneEdit.com, a free DNS management service.
+This service can be used on any machine with an active internet connection and a constantly reachable IP address or DNS lookup.
 
@@
 
-\subsection{Traffic}
-We have two load sharers set up. Both sharers are currently configured to
-divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
-for a load distributer to go down and we would still be able to serve requests
-to the servers. These load sharers are selected by the clients using round
-robin DNS where distrivia.lame.ws will select either load distributer that is
-up at random. If a load distributer should go down or become unreachable the
-DNS service will no longer serve that hosts DNS record until it is again
-reachable. This provides us with stability for accessing the servers. The
-load sharers are set up to attempt to connect to a server twice in a one second
-period before deeming it dead and removing it from its list of servers to direct clients towards.
-Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
-for our load sharing needs.
+\subsection{Load Sharers}
+The load sharers act as an agent between the clients and the servers to ensure reliable, fast communication.
+Messages are relayed through the load sharers from the client.
+Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
+This is an important part of the distributed system in keeping network traffic down on the the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
+They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
 
@@
 \subsection{Messages}
-We are currently using the https protocol for our messages. This provides a secure
-and usable messaging system that we have designed our client and server APIs to use.
-The actual messages are sent and received in two way's. Initially a user session key is
-generated using the UUID\cite{uuid} algorithm and returned to the user on successful
-authentication. This session key is then passed back to the server with every in coming
-message. Messages are sent to the server using POST and GET request methods supported
-by the HTTP protocol. Responses from the server are in the form of JSON \cite{json} objects.
-JSON is a small, easily parseable format, representing objects in a human readable format as
-they would be represented in JavaScript. With the web client the JSON object returned from
-the server is instantly usable, however for the Android client we have to parse the JSON object
-into a native Java object. The Android SDK provides libraries to do this, located in the
+Distrivia uses https protocol for communication. 
+This provides a secure and usable messaging system that both the client and server APIs use.
+The actual messages are sent and received in two ways. 
+Initially a user session key is generated using the UUID\cite{uuid} algorithm and returned to the user on successful authentication. 
+This session key is then passed back to the server with every incoming
+message. 
+Messages are sent to the server using POST and GET request methods supported
+by the HTTP protocol. 
+Responses from the server are in the form of JSON \cite{json} objects.
+JSON is a small, easily-parseable format, representing objects in a human readable format as they would be represented in JavaScript. 
+With the web client the JSON object returned from the server is instantly usable, however for other applications, parsing the JSON object into native objects is necessary. 
+% Maybe should go under implementation?
+The Android SDK provides libraries to do this, located in the
 org.json \cite{orgjson} package name space.
+% Include the package used for iPhone and cite
 
@@
 \subsection{Network}
+
+For this project, we set up two load balancers which are running on personal desktop computers that have reliable internet connections.
+The duplicate sharers allow for a load distributer to go down and we would still be able to serve requests to the servers. 
+% TODO cite ZoneEdit
+These are set up with round robin DNS entries, courtesy of ZoneEdit.com, a free DNS management service.
+These load sharers are selected by the clients where distrivia.lame.ws will select either load distributer that is up at random. 
+If a load distributer should go down or become unreachable the DNS service will no longer serve that hosts DNS record until it is again reachable.
+This provides us with stability for accessing the servers.
 

### 2011-05-11 papers/phase-three/paper.tex

@@
 The web client ensures that almost any device will be able to connect and play.
-Designing it on mobile platforms allows us to take advtange of the specific platform and lets people easily play on the go.
+Designing it on mobile platforms allows us to take advantage of the specific platform and lets people easily play on the go.
 
@@
 \subsection{Servers}
-For our servers, we are using Amazon EC2 micro instances.
+For our servers, we used Amazon EC2 micro instances.
 These are running x86-64 Amazon Linux.
@@
 Each server is installed with our custom web app that services our requests.
-Each one is also equipped with an instance of Riak for maintaining our database.
+Each one is also equipped with an instance of Riak \cite{riak} for maintaining our database.
+% TODO cite Flask and Tornado
 The Python web app utilizes the Flask web framework and we serve the application and all files with the Tornado web server, both of which are open source.
-We have five servers all running our server application and hosting the databases.
-Two of those are set up as hot spares in case of a failure.
 
-Currently, we are using the NGINX \cite{nginx} in a reverse proxy configuration for our load sharing needs.
+For load sharing, we used NGINX \cite{nginx} in a reverse proxy configuration.
 This service can be used on any machine with an active internet connection and a constantly reachable IP address or DNS lookup.
@@
 \subsection{Servers}
-For this project we deployed six servers running on Amazon's Elastic Compute Cloud \cite{aec}.
-One server is being used as a web-monitor host running Monit\cite{monit}.
-We were able to login to the web-monitor to see the status of all our servers, databases, and load sharers.
-This assisted us in managing whether or not the services were running and allowed us to track down any problems, if they arose.
-Each server contains the server application that responds to clients as well as the Riak \cite{riak} databases.
-Riak handles auto-synchronization of the databases between the five servers.
-Note that the hot spares were setup to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly.
-This allows for them to immediately be ready for read/writes in the event that the original servers are down.
-With this configuration if we were to add a server, we would just need to update Riak and it would sync the databases to any additional servers as well.
+% Should talk about Node Agreement?
+As previously mentioned, each server contains the server application that responds to clients as well as the Riak databases.
+Riak handles auto-synchronization of the databases between any connected servers.
+This allows for data to be transparently transferred and replicated across all server-nodes in the ring.
+Servers can easily be added and removed from the ring by updating Riak.
+When Riak is updated, the current nodes will either start updating any new nodes or stop communicating with any nodes that are no longer in the ring, according to the new update.
 These servers, therefore, all contain the same information.
 If any servers go down, the distributed system would still run fine.
-We could have all servers go down except one and still be reliably handling requests.
+This configuration allows for all servers go down except one and the system would still be reliably handling requests.
 
 \subsection{Server Applications}
+% TODO Finish
 The server application handles requests from the user via the load sharers.
+Interpretation of the client messages and replies are handled by the applications. There is one application per server processing requests and responding via https messages with JSON objects.
 The server application supports the following features:
@@
 They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
+This is important to make sure that any servers that go down do not receive further communication attempts.
 
 \subsection{Clients}
+% TODO finish and separate into design/implementation
 Distrivia is implemented on three distinct platforms (web, Android, and iPhone).
@@
 \subsection{Network}
+For the implementation of Distriva, we deployed six servers on Amazon's Elastic Compute Cloud \cite{aec} to run the server application and host the databases.
+One server is being used as a web-monitor host running Monit\cite{monit}.
+We were able to login to the web-monitor to see the status of all our servers, databases, and load sharers.
+This assisted us in managing whether or not the services were running and allowed us to track down any problems, if they arose.
+Three of the servers were set up as active, available servers for constant use from querying clients.
+Two of the servers were set up as hot spares, in case of a failure.
+Note that the hot spares were set up to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly unless the load sharers find that no active servers are responding.
+If this happens, they then start relaying the client messages to the hot spares, which are already set up with the most up-to-date information.
 
-For this project, we set up two load balancers which are running on personal desktop computers that have reliable internet connections.
-The duplicate sharers allow for a load distributer to go down and we would still be able to serve requests to the servers. 
+For this project, we set up two load sharers which are running on personal desktop computers that have reliable internet connections.
+The duplicate sharers allow for a load sharer to go down and we would still be able to serve requests to the servers. 
 % TODO cite ZoneEdit
@@
 \subsection{Clients}
+% TODO finish and add photos
 % Show images of implemented clients
@@
 \section{Lessons Learned}
+% TODO finish
 
 \section{Future Work}
+% TODO finish
+% Categories
+% User added Question
+% Blackberry & iPad support
 

### 2011-05-11 papers/phase-three/paper.tex
Paper: Fix typo
Paper: Fix double the

@@
 The server application supports the following features:
-\begin{itemized}
+\begin{itemize}
 \item Client registration
@@
 \item Global leaderboard
-\end{itemized}
+\end{itemize}
 
@@
 Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
-This is an important part of the distributed system in keeping network traffic down on the the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
+This is an important part of the distributed system in keeping network traffic down on the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
 They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.

### 2011-05-12 papers/phase-three/paper.tex
Paper: Bring in additions from our paper pow-wow. Add images to paper.

@@
 High availability was a major concern for us, as it enables people to compete at all times.
-This form of trivia is a multiplayer social game.
+This form of trivia is a multi player social game.
 It takes advantage of a number of different platforms so that users can feel free to play on any device they prefer.
@@
 \subsection{Servers}
-For our servers, we used Amazon EC2 micro instances.
-These are running x86-64 Amazon Linux.
-They have 8gb of network attached storage and 613mb of memory.
+For our servers, we used Amazon EC2 micro instances,  running x86-64 custom Amazon Linux.
+They each have 8GB of network attached storage and 613MB of memory.
 
 Each server is installed with our custom web app that services our requests.
-Each one is also equipped with an instance of Riak \cite{riak} for maintaining our database.
-% TODO cite Flask and Tornado
-The Python web app utilizes the Flask web framework and we serve the application and all files with the Tornado web server, both of which are open source.
+They are  also equipped with an instance of Riak \cite{riak} which is our database back end of choice for persisting game and player.
+Our Python web app utilizes the Flask \cite{flask} web framework and we serve this application and all application content with the Tornado \cite{tornado} web server, both of which are open source.
 
-For load sharing, we used NGINX \cite{nginx} in a reverse proxy configuration.
-This service can be used on any machine with an active internet connection and a constantly reachable IP address or DNS lookup.
+For load sharing, we used the NGINX \cite{nginx} web server in a reverse proxy configuration.
+This service can be used on any machine with an active Internet connection and the ability to receive connections on port 80 for HTTP and port 443 SSL.
 
@@
 \subsection{Servers}
-% Should talk about Node Agreement?
 As previously mentioned, each server contains the server application that responds to clients as well as the Riak databases.
@@
 \subsection{Server Applications}
-% TODO Finish
 The server application handles requests from the user via the load sharers.
-Interpretation of the client messages and replies are handled by the applications. There is one application per server processing requests and responding via https messages with JSON objects.
+Interpretation of the client messages and replies are handled by the applications.
+There is one application per server processing requests and responding via https messages with JSON objects.
+Requests are formed using a REST like API, where the URL is the method we want to invoke.
+The parameters to the method's are passed in through a HTTP POST.
+The server processes the request reading or writing to the data store and returns the appropriate data in JSON format.
+This system is basically an abstracted RPC system, composed of two different web technologies.
+Every request to the API is checked for proper authentication.
+Authentication is handled by generating a unique token for each user login, which they need to pass along with each request.
+This method avoids the possibility of potential security vulnerabilities from passing the users password around more than needed.
 The server application supports the following features:
@@
 \item Question answering
-\item Global leaderboard
+\item Global leader board
 \end{itemize}
+
+The database back end was designed for high availability and durability of the game data.
+For every write to the data store, all other online nodes must agree with the write for it to be committed.
+In this way we can make sure that their is total consistency in the database at all times, reducing the risk of database corruption.
 
@@
 Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
-This is an important part of the distributed system in keeping network traffic down on the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
-They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
+This is an important part of the distributed system in keeping network traffic down on the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
 This is important to make sure that any servers that go down do not receive further communication attempts.
@@
 \subsection{Clients}
-% TODO finish and separate into design/implementation
-Distrivia is implemented on three distinct platforms (web, Android, and iPhone).
-The clients were designed to run without specific equipment or relying on external applications. 
-The clients can be run, once installed, from desktop computers, laptops, Androids, and iPhones out of box.
-The web client can be run from any browser that supports CSS, which is true of all modern web browsers.
-The web client can be run from any operating system that supports web browsing and has a connection to the internet (this includes mobile devices). 
-This gives users of blackberry phones and palms the ability to play, even though there is not a native app for them.
+Distrivia is designed for three distinct platforms (web, Android, and iPhone).
+The clients were designed to run on each platform without specific hardware or relying on external applications.
+The clients can be run, once installed, from desktop computers, laptops, Androids, and iPhones out of the box.
+The web client can be run from any browser that supports CSS and javascript, which is true of all modern graphical web browsers.
+This gives users of other mobile phones, such as Blackberrys or Palm Pres, the ability to play even though there is not a native app for them.
 The Android client will run on any Android platform running OS 2.1 or higher and does not use any unique services that require specific hardware.
 Likewise, the iPhone client will run on any iPhone/iPod touch platform running any iOS without the need for specific hardware.
-The Android and iPhone clients just require an active data connection either by cell signal or wireless internet.
+The Android and iPhone clients just require an active data connection either by cell signal or wireless Internet.
 
@@
 We tried to keep the layout as simple as possible, for the user to be able to easily navigate the game.
-The mobile clients are the most similar due to their limited screen real estate.
+The mobile clients are the quite similar due to their similar and limited screen real estate.
 This was important in allowing players to play on multiple platforms while using a layout they were used to.
@@
 
+The clients are broken down into 4 distinct views/activities: login, join, compete, and view leader board. 
+Login provides the player with a way to access the game using a username/password combination.
+From the same screen, a user can create a new account, which will automatically log them in after creation.
+Once the player has been verified, the client will progress to the join screen. 
+The join screen allows players to pick from joining public games, joining/creating private games, or viewing the global leader board. 
+Once a user requests to join a game (private or public) the client will request status updates from the server about the progress of the game.
+These status queries occur every 5 seconds, allowing time for the server to respond without becoming overloaded. 
+Once the game has enough players to start, the client is alerted through these status queries and the clients progress to the competition screen.
+During competition, the players is presented with the question and a set of possible answers.
+The player can then read, select an answer, and submit the answer using the “Submit” button.
+The screen will then be updated with the new scores and the next question/answers until the end of the round.
+Once the player reaches the end of a round, the player is shown the local leaderboard for the round and transported back to the join screen for them to join another game.
+
+A large portion of designing the clients was devoted to allowing easy navigation for players without overloading the servers with requests.
+There are a couple points during game play where the client is requesting “constant” information to interactively keep updated.
+During these occasions, the clients pause for 5 seconds before querying the system again as to not confuse the clients.
+
 \subsection{Messages}
-Distrivia uses https protocol for communication. 
+Distrivia uses the https protocol for communication.
 This provides a secure and usable messaging system that both the client and server APIs use.
@@
 Initially a user session key is generated using the UUID\cite{uuid} algorithm and returned to the user on successful authentication.
-This session key is then passed back to the server with every incoming
-message. 
-Messages are sent to the server using POST and GET request methods supported
-by the HTTP protocol. 
+This session key is then passed back to the server with every sent message.
+Messages are sent to the server using POST request methods supported by the HTTP protocol.
 Responses from the server are in the form of JSON \cite{json} objects.
@@
 With the web client the JSON object returned from the server is instantly usable, however for other applications, parsing the JSON object into native objects is necessary.
-% Maybe should go under implementation?
-The Android SDK provides libraries to do this, located in the
-org.json \cite{orgjson} package name space.
-% Include the package used for iPhone and cite
+The Android Software Development Kit provides libraries to do this, located in the org.json \cite{orgjson} package name space.
+This was also accomplished for iOS by parsing JSON objects to native Objective-C objects using the JSONKit \cite{objcjson} package developed by John Engelhart.
 
@@
 One server is being used as a web-monitor host running Monit\cite{monit}.
-We were able to login to the web-monitor to see the status of all our servers, databases, and load sharers.
-This assisted us in managing whether or not the services were running and allowed us to track down any problems, if they arose.
-Three of the servers were set up as active, available servers for constant use from querying clients.
-Two of the servers were set up as hot spares, in case of a failure.
-Note that the hot spares were set up to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly unless the load sharers find that no active servers are responding.
-If this happens, they then start relaying the client messages to the hot spares, which are already set up with the most up-to-date information.
+We were able to log in to the web-monitor to see the status of all our servers, databases, and load sharers. 
+This assisted us in managing whether or not the services were running and allowed us to track down any problems when they arose.
+Three of the servers were set up as active, front facing servers for clients to query.
+The two other servers were set up as hot spares, in case of a failure. 
+The hot spares were set up to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly unless the load sharers found no active servers are responding.
+In the event of such a failure the load distributor would automatically fail over and start relaying the client messages to the hot spares. 
+Since both hot spares are members of the database cluster they already would have the most up-to-date game information information.
 
-For this project, we set up two load sharers which are running on personal desktop computers that have reliable internet connections.
+For this project, we set up two load sharers which are running on personal desktop computers with reliable Internet connections.
 The duplicate sharers allow for a load sharer to go down and we would still be able to serve requests to the servers.
-% TODO cite ZoneEdit
-These are set up with round robin DNS entries, courtesy of ZoneEdit.com, a free DNS management service.
+These are set up with round robin DNS entries, courtesy of ZoneEdit.com \cite{zoneedit}, a free DNS management service.
 These load sharers are selected by the clients where distrivia.lame.ws will select either load distributer that is up at random.
@@
 \subsection{Clients}
-% TODO finish and add photos
-% Show images of implemented clients
-Creating native apps for the Android OS and iPhone gives the users the best performance on those devices along with the native look and feel of the device for optimal design.
-\subsubsection{Web}
+We implemented the Distrivia applications on multiple platforms.
+For the web client, we used Chrome, Firefox, Safari, and Internet Explorer.
+Using these different web browsers, we were successfully able to compete with users on other browsers and devices.
+For the mobile platforms we implemented the native Distrivia apps for Android and iPhone.
+Creating native apps for Android and iPhone gives the users the best performance on those devices along with the native look and feel of the device for optimal design.
+Playability on all clients was similar and easy to navigate. Shown below are screenshots from the various implementations of the Distrivia project.
+\begin{figure}[h!]
+   \includegraphics[scale=0.12]{iPhone_join.png}
+   \includegraphics[scale=0.12]{iPhone_leaderboard2.png}
+   \includegraphics[scale=0.12]{iPhone_round.png}
+   \caption{iPhone Client User Interface}
+\end{figure}
 
-\subsubsection{Android}
+\begin{figure}[h!]
+   \includegraphics[scale=0.32]{android/join.png}
+   \includegraphics[scale=0.32]{android/lb.png}
+   \includegraphics[scale=0.32]{android/answer2.png}
+   \caption{Android Client User Interface}
+\end{figure}
 
-\subsubsection{iPhone}
+\begin{figure}[h!]
+   \includegraphics[scale=0.21]{web_join.png}
+   \includegraphics[scale=0.21]{web_leader.png}
+   \includegraphics[scale=0.21]{web_round.png}
+   \caption{Web Client User Interface}
+\end{figure}
 
 \section{Lessons Learned}
-% TODO finish
+One of the first lessons we learned during this project was the concept that you can't have high performance, durability, and availability.
+For our system which does not have to do a significant amount of computation for each user request, we decided to sacrifice performance in favor of durability and availability.
+The computations are very quick and simple, and we think users would rather have a potentially slow service than an unavailable service.
+
+While it was a concept we were already familiar with, the importance of consistency was heavily ingrained into us.
+During development, we frequently ran into trouble where our clients would start off communicating with one server and then switch later.
+Our client would then often start getting errors because the new server didn't recognize the authentication key.
+As a result we had to go back and really make sure our servers stayed consistent so that when clients end up talking to a different server the communications without interruption.
+It also made us realize just how hard it can be to keep multiple computers synchronized at all times.
 
 \section{Future Work}
-% TODO finish
-% Categories
-% User added Question
-% Blackberry & iPad support
+For future work on this system, we've thought of adding a few new features that would improve gameplay and diversity of the experience for the players.
+We don't have have any revolutionary upgrades we'd like to perform on the server-side.
+Overall, we are satisfied with the performance of the server including the reliability, response speed, and availability.
+The features we have contemplated adding in future work include: categories, user added content, support for more platforms, and private competition via bluetooth or local wifi.
+
+Distrivia randomizes the questions in all categories and sets up each game to have these randomized groupings.
+It would be nice, in the future, to support the feature of players being able to choose from a list of categories to compete in.
+This would allow players to compete in areas that they feel most comfortable in or to try out new categories to really test their trivia prowess.
+
+Another feature to look into would be allowing users to submit their own questions/answers to the server for other players to play.
+This would help build the database and get a broader range of questions.
+There would need to be some sort of interactive rating system so that players can rate user-added question so that if the question were rated low enough, it would no longer be included in future games.
+For a different approach, the player may only be able to use custom questions in private rounds with their friends so that the questions wouldn't need to be monitored or rated.
+
+Distrivia currently runs natively on two mobile platforms.
+It would be preferred if this could be expanded to more platforms to allow for a broader range of users to participate.
+Using the current framework, it would not be much more effort to add native applications for blackberrys, palm devices, Android tablets, and iPads.
+Android tablets and iPads would be interesting devices to add support for since they allow utilization of larger screen space.
+This would allow the user to be able to see full local leader boards while competing in each round, as well as other upgraded viewing options from the smaller mobile devices.
+
+Lastly, support for bluetooth connected play and local wifi play would add even greater support for private gameplay. 
+It would also make it so that devices would not need connections to the Internet to participate.
+This means that non-data devices such as iPods could play without access to wifi.
+It would also allow users in data dead-zones to participate and play with their friends.
 

### 2011-05-12 src/clients/web/distrivia.js
Added loading icon to private game functions on web client

@@ -286,7 +286,7 @@ function Next( ref ){
          }else{
             errMsg( "Could not load next question" );
          }
-
+         unload();
          enable( func, ref );
       }
    };
@@ -299,6 +299,7 @@ function Next( ref ){
       xr.setRequestHeader("Content-type", "application/x-www-form-urlencoded");
       xr.send(param);
       errClear();
+      loading();
    }else{
       enable( func, ref );
       errMsg( "Please select an answer." );
@@ -442,6 +443,7 @@ function Start(ref){
       if( xr.readyState == 4 && xml_n == xr_n ){
          if( xr.status == 200 ){
             CheckStatus(false);
+            unload();
          }
       }
    };
@@ -452,6 +454,8 @@ function Start(ref){
    xr.setRequestHeader("Content-type", "application/x-www-form-urlencoded");
    xr.send(param);
 
+   loading();
+
    return false;
 }
 
@@ -459,7 +463,7 @@ function Start(ref){
  * Creates a private game
  */
 function Make(ref){
-   var func = "start";
+   var func = "make";
    if( disabled(func, ref) ){
       return false;
    }else{
@@ -468,9 +472,6 @@ function Make(ref){
 
    var xr = XML();
    var xml_n = ++xr_n;
-
-   var bl = byId('board_list');
-   addClass( bl, 'board_load' );
 
    xr.onreadystatechange = function(){
       if( xr.readyState == 4 && xml_n == xr_n ){
@@ -498,6 +499,7 @@ function Make(ref){
                errMsg( "Couldn't create game, server error." );
 
            }
+           unload();
          }
       }
    };
@@ -540,6 +542,8 @@ function Make(ref){
       xr.open( "POST", erl("/private/create/" + gnum), true );
       xr.setRequestHeader("Content-type", "application/x-www-form-urlencoded");
       xr.send(param);
+
+      loading();
    }else{
       enable(func, ref);
    }
@@ -804,6 +808,7 @@ function Private(ref){
                errMsg( "Server connection error" );
             }
             enable( func, ref );
+            unload();
          }
       }
    }
@@ -830,6 +835,7 @@ function Private(ref){
       xr.setRequestHeader("Content-type", "application/x-www-form-urlencoded");
 
       xr.send( param );
+      loading();
    }else{
       enable( func, ref );
    }

### 2011-05-12 poster/poster_landscape.tex
Poster changes

@@
   % Show grid to help with alignment
-  grid=yes,
+  grid=no,
   % Column spacing
@@
   headerFontColor=white,
-  boxColorOne=ritbrown,
-  boxColorTwo=ritbrownl,
+  boxColorOne=white,
+  boxColorTwo=white,
   % Format of textbox
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our motivation for this project was to build a system that would allow people to compete across multiple platforms reliably.
+High availability was a major concern for us, as it enables people to compete at all times.
+This form of trivia is a multi player social game.
+It takes advantage of a number of different platforms so that users can feel free to play on any device they prefer.
+The web client ensures that almost any device will be able to connect and play.
+Designing it on mobile platforms allows us to take advantage of the specific platform and lets people easily play on the go.
+  }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \headerbox{Architecture}{name=arch,column=3}{
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	\includegraphics[scale=0.45]{images/amazon-logo.png}
+	\includegraphics[scale=0.045]{images/android-logo.png}
+	\includegraphics[scale=0.35]{images/flask-logo.png}
+	\includegraphics[scale=0.5]{images/ios-logo.png}
+	\includegraphics[scale=0.6]{images/logo-riak.png}
+	\includegraphics[scale=0.2]{images/python-logo.png}
+	\includegraphics[scale=0.5]{images/tornado-logo.png}
+	\includegraphics[scale=0.3]{images/nginx-logo.png}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Architecture}{name=arch,column=0,below=motivation}{
+  \headerbox{Design}{name=design,column=1, span=2}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \centering
+	\includegraphics[scale=0.4]{../papers/phase-three/diagram.png}
+
+\begin{multicols}{3}
+\begin{itemize}
+\item Round Robin DNS \\
+\item Two Load Sharers 
+\item Three front end node  \\
+\item Two hot spares 
+\item Riak on each server \\
+\item Webapp on each server
+\end{itemize}
+
+\end{multicols}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Design}{name=design,column=1, span=1}{
+  \headerbox{Implementation}{name=implementation,column=1,below=design,span=2}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{multicols}{3}
+\includegraphics[scale=0.22]{../papers/phase-three/iPhone_round.png} \\
+\includegraphics[scale=0.52]{../papers/phase-three/android/answer2.png} \\
+\includegraphics[scale=0.40]{../papers/phase-three/web_round.png}
+\end{multicols}
+
+\begin{multicols}{3}
+\centering iPhone Client \\
+\centering Android Client \\
+\centering Web Client
+\end{multicols}
+
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Implementation}{name=implementation,column=1,below=design}{
+  \headerbox{Lessons Learned}{name=lessons,column=0, below=motivation}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{itemize}
+  \item You will always be balancing between Durability, Performance, and Availability.
+  \item Consistent deployment of system code across all servers and hot spares
+  is key to being able to debug the system.
+  \item Developing a consistent API before starting development is invaluable
+  to reducing wasted man hours.
+\end{itemize}
   }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \headerbox{Lessons Learned}{name=lessons,column=2, row=0}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  }
+  \headerbox{Future Work}{name=future,column=0, below=lessons}{
 
-  \headerbox{Future Work}{name=future,column=2,row=0.4}{
+\begin{itemize}
+\item Blackberry, iPad, Android tablet and Palm clients.
+\item Categorized questions, so you can play your strengths or weaknesses.
+\item Allowing users to add custom questions and answers.
+\item Private local games over bluetooth or local WiFi.
+\end{itemize}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2011-05-12 papers/phase-three/paper.tex
Paper: Proper citations and editted images.
Paper: Add Sam's lessons learned paragraph

@@
 \title{ Distrivia: A Distributed Trivia Game }
-\numberofauthors{3}
-\author{
-\alignauthor
-Brian Gianforcaro \\
-   	\affaddr{Rochester Institute of Technology}\\
-   	\email{bjg1955@rit.edu}
-\alignauthor
-Steven Glazer \\
-   	\affaddr{Rochester Institute of Technology}\\
-   	\email{sfg6126@rit.edu}
-\alignauthor
-Samuel Milton \\
-   	\affaddr{Rochester Institute of Technology}\\
-   	\email{srm2997@rit.edu}
-}
+%\numberofauthors{3}
+%\author{
+%\alignauthor
+%Brian Gianforcaro \\
+%   	\affaddr{Rochester Institute of Technology}\\
+%   	\email{bjg1955@rit.edu}
+%\alignauthor
+%Steven Glazer \\
+%   	\affaddr{Rochester Institute of Technology}\\
+%   	\email{sfg6126@rit.edu}
+%\alignauthor
+%Samuel Milton \\
+%   	\affaddr{Rochester Institute of Technology}\\
+%   	\email{srm2997@rit.edu}
+%}
 \maketitle
@@
 \begin{figure}[h!]
-   \includegraphics[scale=0.21]{web_join.png}
-   \includegraphics[scale=0.21]{web_leader.png}
-   \includegraphics[scale=0.21]{web_round.png}
+   \includegraphics[scale=0.24]{web_join.png}
+   \includegraphics[scale=0.24]{web_leader.png}
+   \includegraphics[scale=0.24]{web_round.png}
    \caption{Web Client User Interface}
@@
 
+Another lesson we learned was that we should start with a well defined API.  We
+endured a lot of headaches during this project as a result of incompatible API
+calls between the server and clients.  Even after we went and defined how we
+wanted out API calls to work, we neglected to specifically state how they would
+return some of the information.  So we continued to have problems there.  If we
+had taken the time to sit down as a group in the beginning and create a well
+thought-out API set, it would have greatly simplified our implementations
+later.  
 \section{Future Work}

### 2011-05-12 papers/phase-three/paper.tex
Sticky changes

@@
 This paper will outline our motivations behind the project, the architecture, design, implementation, lessons learned, and future work for the distributed trivia system.
-The distrivia system was implemented on 3 platforms (web, Android, and iPhone) to provide multiple ways for players to stay connected.
+The Distrivia system was implemented on 3 platforms (web, Android, and iPhone) to provide multiple ways for players to stay connected.
 It also utilizes advanced distributed systems algorithms and technology such as Amazon's EC2, Riak, SSL communication, round robin DNS, and NGINX load sharing.
@@
 \section{Architecture}
-\subsection{Servers}
 For our servers, we used Amazon EC2 micro instances,  running x86-64 custom Amazon Linux.
@@
 \subsection{Server Applications}
-The server application handles requests from the user via the load sharers.
+The server application handles requests from the user via the load distributers.
 Interpretation of the client messages and replies are handled by the applications.
@@
 
-\subsection{Load Sharers}
-The load sharers act as an agent between the clients and the servers to ensure reliable, fast communication.
-Messages are relayed through the load sharers from the client.
-Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
+\subsection{Load Distributers}
+The load distributers act as an agent between the clients and the servers to
+ensure reliable, fast communication. Messages are relayed through the load
+distributers from the client.
+Once received, the load distributer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
 This is an important part of the distributed system in keeping network traffic down on the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
@@
 One server is being used as a web-monitor host running Monit\cite{monit}.
-We were able to log in to the web-monitor to see the status of all our servers, databases, and load sharers. 
+We were able to log in to the web-monitor to see the status of all our servers, databases, and load distributers. 
 This assisted us in managing whether or not the services were running and allowed us to track down any problems when they arose.
@@
 The two other servers were set up as hot spares, in case of a failure. 
-The hot spares were set up to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly unless the load sharers found no active servers are responding.
+The hot spares were set up to be part of the database cluster so they have a full copy of the database on hand, however they did not accept any reads or writes directly unless the load distributers found no active servers are responding.
 In the event of such a failure the load distributor would automatically fail over and start relaying the client messages to the hot spares. 
@@
 
-For this project, we set up two load sharers which are running on personal desktop computers with reliable Internet connections.
-The duplicate sharers allow for a load sharer to go down and we would still be able to serve requests to the servers.
+For this project, we set up two load distributers which are running on personal desktop computers with reliable Internet connections.
+The duplicate distributers allow for a load distributer to go down and we would still be able to serve requests to the servers.
 These are set up with round robin DNS entries, courtesy of ZoneEdit.com \cite{zoneedit}, a free DNS management service.
-These load sharers are selected by the clients where distrivia.lame.ws will select either load distributer that is up at random.
+These load distributers are selected by the clients where distrivia.lame.ws will select either load distributer that is up at random.
 If a load distributer should go down or become unreachable the DNS service will no longer serve that hosts DNS record until it is again reachable.
